### 2022-01-24 MS_physiology_infection.Rmd
R_code and datasheet added

---
title: "Manuscript_physiological_consequences_blood_parasite_infection"
author: "Tony Rinaud"
date: "`r Sys.Date()`"
output: pdf_document
---

# Analysis of blood parasite infection effect on physiological change of common buzzard nestlings:

  Data from common buzzard's (*Buteo buteo*) nestling of the years 2016, 2018, 2019 and 2020 which have been sampled twice during their nesting phase.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required packages

```{r packages, message=F, warning=F}
library(easypackages)
libraries('plotly','ggplot2','Hmisc','ggalt','plyr','chron','dplyr','stringr','tidyr','FSA','grid','gridExtra','ggsci','lme4','RVAideMemoire','lsmeans','MuMIn','EnvStats','devtools','RColorBrewer','tidyverse','brms','tidybayes','patchwork','pdftools','osmdata','rgdal','magrittr','purrr','forcats','modelr','ggstance','ggridges','cowplot','ggrepel','gganimate','ggridges','rptR','rdwd','sjPlot','sjlabelled','sjmisc','wesanderson', "ggpubr","ggsignif",'ggdist','ggeffect')

# Routine clean-up upon start
rm(list=ls())

theme_set(theme_tidybayes() + panel_border())

```

```{r data, echo=F}

## Data source

data2016_2020=read.csv('./physiology_infection_stage_full_wideformat.csv', h=T, sep=';', dec=".")

data2016_2020$Nest=as.factor(data2016_2020$Nest)
data2016_2020$Date=chron(as.character(data2016_2020$Date), format="d/m/y")
data2016_2020$Infection_intensity=as.factor(data2016_2020$Infection_intensity)
data2016_2020$Prevalence=as.factor(data2016_2020$Prevalence)
data2016_2020$Breathing_rate=scale(as.numeric(data2016_2020$Breathing_rate))
data2016_2020$Sex=as.factor(data2016_2020$Sex)
data2016_2020$Sampling_rank=as.factor(data2016_2020$Sampling_rank)
data2016_2020$Weight_g=as.numeric(data2016_2020$Weight.2)
data2016_2020$Wing_cm=as.numeric(data2016_2020$Wing)
data2016_2020$body_temperature=scale(as.numeric(data2016_2020$body_temperature))
data2016_2020$delta_body_condition=scale(as.numeric(data2016_2020$delta_body_condition))
data2016_2020$Ambient_Temperature_AvgC=as.numeric(data2016_2020$TemperatureAvgC)
data2016_2020$Treatment=as.factor(data2016_2020$Treatment)
data2016_2020$Year=as.factor(data2016_2020$Year)
data2016_2020$Growth_rate=scale(as.numeric(data2016_2020$Growth_rate))
data2016_2020$Growth_rate=scale(as.numeric(data2016_2020$Growth_rate_unlog))

data2016_2020$Diff_Inf_Class=factor(data2016_2020$Diff_Inf_Class, levels=c("Uninfected","Increase","Peak","Decrease"))
data2016_2020=arrange(data2016_2020,data2016_2020$Diff_Inf_Class)

```

**Results**

## Testing for effectiveness of treatment

```{r}

# Contingency table of control versus treated but uninfected nestlings at the two samplings

tab.cont_noinfect=matrix(c(length(data2016_2020$Infection_intensity.1[data2016_2020$Infection_intensity.1 %in% 0 & data2016_2020$Treatment %in% "Control"]),length(data2016_2020$Infection_intensity.1[data2016_2020$Infection_intensity.1 %in% 0 & data2016_2020$Treatment %in% "Malarone"]),length(data2016_2020$Prevalence[data2016_2020$Prevalence %in% 0 & data2016_2020$Treatment %in% "Control" & data2016_2020$Sampling_rank %in% 2]),length(data2016_2020$Prevalence[data2016_2020$Prevalence %in% 0 & data2016_2020$Treatment %in% "Malarone" & data2016_2020$Sampling_rank %in% 2])),nrow = 2,ncol = 2,dimnames = list(c("Control","Malarone"),c("Before","After")))

# Testing whether proportions of uninfected nestlings at first and second samplings differs between treatments

tab.cont_noinfect=t(tab.cont_noinfect)

prop.test(tab.cont_noinfect)

pairwise.prop.test(tab.cont_noinfect)

# Contingency table of control versus treated but infected at the two samplings

tab.cont_infected=matrix(c(length(data2016_2020$Infection_intensity.1[data2016_2020$Infection_intensity.1 %in% c(1,2,3,4) & data2016_2020$Treatment %in% "Control"]),length(data2016_2020$Infection_intensity.1[data2016_2020$Infection_intensity.1 %in% c(1,2,3,4) & data2016_2020$Treatment %in% "Malarone"]),length(data2016_2020$Prevalence[data2016_2020$Prevalence %in% 1 & data2016_2020$Treatment %in% "Control"]),length(data2016_2020$Prevalence[data2016_2020$Prevalence %in% 1 & data2016_2020$Treatment %in% "Malarone"])), nrow = 2, ncol = 2, dimnames = list(c("Control","Malarone"),c("Pre","Post")))

# Testing whether proportions of infected nestlings at first and second samplings differs between treatments

tab.cont_infected=t(tab.cont_infected)

prop.test(tab.cont_infected)

pairwise.prop.test(tab.cont_infected)

## plotting count of infected / uninfected nestlings across treatments

tab_cont=data.frame(Timepoint=c("Pre-treatment","Post-treatment","Pre-treatment","Post-treatment","Pre-treatment","Post-treatment","Pre-treatment","Post-treatment"),Count=c(tab.cont_noinfect[1,1],tab.cont_noinfect[2,1],tab.cont_noinfect[1,2],tab.cont_noinfect[2,2],tab.cont_infected[1,1],tab.cont_infected[2,1],tab.cont_infected[1,2],tab.cont_infected[2,2]),Treatment=c("Control","Control","Malarone","Malarone","Control","Control","Malarone","Malarone"),Prevalence=c("Uninfected","Uninfected","Uninfected","Uninfected","Infected","Infected","Infected","Infected"))

tab_cont$Timepoint=factor(tab_cont$Timepoint,levels = c("Pre-treatment","Post-treatment"))
tab_cont$Prevalence=factor(tab_cont$Prevalence,levels = c("Uninfected","Infected"))

# Figure 2a

treatment_prevalence_changes=ggplot(tab_cont)+
  aes(Timepoint,Count,fill=Prevalence)+
  facet_wrap(facets = "Treatment")+
  geom_bar(stat = 'identity',  width = 0.3)+
  labs(y="Count of nestlings")+
  geom_text(aes(label=Count),position = position_stack(0.5))+
  scale_fill_manual(values=c("#D0D0D0","#A8A8A8"))+
  theme(axis.title.x = element_blank(), strip.text = element_text(size=14, face="bold"),legend.text = element_text(size=12), legend.title = element_text(size=14),axis.title.y=element_text(size=14, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=12))

## plotting mean infection intensity values of nestlings across treatments

mean_inf_int=c(mean(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Control"])), na.rm=T),mean(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Control"])), na.rm=T),mean(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Malarone"])), na.rm=T),mean(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Malarone"])), na.rm=T))

se_inf_int=c(se(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Control"]))),se(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Control"]))),se(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Malarone"]))), se(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Malarone"]))))

tab_mean=data.frame(Timepoint=c("Pre-treatment","Post-treatment","Pre-treatment","Post-treatment"),Mean_infection_intensity=mean_inf_int,se_inf_int=se_inf_int,Treatment=c("Control","Control","Malarone","Malarone"))

tab_mean$Timepoint=factor(tab_mean$Timepoint,levels = c("Pre-treatment","Post-treatment"))

# Figure 2b

treatment_meaninf_changes=ggplot(tab_mean)+
  aes(Timepoint,Mean_infection_intensity,group=Treatment)+
  geom_vline(xintercept = "Pre-treatment", linetype = "dashed", color='darkgrey')+
  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color='darkgrey')+
  labs(y="Mean infection intensity")+
  ylim(c(0,3))+
  geom_line(aes(color=Treatment), size=2)+
  geom_errorbar(ymin=tab_mean$Mean_infection_intensity-tab_mean$se_inf_int, ymax=tab_mean$Mean_infection_intensity+tab_mean$se_inf_int,colour="black",
               size=1.5 , width=0.05)+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5)+ 
  scale_color_manual(values=c("lightgrey","black"))+
  theme_classic()+
  theme(axis.title.x = element_blank(), legend.text = element_text(size=12), legend.title = element_text(size=14), axis.title.y=element_text(size=16, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=12), plot.margin = unit(c(0,0,0,30), "pt"))

# Panel wrapping Fig2 a & b:

treatment_prevalence_changes+treatment_meaninf_changes+ plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

# Mean infection intensity

mean_before_after=data.frame(Ring_no=c(data2016_2020$Ring_no[data2016_2020$Sampling_rank %in% 2], data2016_2020$Ring_no[data2016_2020$Sampling_rank %in% 2]), Infection_intensity=c(as.character(data2016_2020$Infection_intensity.1), as.character(data2016_2020$Infection_intensity)),Treatment=c(as.character(data2016_2020$Treatment[data2016_2020$Sampling_rank %in% 2]), as.character(data2016_2020$Treatment[data2016_2020$Sampling_rank %in% 2])),Timepoint=c(rep("Pre-treatment",times=length(data2016_2020$Treatment)),rep("Post-treatment",times=length(data2016_2020$Infection_intensity))))

mean_before_after$Treatment=as.factor(mean_before_after$Treatment)
mean_before_after$Timepoint=as.factor(mean_before_after$Timepoint)

mal=mean_before_after[mean_before_after$Treatment %in% "Malarone",]
ctrl=mean_before_after[mean_before_after$Treatment %in% "Control",]

# Testing for difference in infection intensity in malarone treated nestlings before versus after treatment

perm.t.test(as.numeric(as.character(mal$Infection_intensity))~mal$Timepoint)

# Testing for difference in infection intensity in control nestlings before versus after treatment

perm.t.test(as.numeric(as.character(ctrl$Infection_intensity))~ctrl$Timepoint)
```

## Testing the effect of antimalarial treatment on the four physiological parameters in nestlings

### Breathing rate

```{r}

# Model 
# No effect of treatment on the breathing rate of nestlings

lm_d1=lm(Breathing_rate~Treatment, data=data2016_2020)
```

### Body temperature

```{r}

# Model 
# No effect of treatment on the body temperature of nestlings

lm_d2=lm(body_temperature~Treatment, data=data2016_2020)
```

### Body condition change

```{r}

# Model 
# No effect of treatment on the body condition change of nestlings

lm_d3=lm(delta_body_condition~Treatment, data=data2016_2020)
```

### Growth rate

```{r}

# Model 
# No effect of the antimalarial treatment on the growth rate

lm_d4=lm(Growth_rate~Treatment, data=data2016_2020)

# Table S1

tab_model(lm_d1,lm_d2,lm_d3,lm_d4,
          show.reflvl = T,
          show.ci50 = T ,
          show.stat = T,
          string.stat = "t",
          pred.labels = c("Intercept","Treatment [Malarone]"),
          dv.labels = c("Breathing rate","Body temperature", "Δ Body condition","Growth rate"),
          file = "./table_results/Physiological_parameters_in_decreasing_control_treated.html")
```

```{r, echo=F}

# Filtering non-applicable infection change

data2016_2020=data2016_2020[!is.na(data2016_2020$Diff_Inf_Class),]

```

## Summary sample sizes data

```{r}
#Summary of sample size across years

table(data2016_2020$Year)

### Number samples across infection stages

table(data2016_2020$Diff_Inf_Class)

### Average days between first and second sample

mean(data2016_2020$days_resample)

sd(data2016_2020$days_resample)

range(data2016_2020$days_resample)

### table infection prevalence in nestlings

table(data2016_2020$Prevalence)

```

# Infection stages as response variable

## 1) Variation of breathing rate according to infection stage

```{r mixed model breathing rate, warning=F, message=F, echo=F}

# Model

lmer_br=lmer(data= data2016_2020, Breathing_rate~Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample+Age_in_days+Weight_g+Sex+Ambient_Temperature_AvgC+Year+(1|Nest))

# Predicted values for each infection stage

mod_br=get_model_data(lmer_br,type='pred',terms="Diff_Inf_Class") %>% 
   mutate(x=factor(c("Uninfected","Increase","Peak","Decrease"), levels=c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for breathing rate data

n=table(data2016_2020$Diff_Inf_Class[!is.na(data2016_2020$Breathing_rate)])

mod_br <- mod_br %>% 
  mutate(x = factor(c(paste0(x,"\nn=",n)), levels=c(paste0(x,"\nn=",n))))

gg1_pred=ggplot(mod_br)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_br$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Breathing rate")+
  ylim(c(min(mod_br$conf.low)-0.3,max(mod_br$conf.high)+0.5))+
  geom_errorbar(aes(ymin=mod_br$conf.low,ymax=mod_br$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_br$predicted-mod_br$std.error,ymax=mod_br$predicted+mod_br$std.error),size=8, colour=wes_palette("Zissou1",4), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
  aes(x=1, y=max(mod_br$conf.high)+0.3, xend=4, yend=max(mod_br$conf.high)+0.3))+
  geom_text(aes(x=2.5, y=max(mod_br$conf.high)+0.42),
  label="n.s.", size = 5)
```

## 2) Variation of body temperature according to infection stage

```{r mixed model body temp after, warning=FALSE, message=F, echo=F}

# Model

lmer_bt=lmer(data = data2016_2020,body_temperature~Diff_Inf_Class+Diff_Inf_Class:Treatment+Ambient_Temperature_AvgC+days_resample+Age_in_days+Weight_g+Sex+Year+(1|Nest))

# Predicted values for each infection stage

mod_bt=get_model_data(lmer_bt,type='pred',terms="Diff_Inf_Class") %>%
  mutate(x=factor(c("Uninfected","Increase","Peak","Decrease"), levels=c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for body temperature data

n2=table(data2016_2020$Diff_Inf_Class[!is.na(data2016_2020$body_temperature)])

mod_bt <- mod_bt %>% 
  mutate(x = factor(c(paste0(x,"\nn=",n2)), levels=c(paste0(x,"\nn=",n2))))

gg2_pred=ggplot(mod_bt)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_bt$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Body temperature")+
  geom_errorbar(aes(ymin=mod_bt$conf.low,ymax=mod_bt$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_bt$predicted-mod_bt$std.error,ymax=mod_bt$predicted+mod_bt$std.error),size=8,colour=wes_palette("Zissou1",4), width=0)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title.y=element_text(size=14, margin=unit(c(0,3,0,0),"mm")),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=0.7, xend=4, yend=0.7))+
    geom_text(aes(x=2.5, y=0.78),
              label="n.s.", size = 5)

```

## 3) Variation of body condition according to infection stages

```{r mixed model body condition, warning=FALSE, message=F, echo=F}

# Model

lmer_bc=lmer(data= data2016_2020,delta_body_condition~Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample+Age_in_days+Year+(1|Nest))

# Predicted values for each infection stage

mod_bc=get_model_data(lmer_bc,type='pred',terms="Diff_Inf_Class") %>%
  mutate(x=factor(c("Uninfected","Increase","Peak","Decrease"), levels=c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for body condition change data

n3=table(data2016_2020$Diff_Inf_Class[!is.na(data2016_2020$delta_body_condition)])

mod_bc <- mod_bc %>% 
  mutate(x = factor(c(paste0(x,"\nn=",n3)), levels=c(paste0(x,"\nn=",n3))))

# Plot of predicted values of body condition change among infection stages

gg3_pred=ggplot(mod_bc)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_bc$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Δ Body condition")+
  geom_errorbar(aes(ymin=mod_bc$conf.low,ymax=mod_bc$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_bc$predicted-mod_bc$std.error,ymax=mod_bc$predicted+mod_bc$std.error),size=8,colour=wes_palette("Zissou1",4), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_bc$conf.high)+0.3, xend=4, yend=max(mod_bc$conf.high)+0.3))+
    geom_text(aes(x=2.5, y=max(mod_bc$conf.high)+0.4),
              label="n.s.", size = 5)

```

## 4) Variation of growth rate according to infection stages

```{r mixed model body temp, warning=FALSE, message=F, echo=F}

# Model

lmer_gr=lmer(data=data2016_2020,Growth_rate~Diff_Inf_Class+Diff_Inf_Class:Treatment+Sex+days_resample+Age_in_days+Year+(1|Nest))

# Predicted values for each infection stages

mod_gr=get_model_data(lmer_gr,type='pred',terms="Diff_Inf_Class")%>%
  mutate(x=factor(c("Uninfected","Increase","Peak","Decrease"), levels=c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for growth rate data

n4=table(data2016_2020$Diff_Inf_Class[!is.na(data2016_2020$Growth_rate)])

mod_gr <- mod_gr %>% 
  mutate(x = factor(c(paste0(x,"\nn=",n4)), levels=c(paste0(x,"\nn=",n4))))

gg4_pred=ggplot(mod_gr)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_gr$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Growth rate")+
  geom_errorbar(aes(ymin=mod_gr$conf.low,ymax=mod_gr$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_gr$predicted-mod_gr$std.error,ymax=mod_gr$predicted+mod_gr$std.error),size=8,colour=wes_palette("Zissou1",4), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title.y=element_text(size=14,margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 30, "pt"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_gr$conf.high)+0.2, xend=4, yend=max(mod_gr$conf.high)+0.2))+
    geom_text(aes(x=2.5, y=max(mod_gr$conf.high)+0.3),
              label="n.s.", size = 5)

```

# Summary four models

```{r, summary}

# Figure 4

gg1_pred+gg2_pred+gg3_pred+gg4_pred + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

# Table 3

sjPlot::tab_model(lmer_br,lmer_bt,lmer_bc,lmer_gr,
                  show.ci50 = T ,
                  show.stat = T,
                  string.stat = "t",
                  df.method = "kr",
                  dv.labels = c("Breathing rate","Body temperature","Δ Body condition","Growth rate"),
                  file = "./table_results/Table_results_lmer_physiological_parameters_p.val_kr.html")

```

# Parasitemia as response variable

## 1) Variation of breathing rate according to Leucocytozoon increase, Peak or increase infection intensity

```{r mixed model breathing rate 2, warning=F, message=F, echo=F}

# Model

lmer_br_para=lmer(data=data2016_2020, Breathing_rate~Infection_intensity+Infection_intensity:Treatment+days_resample+Age_in_days+Weight_g+Sex+Ambient_Temperature_AvgC+Year+(1|Nest))

# Predicted values for post-treament parasitemia

mod_br_para=get_model_data(lmer_br_para,type='pred',terms="Infection_intensity") %>% 
   mutate(x=factor(c("0","1","2","3","4"), levels=c("0","1","2","3","4")))

# Table with sample sizes specific for breathing rate change data

m1=table(data2016_2020$Infection_intensity[!is.na(data2016_2020$Breathing_rate)])

mod_br_para <- mod_br_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m1)), levels=c(paste0(x,"\nn=",m1))))
mod_br_para$lower_CI=c(NA,mod_br_para$predicted[1]-0.44,mod_br_para$predicted[1]-0.86,mod_br_para$predicted[1]-0.57,mod_br_para$predicted[1]-0.58)
mod_br_para$higher_CI=c(NA,mod_br_para$predicted[1]+0.40,mod_br_para$predicted[1]+0.16,mod_br_para$predicted[1]+0.19,mod_br_para$predicted[1]+0.55)

gg1_pred_para=ggplot(mod_br_para)+
  aes(as.factor(mod_br_para$x),mod_br_para$predicted)+
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Breathing rate")+
  geom_errorbar(aes(ymin=mod_br_para$lower_CI,ymax=mod_br_para$higher_CI),colour="black",size=2, width=.1)+
  # geom_errorbar(aes(ymin=mod_br_para$predicted-mod_br_para$std.error,ymax=mod_br_para$predicted+mod_br_para$std.error),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_br_para$higher_CI, na.rm=T)+0.2, xend=5, yend=max(mod_br_para$higher_CI, na.rm=T)+0.2))+
    geom_text(aes(x=3, y=max(mod_br_para$higher_CI, na.rm=T)+0.27),
              label="n.s.", size = 5)
```

## 2) Variation of body temperature according to Leucocytozoon Infection_intensity and presence

```{r  mixed model body temperature 2, warning=FALSE, message=F, echo=F}

# Model

lmer_bt_para=lmer(data= data2016_2020,body_temperature~Infection_intensity+Infection_intensity:Treatment+days_resample+Ambient_Temperature_AvgC+Age_in_days+Weight_g+Sex+Year+(1|Nest))

# Predicted values for post-treament parasitemia

mod_bt_para=get_model_data(lmer_bt_para,type='pred',terms="Infection_intensity") %>% 
   mutate(x=factor(c("0","1","2","3","4"), levels=c("0","1","2","3","4")))

# Table with sample sizes specific for body temperature change data

m2=table(data2016_2020$Infection_intensity[!is.na(data2016_2020$body_temperature)])

mod_bt_para <- mod_bt_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m2)), levels=c(paste0(x,"\nn=",m2))))
mod_bt_para$lower_CI=c(NA,mod_bt_para$predicted[1]-0.44,mod_bt_para$predicted[1]-0.72,mod_bt_para$predicted[1]-0.69,mod_bt_para$predicted[1]-1.45)
mod_bt_para$higher_CI=c(NA,mod_bt_para$predicted[1]+0.56,mod_bt_para$predicted[1]+0.29,mod_bt_para$predicted[1]+0.22,mod_bt_para$predicted[1]+(-0.23))

gg2_pred_para=ggplot(mod_bt_para)+
  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted)+
  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm=T), linetype = "dashed")+
  geom_errorbar(aes(ymin=mod_bt_para$lower_CI,ymax=mod_bt_para$higher_CI),colour="black",size=2, width=.1)+
  labs(x="", y="Body temperature")+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_bt_para$higher_CI, na.rm=T)+0.2, xend=5, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.2))+
    geom_text(aes(x=3, y=max(mod_bt_para$higher_CI, na.rm=T)+0.25),
              label="**", size = 8)+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_bt_para$higher_CI, na.rm=T)+0.2, xend=1, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.05))+
  geom_segment(size = .8,
                 aes(x=5, y=max(mod_bt_para$higher_CI, na.rm=T)+0.05, xend=5, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.2))
```

## 3) Variation of body condition according to **Leucocytozoon** Infection_intensity and presence

```{r mixed model body condition change 2, warning=FALSE, message=F, echo=F}

# Model

lmer_bc_para=lmer(data= data2016_2020,delta_body_condition~Infection_intensity+Infection_intensity:Treatment+days_resample+Age_in_days+Year+(1|Nest))

# Predicted values for post-treament parasitemia

mod_bc_para=get_model_data(lmer_bc_para,type='pred',terms="Infection_intensity") %>% 
   mutate(x=factor(c("0","1","2","3","4"), levels=c("0","1","2","3","4")))

# Table with sample sizes specific for body condition change data

m3=table(data2016_2020$Infection_intensity[!is.na(data2016_2020$delta_body_condition)])

mod_bc_para <- mod_bc_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m3)), levels=c(paste0(x,"\nn=",m3))))
mod_bc_para$lower_CI=c(NA,mod_bc_para$predicted[1]-0.04,mod_bc_para$predicted[1]-0.72,mod_bc_para$predicted[1]-0.53,mod_bc_para$predicted[1]-1.02)
mod_bc_para$higher_CI=c(NA,mod_bc_para$predicted[1]+0.76,mod_bc_para$predicted[1]+0.26,mod_bc_para$predicted[1]+0.22,mod_bc_para$predicted[1]+(-0.05))

gg3_pred_para=ggplot(mod_bc_para)+
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted)+
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Δ Body condition")+
  geom_errorbar(aes(ymin=mod_bc_para$lower_CI,ymax=mod_bc_para$higher_CI),colour="black",size=2, width=.1)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=-0.325843-1.6, xend=5, yend=-0.325843-1.6))+
    geom_text(aes(x=3, y=-0.325843-1.75),
              label="p=0.07", size = 5)+
  geom_segment(size = .8,
                 aes(x=1, y=-0.325843-1.45, xend=1, yend=-0.325843-1.6))+
  geom_segment(size = .8,
                 aes(x=5, y=-0.325843-1.6, xend=5, yend=-0.325843-1.45))

```

## 4) Variation of growth rate according to Leucocytozoon Infection_intensity and treatment:

```{r mixed model growth rate 2, warning=FALSE, message=F, echo=F}

# Model

lmer_gr_para=lmer(data= data2016_2020,Growth_rate~Infection_intensity+Infection_intensity:Treatment+days_resample+Sex+Age_in_days+Year+(1|Nest))

# Predicted values for post-treament parasitemia

mod_gr_para=get_model_data(lmer_gr_para,type='pred',terms="Infection_intensity") %>% 
   mutate(x=factor(c("0","1","2","3","4"), levels=c("0","1","2","3","4")))

# Table with sample sizes specific for growth rate data

m4=table(data2016_2020$Infection_intensity[!is.na(data2016_2020$Growth_rate)])

mod_gr_para <- mod_gr_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m4)), levels=c(paste0(x,"\nn=",m4))))
mod_gr_para$lower_CI=c(NA,mod_gr_para$predicted[1]-0.11,mod_gr_para$predicted[1]-0.79,mod_gr_para$predicted[1]-0.54,mod_gr_para$predicted[1]-0.89)
mod_gr_para$higher_CI=c(NA,mod_gr_para$predicted[1]+0.58,mod_gr_para$predicted[1]+0.06,mod_gr_para$predicted[1]+0.10,mod_gr_para$predicted[1]+0.04)

gg4_pred_para=ggplot(mod_gr_para)+
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted)+
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Growth rate")+
  geom_errorbar(aes(ymin=mod_gr_para$lower_CI,ymax=mod_gr_para$higher_CI),colour="black",size=2, width=.1)+
  # geom_errorbar(aes(ymin=mod_gr_para$predicted-mod_gr_para$std.error,ymax=mod_gr_para$predicted+mod_gr_para$std.error),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=mod_gr_para$predicted[1]-0.79-0.5, xend=5, yend=mod_gr_para$predicted[1]-0.79-0.5))+
    geom_text(aes(x=3, y=mod_gr_para$predicted[1]-0.79-0.63),
              label="p=0.09", size = 5)+
  geom_segment(size = .8,
                 aes(x=1, y=mod_gr_para$predicted[1]-0.79-0.35, xend=1, yend=mod_gr_para$predicted[1]-0.79-0.5))+
  geom_segment(size = .8,
                 aes(x=5, y=mod_gr_para$predicted[1]-0.79-0.5, xend=5, yend=mod_gr_para$predicted[1]-0.79-0.3))

```

# Summary four models

```{r summary}

# Figure 5

gg1_pred_para+gg2_pred_para+gg3_pred_para+gg4_pred_para + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

# Table 4

sjPlot::tab_model(lmer_br_para,lmer_bt_para,lmer_bc_para,lmer_gr_para,
                  show.ci50 = T ,
                  show.stat = T,
                  string.stat = "t",
                  p.val = "kr",
                  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
                  file = "./table_results/table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")

```

### Host health to parasitemia 
```{r, warning=F,message=F}

tol_resdata=data2016_2020

tol_resdata$Infection_intensity=as.numeric(tol_resdata$Infection_intensity)
tol_resdata$Diff_Inf_Class=factor(tol_resdata$Diff_Inf_Class, levels=c("Increase","Peak","Decrease"))

# First sampling parasitemia

## Same with delta body condition

tol_resdata$Infection_intensity.1=as.numeric(tol_resdata$Infection_intensity.1)
tolres_deltamod=lm(delta_body_condition~Infection_intensity.1*Diff_Inf_Class, data=tol_resdata)

# comparison of slopes among infection stages

lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.1, var="Infection_intensity.1")

contrast(lms_delta,"pairwise")

tolre_deltasum=summary(lms_delta)

# comparison of slopes to zero

summary(lms_delta, infer=T)

# body condition change - first infection intensity

tolres_delta_first=ggplot(data =data2016_2020[! data2016_2020$Infection_intensity.1 %in% NA & ! data2016_2020$Diff_Inf_Class %in% c(NA,"Uninfected"),], aes(y=delta_body_condition,x=as.numeric(Infection_intensity.1),col=Diff_Inf_Class))+
    geom_jitter(size=3, alpha=0.5)+
    geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
    labs(title = "First sampling", y="Body condition change",x="Parasitemia \n at first sampling", col='Infection stages')+
    # scale_x_continuous(breaks=seq(1,5,1),labels=c("0","1","2","3","4"))+
    scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
    theme_classic()+
    theme(legend.position = "none", axis.text = element_text(size=16), axis.title = element_text(size=18))

# Second sampling parasitemia

## with delta body condition

tolres_deltamod=lm(delta_body_condition~Infection_intensity*Diff_Inf_Class, data=tol_resdata)

## comparison of slopes among infection stages

lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity, var="Infection_intensity")

contrast(lms_delta,"pairwise")

tolre_deltasum=summary(lms_delta)

## comparison of slopes to zero

summary(lms_delta, infer=T)

## plot

tolre_sum=tolre_sum[!tolre_sum$Diff_Inf_Class %in% "Uninfected",]

gtolre=ggplot(tolre_sum)+
  aes(Diff_Inf_Class,Infection_intensity.trend)+
  geom_point(size=6)+
  geom_errorbar(ymin=tolre_sum$Infection_intensity.trend-tolre_sum$SE,ymax=tolre_sum$Infection_intensity.trend+tolre_sum$SE,size=5, width=0)+
  geom_errorbar(ymin=tolre_sum$lower.CL,ymax=tolre_sum$upper.CL,size=2, width=0.1)+
  ylim(-120,20)

tolres=ggplot(data =data2016_2020[! data2016_2020$Infection_intensity %in% c(NA,0) & ! data2016_2020$Diff_Inf_Class %in% NA,], aes(y=body_condition.2,x=as.numeric(Infection_intensity),col=Diff_Inf_Class))+
  geom_jitter(size=3, alpha=0.5)+
  geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
  labs(y="Body condition \n at second sampling",x="Parasitemia \n at second sampling", col='Infection stages')+
  scale_x_continuous(breaks=seq(2,5,1),labels=c("1","2","3","4"))+
  scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
  theme_classic()+
  theme(legend.text = element_text(size=19),legend.title = element_text(size=22), axis.text = element_text(size=16), axis.title = element_text(size=18))

# body condition change - second infection intensity

tolres_delta=ggplot(data =data2016_2020[! data2016_2020$Infection_intensity %in% c(NA,0) & ! data2016_2020$Diff_Inf_Class %in% NA,], aes(y=delta_body_condition,x=as.numeric(Infection_intensity),col=Diff_Inf_Class))+
    geom_jitter(size=3, alpha=0.5)+
    geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
    labs(title="Second sampling",y="Body condition change",x="Parasitemia \n at second sampling", col='Infection stages')+
    scale_x_continuous(breaks=seq(2,5,1),labels=c("1","2","3","4"))+
    scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
    theme_classic()+
    theme(legend.text = element_text(size=19),legend.title = element_text(size=22), axis.text = element_text(size=16), axis.title = element_text(size=18))

# Figure 3

tolres_delta_first+tolres_delta+ plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

```

### 2022-01-24 MS_physiology_infection.Rmd
Add files via upload

@@
   scale_fill_manual(values=c("#D0D0D0","#A8A8A8"))+
-  theme(axis.title.x = element_blank(), strip.text = element_text(size=14, face="bold"),legend.text = element_text(size=12), legend.title = element_text(size=14),axis.title.y=element_text(size=14, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=12))
+  theme(axis.title.x = element_blank(), strip.text = element_text(size=16, face="bold"),legend.text = element_text(size=14), legend.title = element_text(size=16),axis.title.y=element_text(size=18, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=16))
 
@@
   theme_classic()+
-  theme(axis.title.x = element_blank(), legend.text = element_text(size=12), legend.title = element_text(size=14), axis.title.y=element_text(size=16, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=12), plot.margin = unit(c(0,0,0,30), "pt"))
+  theme(axis.title.x = element_blank(), legend.text = element_text(size=16), legend.title = element_text(size=16), axis.title.y=element_text(size=18, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=16), plot.margin = unit(c(0,0,0,30), "pt"))
 
@@
 
-### Host health to parasitemia 
+# Host health to parasitemia 
 ```{r, warning=F,message=F}
@@
 ```
+
+# Supplementary figure
+
+```{r}
+
+gg1=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
+  aes(Diff_Inf_Class,Breathing_rate)+
+  geom_hline(yintercept = mean(data2016_2020$Breathing_rate, na.rm=T), linetype = "dashed")+
+  labs(x="", y="Breathing rate (z-transformed)")+
+  geom_jitter(color ="lightgrey", size=2, width=.3)+
+  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
+               size=2.8 , width=0.05, show.legend = FALSE, 
+               fun.max = function(x) mean(x) + sd(x),
+               fun.min = function(x) mean(x) - sd(x))+
+  stat_summary(fun=mean, colour="black", geom="point", 
+               size=5 ,show.legend = FALSE)+
+  stat_n_text()+
+  theme_classic()+
+  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+
+gg2=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
+  aes(Diff_Inf_Class,body_temperature)+
+  geom_hline(yintercept = mean(data2016_2020$body_temperature, na.rm=T), linetype = "dashed")+
+  labs(x="", y="Body temperature (z-transformed)")+
+  geom_jitter(color ="lightgrey", size=2, width=.3)+
+  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
+               size=2.8 , width=0.05, show.legend = FALSE, 
+               fun.max = function(x) mean(x) + sd(x),
+               fun.min = function(x) mean(x) - sd(x))+
+  stat_summary(fun=mean, colour="black", geom="point", 
+               size=5 ,show.legend = FALSE)+
+  stat_n_text()+
+  theme_classic()+
+  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+
+gg3=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
+  aes(Diff_Inf_Class,delta_body_condition)+
+  geom_hline(yintercept = mean(data2016_2020$delta_body_condition, na.rm=T), linetype = "dashed")+
+  labs(x="", y="Body condition (z-transformed)")+
+  geom_jitter(color ="lightgrey", size=2, width=.3)+
+  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
+               size=2.8 , width=0.05, show.legend = FALSE, 
+               fun.max = function(x) mean(x) + sd(x),
+               fun.min = function(x) mean(x) - sd(x))+
+  stat_summary(fun=mean, colour="black", geom="point", 
+               size=5 ,show.legend = FALSE)+
+  stat_n_text()+
+  theme_classic()+
+  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+
+gg4=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
+  aes(Diff_Inf_Class,Growth_rate)+
+  geom_hline(yintercept = mean(data2016_2020$Growth_rate, na.rm=T), linetype = "dashed")+
+  labs(x="", y="Growth rate (z-transformed)")+
+  geom_jitter(color ="lightgrey", size=2, width=.3)+
+  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
+               size=2.8 , width=0.05, show.legend = FALSE, 
+               fun.max = function(x) mean(x) + sd(x),
+               fun.min = function(x) mean(x) - sd(x))+
+  stat_summary(fun=mean, colour="black", geom="point", 
+               size=5 ,show.legend = FALSE)+
+  stat_n_text()+
+  theme_classic()+
+  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+
+# Figure S1
+
+gg1+gg2+gg3+gg4 + plot_annotation(tag_levels = 'A')& 
+  theme(plot.tag = element_text(size = 16, face = "bold"))
+
+```

### 2022-02-07 MS_physiology_infection.Rmd
Add files via upload

@@
 data2016_2020$Prevalence=as.factor(data2016_2020$Prevalence)
-data2016_2020$Breathing_rate=scale(as.numeric(data2016_2020$Breathing_rate))
+data2016_2020$Breathing_rate=as.numeric(data2016_2020$Breathing_rate)
 data2016_2020$Sex=as.factor(data2016_2020$Sex)
 data2016_2020$Sampling_rank=as.factor(data2016_2020$Sampling_rank)
-data2016_2020$Weight_g=as.numeric(data2016_2020$Weight.2)
+data2016_2020$Weight_g=scale(as.numeric(data2016_2020$Weight.2))
 data2016_2020$Wing_cm=as.numeric(data2016_2020$Wing)
-data2016_2020$body_temperature=scale(as.numeric(data2016_2020$body_temperature))
-data2016_2020$delta_body_condition=scale(as.numeric(data2016_2020$delta_body_condition))
-data2016_2020$Ambient_Temperature_AvgC=as.numeric(data2016_2020$TemperatureAvgC)
+data2016_2020$body_temperature=as.numeric(data2016_2020$body_temperature)
+data2016_2020$delta_body_condition=as.numeric(data2016_2020$delta_body_condition)
+data2016_2020$Ambient_Temperature_AvgC=scale(as.numeric(data2016_2020$TemperatureAvgC))
 data2016_2020$Treatment=as.factor(data2016_2020$Treatment)
 data2016_2020$Year=as.factor(data2016_2020$Year)
-data2016_2020$Growth_rate=scale(as.numeric(data2016_2020$Growth_rate))
-data2016_2020$Growth_rate=scale(as.numeric(data2016_2020$Growth_rate_unlog))
+data2016_2020$Growth_rate=as.numeric(data2016_2020$Growth_rate_unlog)
+data2016_2020$days_resample=scale(data2016_2020$days_resample)
+data2016_2020$Age_in_days=scale(as.numeric(data2016_2020$Age_in_days))
 
@@
 
+mean_infint=data.frame(Sampling_rank=factor(c(rep("1",length(data2016_2020$Sampling_rank)),as.character(data2016_2020$Sampling_rank)),levels=c("1","2"), labels = c("Pre-treatment","Post-treatment")),Infection_intensity=as.numeric(c(as.character(data2016_2020$Infection_intensity.1),as.character(data2016_2020$Infection_intensity))),Treatment=factor(c(as.character(rep(data2016_2020$Treatment,2))),levels = c("Control","Malarone")))
+
 # Figure 2b
 
-treatment_meaninf_changes=ggplot(tab_mean)+
-  aes(Timepoint,Mean_infection_intensity,group=Treatment)+
+treatment_meaninf_changes=ggplot(mean_infint)+
+  aes(Sampling_rank,Infection_intensity,group=Treatment, fill=Treatment)+
   geom_vline(xintercept = "Pre-treatment", linetype = "dashed", color='darkgrey')+
@@
   labs(y="Mean infection intensity")+
-  ylim(c(0,3))+
-  geom_line(aes(color=Treatment), size=2)+
-  geom_errorbar(ymin=tab_mean$Mean_infection_intensity-tab_mean$se_inf_int, ymax=tab_mean$Mean_infection_intensity+tab_mean$se_inf_int,colour="black",
-               size=1.5 , width=0.05)+
-  stat_summary(fun=mean, colour="black", geom="point", 
-               size=5)+ 
+  # ylim(c(0,3))+
+  geom_point(aes(colour=Treatment),position=position_jitterdodge(jitter.width = 0.2, jitter.height = 0.5))+  # position=position_jitterdodge()
+  # geom_line(aes(group=Treatment,color=Treatment, fill=Treatment),size=2)+
+  stat_summary(fun=mean, geom="line",size=2,color=c("lightgrey","black","black","lightgrey"))+
+  stat_summary(fun=mean, geom="point",size=5)+
+  stat_summary(geom="errorbar", width=0.04, size=2)+
   scale_color_manual(values=c("lightgrey","black"))+
@@
 
-treatment_prevalence_changes+treatment_meaninf_changes+ plot_annotation(tag_levels = 'A')& 
+Fig2=treatment_prevalence_changes+treatment_meaninf_changes+ plot_annotation(tag_levels = 'A')& 
   theme(plot.tag = element_text(size = 16, face = "bold"))
+
+ggsave(Fig2,filename = "./Figs/efficiency_malarone.png",units = "px", width = 6000, height = 3000)
 
@@
   labs(x="", y="Breathing rate")+
-  ylim(c(min(mod_br$conf.low)-0.3,max(mod_br$conf.high)+0.5))+
+  ylim(c(min(mod_br$conf.low)-1.5,max(mod_br$conf.high)+1.5))+
   geom_errorbar(aes(ymin=mod_br$conf.low,ymax=mod_br$conf.high),colour="black",size=2, width=.1)+
@@
   geom_segment(size = .8,
-  aes(x=1, y=max(mod_br$conf.high)+0.3, xend=4, yend=max(mod_br$conf.high)+0.3))+
-  geom_text(aes(x=2.5, y=max(mod_br$conf.high)+0.42),
+  aes(x=1, y=max(mod_br$conf.high)+1, xend=4, yend=max(mod_br$conf.high)+1))+
+  geom_text(aes(x=2.5, y=max(mod_br$conf.high)+1.5),
   label="n.s.", size = 5)
@@
   geom_segment(size = .8,
-                 aes(x=1, y=0.7, xend=4, yend=0.7))+
-    geom_text(aes(x=2.5, y=0.78),
+                 aes(x=1, y=40.6, xend=4, yend=40.6))+
+    geom_text(aes(x=2.5, y=40.7),
               label="n.s.", size = 5)
@@
 
-lmer_bc=lmer(data= data2016_2020,delta_body_condition~Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample+Age_in_days+Year+(1|Nest))
+lmer_bc=lmer(data= data2016_2020,delta_body_condition~Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample+Age_in_days+Sex+Year+(1|Nest))
 
@@
   geom_segment(size = .8,
-                 aes(x=1, y=max(mod_bc$conf.high)+0.3, xend=4, yend=max(mod_bc$conf.high)+0.3))+
-    geom_text(aes(x=2.5, y=max(mod_bc$conf.high)+0.4),
+                 aes(x=1, y=max(mod_bc$conf.high)+17, xend=4, yend=max(mod_bc$conf.high)+17))+
+    geom_text(aes(x=2.5, y=max(mod_bc$conf.high)+23),
               label="n.s.", size = 5)
@@
   geom_segment(size = .8,
-                 aes(x=1, y=max(mod_gr$conf.high)+0.2, xend=4, yend=max(mod_gr$conf.high)+0.2))+
-    geom_text(aes(x=2.5, y=max(mod_gr$conf.high)+0.3),
+                 aes(x=1, y=max(mod_gr$conf.high)+1.2, xend=4, yend=max(mod_gr$conf.high)+1.2))+
+    geom_text(aes(x=2.5, y=max(mod_gr$conf.high)+2),
               label="n.s.", size = 5)
@@
 
-gg1_pred+gg2_pred+gg3_pred+gg4_pred + plot_annotation(tag_levels = 'A')& 
+fig4=gg1_pred+gg2_pred+gg3_pred+gg4_pred + plot_annotation(tag_levels = 'A')& 
   theme(plot.tag = element_text(size = 16, face = "bold"))
+
+ggsave(fig4,filename = "./Figs/predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)
 
@@
   mutate(x = factor(c(paste0(x,"\nn=",m1)), levels=c(paste0(x,"\nn=",m1))))
-mod_br_para$lower_CI=c(NA,mod_br_para$predicted[1]-0.44,mod_br_para$predicted[1]-0.86,mod_br_para$predicted[1]-0.57,mod_br_para$predicted[1]-0.58)
-mod_br_para$higher_CI=c(NA,mod_br_para$predicted[1]+0.40,mod_br_para$predicted[1]+0.16,mod_br_para$predicted[1]+0.19,mod_br_para$predicted[1]+0.55)
+mod_br_para$lower_CI=c(31.11, mod_br_para$predicted[1]-2.96, mod_br_para$predicted[1]-6.49,mod_br_para$predicted[1]-4.67, mod_br_para$predicted[1]-4.63)
+mod_br_para$higher_CI=c(41.42,mod_br_para$predicted[1]+3.90,mod_br_para$predicted[1]+1.75,mod_br_para$predicted[1]+1.46,mod_br_para$predicted[1]+4.45)
 
@@
   geom_segment(size = .8,
-                 aes(x=1, y=max(mod_br_para$higher_CI, na.rm=T)+0.2, xend=5, yend=max(mod_br_para$higher_CI, na.rm=T)+0.2))+
-    geom_text(aes(x=3, y=max(mod_br_para$higher_CI, na.rm=T)+0.27),
+                 aes(x=1, y=max(mod_br_para$higher_CI, na.rm=T)+1.2, xend=5, yend=max(mod_br_para$higher_CI, na.rm=T)+1.2))+
+    geom_text(aes(x=3, y=max(mod_br_para$higher_CI, na.rm=T)+2),
               label="n.s.", size = 5)
@@
   mutate(x = factor(c(paste0(x,"\nn=",m2)), levels=c(paste0(x,"\nn=",m2))))
-mod_bt_para$lower_CI=c(NA,mod_bt_para$predicted[1]-0.44,mod_bt_para$predicted[1]-0.72,mod_bt_para$predicted[1]-0.69,mod_bt_para$predicted[1]-1.45)
-mod_bt_para$higher_CI=c(NA,mod_bt_para$predicted[1]+0.56,mod_bt_para$predicted[1]+0.29,mod_bt_para$predicted[1]+0.22,mod_bt_para$predicted[1]+(-0.23))
+mod_bt_para$lower_CI=c(39.40,mod_bt_para$predicted[1]-0.40,mod_bt_para$predicted[1]-0.60,mod_bt_para$predicted[1]-0.65,mod_bt_para$predicted[1]-1.38)
+mod_bt_para$higher_CI=c(40.40,mod_bt_para$predicted[1]+0.55,mod_bt_para$predicted[1]+0.36,mod_bt_para$predicted[1]+0.19,mod_bt_para$predicted[1]+(-0.24))
 
@@
 
-lmer_bc_para=lmer(data= data2016_2020,delta_body_condition~Infection_intensity+Infection_intensity:Treatment+days_resample+Age_in_days+Year+(1|Nest))
+lmer_bc_para=lmer(data= data2016_2020,delta_body_condition~Infection_intensity+Infection_intensity:Treatment+days_resample+Age_in_days+Sex+Year+(1|Nest))
 
@@
   mutate(x = factor(c(paste0(x,"\nn=",m3)), levels=c(paste0(x,"\nn=",m3))))
-mod_bc_para$lower_CI=c(NA,mod_bc_para$predicted[1]-0.04,mod_bc_para$predicted[1]-0.72,mod_bc_para$predicted[1]-0.53,mod_bc_para$predicted[1]-1.02)
-mod_bc_para$higher_CI=c(NA,mod_bc_para$predicted[1]+0.76,mod_bc_para$predicted[1]+0.26,mod_bc_para$predicted[1]+0.22,mod_bc_para$predicted[1]+(-0.05))
+mod_bc_para$lower_CI=c(-65.99,mod_bc_para$predicted[1]-5.71,mod_bc_para$predicted[1]-53.27,mod_bc_para$predicted[1]-37.05,mod_bc_para$predicted[1]-71.88)
+mod_bc_para$higher_CI=c(25.59,mod_bc_para$predicted[1]+51.67,mod_bc_para$predicted[1]+16.43,mod_bc_para$predicted[1]+16.17,mod_bc_para$predicted[1]+4.09)
 
@@
   geom_segment(size = .8,
-                 aes(x=1, y=-0.325843-1.6, xend=5, yend=-0.325843-1.6))+
-    geom_text(aes(x=3, y=-0.325843-1.75),
-              label="p=0.07", size = 5)+
+                 aes(x=1, y=-105, xend=5, yend=-105))+
+    geom_text(aes(x=3, y=-110),
+              label="p=0.08", size = 5)+
   geom_segment(size = .8,
-                 aes(x=1, y=-0.325843-1.45, xend=1, yend=-0.325843-1.6))+
+                 aes(x=1, y=-105, xend=1, yend=-105+5))+
   geom_segment(size = .8,
-                 aes(x=5, y=-0.325843-1.6, xend=5, yend=-0.325843-1.45))
+                 aes(x=5, y=-105, xend=5, yend=-105+5))
 
@@
   mutate(x = factor(c(paste0(x,"\nn=",m4)), levels=c(paste0(x,"\nn=",m4))))
-mod_gr_para$lower_CI=c(NA,mod_gr_para$predicted[1]-0.11,mod_gr_para$predicted[1]-0.79,mod_gr_para$predicted[1]-0.54,mod_gr_para$predicted[1]-0.89)
-mod_gr_para$higher_CI=c(NA,mod_gr_para$predicted[1]+0.58,mod_gr_para$predicted[1]+0.06,mod_gr_para$predicted[1]+0.10,mod_gr_para$predicted[1]+0.04)
+mod_gr_para$lower_CI=c(11.44,mod_gr_para$predicted[1]-2.22,mod_gr_para$predicted[1]-10.47,mod_gr_para$predicted[1]-6.60,mod_gr_para$predicted[1]-11.39)
+mod_gr_para$higher_CI=c(25.14,mod_gr_para$predicted[1]+7.08,mod_gr_para$predicted[1]+0.92,mod_gr_para$predicted[1]+1.91,mod_gr_para$predicted[1]+0.89)
 
@@
   geom_segment(size = .8,
-                 aes(x=1, y=mod_gr_para$predicted[1]-0.79-0.5, xend=5, yend=mod_gr_para$predicted[1]-0.79-0.5))+
-    geom_text(aes(x=3, y=mod_gr_para$predicted[1]-0.79-0.63),
+                 aes(x=1, y=5, xend=5, yend=5))+
+    geom_text(aes(x=3, y=5-0.63),
               label="p=0.09", size = 5)+
   geom_segment(size = .8,
-                 aes(x=1, y=mod_gr_para$predicted[1]-0.79-0.35, xend=1, yend=mod_gr_para$predicted[1]-0.79-0.5))+
+                 aes(x=1, y=5, xend=1, yend=5+0.5))+
   geom_segment(size = .8,
-                 aes(x=5, y=mod_gr_para$predicted[1]-0.79-0.5, xend=5, yend=mod_gr_para$predicted[1]-0.79-0.3))
+                 aes(x=5, y=5, xend=5, yend=5+0.5))
 
@@
 
-gg1_pred_para+gg2_pred_para+gg3_pred_para+gg4_pred_para + plot_annotation(tag_levels = 'A')& 
+fig5=gg1_pred_para+gg2_pred_para+gg3_pred_para+gg4_pred_para + plot_annotation(tag_levels = 'A')& 
   theme(plot.tag = element_text(size = 16, face = "bold"))
+
+ggsave(fig5,filename = "./Figs/predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)
 
@@
 
-# First sampling parasitemia
-
-## Same with delta body condition
-
-tol_resdata$Infection_intensity.1=as.numeric(tol_resdata$Infection_intensity.1)
-tolres_deltamod=lm(delta_body_condition~Infection_intensity.1*Diff_Inf_Class, data=tol_resdata)
-
-# comparison of slopes among infection stages
-
-lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.1, var="Infection_intensity.1")
-
-contrast(lms_delta,"pairwise")
-
-tolre_deltasum=summary(lms_delta)
-
-# comparison of slopes to zero
-
-summary(lms_delta, infer=T)
-
-# body condition change - first infection intensity
-
-tolres_delta_first=ggplot(data =data2016_2020[!
+# # First sampling parasitemia
+# 
+# ## Same with delta body condition
+# 
+# tol_resdata$Infection_intensity.1=as.numeric(tol_resdata$Infection_intensity.1)
+# tolres_deltamod=lm(body_condition.1~Infection_intensity.1*Diff_Inf_Class, data=tol_resdata)
+# 
+# # comparison of slopes among infection stages 
+# 
+# lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.1, var="Infection_intensity.1")
+# 
+# contrast(lms_delta,"pairwise")
+# 
+# tolre_deltasum=summary(lms_delta)
+# 
+# # comparison of slopes to zero
+# 
+# summary(lms_delta, infer=T)
+# 
+# # body condition change - first infection intensity
+# 
+# tolres_delta_first=ggplot(data =data2016_2020[!
 data2016_2020$Infection_intensity.1 %in% NA & !
-data2016_2020$Diff_Inf_Class %in% c(NA,"Uninfected"),], aes(y=delta_body_condition,x=as.numeric(Infection_intensity.1),col=Diff_Inf_Class))+
-    geom_jitter(size=3, alpha=0.5)+
-    geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
-    labs(title = "First sampling", y="Body condition change",x="Parasitemia \n at first sampling", col='Infection stages')+
-    # scale_x_continuous(breaks=seq(1,5,1),labels=c("0","1","2","3","4"))+
-    scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
-    theme_classic()+
-    theme(legend.position = "none", axis.text = element_text(size=16), axis.title = element_text(size=18))
+data2016_2020$Diff_Inf_Class %in% c(NA,"Uninfected"),], aes(y=body_condition.1,x=as.numeric(Infection_intensity.1),col=Diff_Inf_Class))+
+#     geom_jitter(size=3, alpha=0.5)+
+#     geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
+#     labs(title = "First sampling", y="Body condition change",x="Parasitemia \n at first sampling", col='Infection stages')+
+#     # scale_x_continuous(breaks=seq(1,5,1),labels=c("0","1","2","3","4"))+
+#     scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
+#     theme_classic()+
+#     theme(legend.position = "none", axis.text = element_text(size=16), axis.title = element_text(size=18))
 
@@
 
-tolres_deltamod=lm(delta_body_condition~Infection_intensity*Diff_Inf_Class, data=tol_resdata)
+tolres_deltamod=lm(body_condition.2~Infection_intensity*Diff_Inf_Class, data=tol_resdata)
 
@@
 
-## plot
-
-tolre_sum=tolre_sum[!tolre_sum$Diff_Inf_Class %in% "Uninfected",]
-
-gtolre=ggplot(tolre_sum)+
-  aes(Diff_Inf_Class,Infection_intensity.trend)+
-  geom_point(size=6)+
-  geom_errorbar(ymin=tolre_sum$Infection_intensity.trend-tolre_sum$SE,ymax=tolre_sum$Infection_intensity.trend+tolre_sum$SE,size=5, width=0)+
-  geom_errorbar(ymin=tolre_sum$lower.CL,ymax=tolre_sum$upper.CL,size=2, width=0.1)+
-  ylim(-120,20)
-
-tolres=ggplot(data =data2016_2020[!
+# ## plot
+# 
+# tolres=ggplot(data =data2016_2020[!
 data2016_2020$Infection_intensity %in% c(NA,0) & !
 data2016_2020$Diff_Inf_Class %in% NA,], aes(y=body_condition.2,x=as.numeric(Infection_intensity),col=Diff_Inf_Class))+
-  geom_jitter(size=3, alpha=0.5)+
-  geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
-  labs(y="Body condition \n at second sampling",x="Parasitemia \n at second sampling", col='Infection stages')+
-  scale_x_continuous(breaks=seq(2,5,1),labels=c("1","2","3","4"))+
-  scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
-  theme_classic()+
-  theme(legend.text = element_text(size=19),legend.title = element_text(size=22), axis.text = element_text(size=16), axis.title = element_text(size=18))
+#   geom_jitter(size=3, alpha=0.5)+
+#   geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
+#   labs(y="Body condition \n at second sampling",x="Parasitemia \n at second sampling", col='Infection stages')+
+#   scale_x_continuous(breaks=seq(2,5,1),labels=c("1","2","3","4"))+
+#   scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
+#   theme_classic()+
+#   theme(legend.text = element_text(size=19),legend.title = element_text(size=22), axis.text = element_text(size=16), axis.title = element_text(size=18))
 
@@
 
-tolres_delta=ggplot(data =data2016_2020[!
+tolres=ggplot(data =data2016_2020[!
 data2016_2020$Infection_intensity %in% c(NA,0) & !
@@
     geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
-    labs(title="Second sampling",y="Body condition change",x="Parasitemia \n at second sampling", col='Infection stages')+
+    labs(y="Body condition change",x="Parasitemia \n at second sampling", col='Infection stages')+
     scale_x_continuous(breaks=seq(2,5,1),labels=c("1","2","3","4"))+
@@
 
-tolres_delta_first+tolres_delta+ plot_annotation(tag_levels = 'A')& 
+fig3=tolres + 
   theme(plot.tag = element_text(size = 16, face = "bold"))
 
+ggsave(fig3,filename = "./Figs/delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
 ```

### 2022-02-10 MS_physiology_infection.Rmd
Add files via upload

@@
 
+### Setting classes of variables
+
 data2016_2020$Nest=as.factor(data2016_2020$Nest)
@@
 
+# Filtering non-applicable infection change
+
+data2016_2020=data2016_2020[!is.na(data2016_2020$Diff_Inf_Class),]
+
 ```
 
-**Results**
+**Analyses**
 
@@
 
-## plotting count of infected / uninfected nestlings across treatments
+## Plotting count of infected / uninfected nestlings across treatments
 
@@
 
-## plotting mean infection intensity values of nestlings across treatments
-
-mean_inf_int=c(mean(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Control"])), na.rm=T),mean(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Control"])), na.rm=T),mean(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Malarone"])), na.rm=T),mean(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Malarone"])), na.rm=T))
-
-se_inf_int=c(se(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Control"]))),se(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Control"]))),se(as.numeric(as.character(data2016_2020$Infection_intensity.1[data2016_2020$Treatment %in% "Malarone"]))), se(as.numeric(as.character(data2016_2020$Infection_intensity[data2016_2020$Treatment %in% "Malarone"]))))
-
-tab_mean=data.frame(Timepoint=c("Pre-treatment","Post-treatment","Pre-treatment","Post-treatment"),Mean_infection_intensity=mean_inf_int,se_inf_int=se_inf_int,Treatment=c("Control","Control","Malarone","Malarone"))
-
-tab_mean$Timepoint=factor(tab_mean$Timepoint,levels = c("Pre-treatment","Post-treatment"))
+## Plotting mean infection intensity values of nestlings across treatments
 
@@
 treatment_meaninf_changes=ggplot(mean_infint)+
-  aes(Sampling_rank,Infection_intensity,group=Treatment, fill=Treatment)+
+  aes(Sampling_rank,Infection_intensity, group=Treatment)+
   geom_vline(xintercept = "Pre-treatment", linetype = "dashed", color='darkgrey')+
@@
   labs(y="Mean infection intensity")+
-  # ylim(c(0,3))+
-  geom_point(aes(colour=Treatment),position=position_jitterdodge(jitter.width = 0.2, jitter.height = 0.5))+  # position=position_jitterdodge()
+  geom_point(aes(colour=Treatment),position=position_jitterdodge(jitter.height = 0.1))+  #jitter.width = 0.2, jitter.height = 0.5) position=position_jitterdodge()
   # geom_line(aes(group=Treatment,color=Treatment, fill=Treatment),size=2)+
@@
   stat_summary(fun=mean, geom="point",size=5)+
-  stat_summary(geom="errorbar", width=0.04, size=2)+
+  stat_summary(fun.data=mean_se, geom="errorbar", width=0.04, size=2)+
   scale_color_manual(values=c("lightgrey","black"))+
@@
 
-# Mean infection intensity
+# Testing for difference in mean infection intensity between Pre and Post treatment
 
@@
 
-# Testing for difference in infection intensity in malarone treated nestlings before versus after treatment
+first=mean_before_after[mean_before_after$Timepoint %in% "Pre-treatment",]
+
+## Pre-treatment difference in parasitic load between Treatments
+
+perm.t.test(as.numeric(as.character(first$Infection_intensity))~first$Treatment)
+
+sd(first$Infection_intensity[first$Treatment %in% "Control"])
+
+## In malarone treated nestlings
 
@@
 
-# Testing for difference in infection intensity in control nestlings before versus after treatment
+# In control nestlings
 
 perm.t.test(as.numeric(as.character(ctrl$Infection_intensity))~ctrl$Timepoint)
+
 ```
@@
 
-```{r, echo=F}
+# Infection stages as explanatory variable
 
-# Filtering non-applicable infection change
-
-data2016_2020=data2016_2020[!is.na(data2016_2020$Diff_Inf_Class),]
-
-```
-
-## Summary sample sizes data
-
-```{r}
-#Summary of sample size across years
-
-table(data2016_2020$Year)
-
-### Number samples across infection stages
-
-table(data2016_2020$Diff_Inf_Class)
-
-### Average days between first and second sample
-
-mean(data2016_2020$days_resample)
-
-sd(data2016_2020$days_resample)
-
-range(data2016_2020$days_resample)
-
-### table infection prevalence in nestlings
-
-table(data2016_2020$Prevalence)
-
-```
-
-# Infection stages as response variable
-
-## 1) Variation of breathing rate according to infection stage
+## Breathing rate
 
@@
 
+# Plotting predicted values across infection stages
+
 gg1_pred=ggplot(mod_br)+
@@
 
-## 2) Variation of body temperature according to infection stage
+## Body temperature
 
@@
 
+# Plotting predicted values across infection stages
+
 gg2_pred=ggplot(mod_bt)+
@@
 
-## 3) Variation of body condition according to infection stages
+## Body condition change
 
@@
 
-# Plot of predicted values of body condition change among infection stages
+# Plotting predicted values across infection stages
 
@@
 
-## 4) Variation of growth rate according to infection stages
+## Growth rate
 
@@
   mutate(x = factor(c(paste0(x,"\nn=",n4)), levels=c(paste0(x,"\nn=",n4))))
+
+# Plotting predicted values across infection stages
 
@@
 
-# Parasitemia as response variable
+# Parasitemia as explanatory variable
 
-## 1) Variation of breathing rate according to Leucocytozoon increase, Peak or increase infection intensity
+## Breathing rate
 
@@
 mod_br_para$higher_CI=c(41.42,mod_br_para$predicted[1]+3.90,mod_br_para$predicted[1]+1.75,mod_br_para$predicted[1]+1.46,mod_br_para$predicted[1]+4.45)
+mod_br_para$se=c(2.61,1.74,2.09,1.56,2.31)
+
+# Plotting predicted values across infection intensities
 
@@
   geom_errorbar(aes(ymin=mod_br_para$lower_CI,ymax=mod_br_para$higher_CI),colour="black",size=2, width=.1)+
-  # geom_errorbar(aes(ymin=mod_br_para$predicted-mod_br_para$std.error,ymax=mod_br_para$predicted+mod_br_para$std.error),size=8,colour=wes_palette("Zissou1",5), width=0,)+
+  geom_errorbar(aes(ymin=mod_br_para$predicted-mod_br_para$se,ymax=mod_br_para$predicted+mod_br_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
   geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
@@
 
-## 2) Variation of body temperature according to Leucocytozoon Infection_intensity and presence
+## Body temperature
 
@@
 mod_bt_para$higher_CI=c(40.40,mod_bt_para$predicted[1]+0.55,mod_bt_para$predicted[1]+0.36,mod_bt_para$predicted[1]+0.19,mod_bt_para$predicted[1]+(-0.24))
+mod_bt_para$se=c(0.23,0.24,0.24,0.21,0.29)
+
+# Plotting predicted values across infection intensities
 
@@
   geom_errorbar(aes(ymin=mod_bt_para$lower_CI,ymax=mod_bt_para$higher_CI),colour="black",size=2, width=.1)+
+  geom_errorbar(aes(ymin=mod_bt_para$predicted-mod_bt_para$se,ymax=mod_bt_para$predicted+mod_bt_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
   labs(x="", y="Body temperature")+
@@
 
-## 3) Variation of body condition according to **Leucocytozoon** Infection_intensity and presence
+## Body condition change
 
@@
 mod_bc_para$higher_CI=c(25.59,mod_bc_para$predicted[1]+51.67,mod_bc_para$predicted[1]+16.43,mod_bc_para$predicted[1]+16.17,mod_bc_para$predicted[1]+4.09)
+mod_bc_para$se=c(23.20,14.57,17.69,13.51,19.29)
+
+# Plotting predicted values across infection intensities
 
@@
   geom_errorbar(aes(ymin=mod_bc_para$lower_CI,ymax=mod_bc_para$higher_CI),colour="black",size=2, width=.1)+
+  geom_errorbar(aes(ymin=mod_bc_para$predicted-mod_bc_para$se,ymax=mod_bc_para$predicted+mod_bc_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
   geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
@@
 
-## 4) Variation of growth rate according to Leucocytozoon Infection_intensity and treatment:
+## Growth rate
 
@@
 mod_gr_para$higher_CI=c(25.14,mod_gr_para$predicted[1]+7.08,mod_gr_para$predicted[1]+0.92,mod_gr_para$predicted[1]+1.91,mod_gr_para$predicted[1]+0.89)
+mod_gr_para$se=c(3.47,2.36,2.89,2.16,3.12)
+
+# Plotting predicted values across infection intensities
 
@@
   geom_errorbar(aes(ymin=mod_gr_para$lower_CI,ymax=mod_gr_para$higher_CI),colour="black",size=2, width=.1)+
-  # geom_errorbar(aes(ymin=mod_gr_para$predicted-mod_gr_para$std.error,ymax=mod_gr_para$predicted+mod_gr_para$std.error),size=8,colour=wes_palette("Zissou1",5), width=0,)+
+  geom_errorbar(aes(ymin=mod_gr_para$predicted-mod_gr_para$se,ymax=mod_gr_para$predicted+mod_gr_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
   geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
@@
                   show.ci50 = T ,
+                  show.se = T,
                   show.stat = T,
@@
 # Host health to parasitemia
+
 ```{r, warning=F,message=F}
@@
 
-# # First sampling parasitemia
-# 
-# ## Same with delta body condition
-# 
-# tol_resdata$Infection_intensity.1=as.numeric(tol_resdata$Infection_intensity.1)
-# tolres_deltamod=lm(body_condition.1~Infection_intensity.1*Diff_Inf_Class, data=tol_resdata)
-# 
-# # comparison of slopes among infection stages 
-# 
-# lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.1, var="Infection_intensity.1")
-# 
-# contrast(lms_delta,"pairwise")
-# 
-# tolre_deltasum=summary(lms_delta)
-# 
-# # comparison of slopes to zero
-# 
-# summary(lms_delta, infer=T)
-# 
-# # body condition change - first infection intensity
-# 
-# tolres_delta_first=ggplot(data =data2016_2020[!
-data2016_2020$Infection_intensity.1 %in% NA & !
-data2016_2020$Diff_Inf_Class %in% c(NA,"Uninfected"),], aes(y=body_condition.1,x=as.numeric(Infection_intensity.1),col=Diff_Inf_Class))+
-#     geom_jitter(size=3, alpha=0.5)+
-#     geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
-#     labs(title = "First sampling", y="Body condition change",x="Parasitemia \n at first sampling", col='Infection stages')+
-#     # scale_x_continuous(breaks=seq(1,5,1),labels=c("0","1","2","3","4"))+
-#     scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
-#     theme_classic()+
-#     theme(legend.position = "none", axis.text = element_text(size=16), axis.title = element_text(size=18))
+# Second sampling parasitemia
 
-# Second sampling parasitemia
+## linear model testing effect of infection intensity at second sampling on body condition change
+
+tolres_mod=lm(delta_body_condition~Infection_intensity, data=tol_resdata)
+
+summary(tolres_mod)
+
+## Testing the interaction between infection stages and infection intensities
 
@@
 
-tolres_deltamod=lm(body_condition.2~Infection_intensity*Diff_Inf_Class, data=tol_resdata)
+tolres_deltamod=lm(delta_body_condition~Infection_intensity*Diff_Inf_Class, data=tol_resdata)
 
@@
 
-# ## plot
-# 
-# tolres=ggplot(data =data2016_2020[!
-data2016_2020$Infection_intensity %in% c(NA,0) & !
-data2016_2020$Diff_Inf_Class %in% NA,], aes(y=body_condition.2,x=as.numeric(Infection_intensity),col=Diff_Inf_Class))+
-#   geom_jitter(size=3, alpha=0.5)+
-#   geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
-#   labs(y="Body condition \n at second sampling",x="Parasitemia \n at second sampling", col='Infection stages')+
-#   scale_x_continuous(breaks=seq(2,5,1),labels=c("1","2","3","4"))+
-#   scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
-#   theme_classic()+
-#   theme(legend.text = element_text(size=19),legend.title = element_text(size=22), axis.text = element_text(size=16), axis.title = element_text(size=18))
-
-# body condition change - second infection intensity
+# Plotting body condition change - second infection intensity
 
@@
 
-# Supplementary figure
+# Supplementary figures
 
 ```{r}
+
+# Plotting observed values across infection stages
 
@@
   geom_hline(yintercept = mean(data2016_2020$Breathing_rate, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Breathing rate (z-transformed)")+
+  labs(x="", y="Breathing rate")+
   geom_jitter(color ="lightgrey", size=2, width=.3)+
@@
   geom_hline(yintercept = mean(data2016_2020$body_temperature, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Body temperature (z-transformed)")+
+  labs(x="", y="Body temperature")+
   geom_jitter(color ="lightgrey", size=2, width=.3)+
@@
   geom_hline(yintercept = mean(data2016_2020$delta_body_condition, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Body condition (z-transformed)")+
+  labs(x="", y="\U0394 Body condition")+
   geom_jitter(color ="lightgrey", size=2, width=.3)+
@@
   geom_hline(yintercept = mean(data2016_2020$Growth_rate, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Growth rate (z-transformed)")+
+  labs(x="", y="Growth rate")+
   geom_jitter(color ="lightgrey", size=2, width=.3)+
@@
 
-gg1+gg2+gg3+gg4 + plot_annotation(tag_levels = 'A')& 
+figs1=gg1+gg2+gg3+gg4 + plot_annotation(tag_levels = 'A')& 
   theme(plot.tag = element_text(size = 16, face = "bold"))
 
+ggsave(figs1,filename = "./Figs/observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)
+
+# Plotting observed values across infection intensities
+
+gg5=ggplot(data2016_2020[!data2016_2020$Infection_intensity %in% NA,])+
+  aes(Infection_intensity,Breathing_rate)+
+  geom_hline(yintercept = mean(data2016_2020$Breathing_rate, na.rm=T), linetype = "dashed")+
+  labs(x="", y="Breathing rate")+
+  geom_jitter(color ="lightgrey", size=2, width=.3)+
+  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
+               size=2.8 , width=0.05, show.legend = FALSE, 
+               fun.max = function(x) mean(x) + sd(x),
+               fun.min = function(x) mean(x) - sd(x))+
+  stat_summary(fun=mean, colour="black", geom="point", 
+               size=5 ,show.legend = FALSE)+
+  stat_n_text()+
+  theme_classic()+
+  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+
+gg6=ggplot(data2016_2020[!data2016_2020$Infection_intensity %in% NA,])+
+  aes(Infection_intensity,body_temperature)+
+  geom_hline(yintercept = mean(data2016_2020$body_temperature, na.rm=T), linetype = "dashed")+
+  labs(x="", y="Body temperature")+
+  geom_jitter(color ="lightgrey", size=2, width=.3)+
+  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
+               size=2.8 , width=0.05, show.legend = FALSE, 
+               fun.max = function(x) mean(x) + sd(x),
+               fun.min = function(x) mean(x) - sd(x))+
+  stat_summary(fun=mean, colour="black", geom="point", 
+               size=5 ,show.legend = FALSE)+
+  stat_n_text()+
+  theme_classic()+
+  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+
+gg7=ggplot(data2016_2020[!data2016_2020$Infection_intensity %in% NA,])+
+  aes(Infection_intensity,delta_body_condition)+
+  geom_hline(yintercept = mean(data2016_2020$delta_body_condition, na.rm=T), linetype = "dashed")+
+  labs(x="", y="\U0394 Body condition")+
+  geom_jitter(color ="lightgrey", size=2, width=.3)+
+  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
+               size=2.8 , width=0.05, show.legend = FALSE, 
+               fun.max = function(x) mean(x) + sd(x),
+               fun.min = function(x) mean(x) - sd(x))+
+  stat_summary(fun=mean, colour="black", geom="point", 
+               size=5 ,show.legend = FALSE)+
+  stat_n_text()+
+  theme_classic()+
+  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+
+gg8=ggplot(data2016_2020[!data2016_2020$Infection_intensity %in% NA,])+
+  aes(Infection_intensity,Growth_rate)+
+  geom_hline(yintercept = mean(data2016_2020$Growth_rate, na.rm=T), linetype = "dashed")+
+  labs(x="", y="Growth rate")+
+  geom_jitter(color ="lightgrey", size=2, width=.3)+
+  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
+               size=2.8 , width=0.05, show.legend = FALSE, 
+               fun.max = function(x) mean(x) + sd(x),
+               fun.min = function(x) mean(x) - sd(x))+
+  stat_summary(fun=mean, colour="black", geom="point", 
+               size=5 ,show.legend = FALSE)+
+  stat_n_text()+
+  theme_classic()+
+  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+
+# Figure S2
+
+figs2=gg5+gg6+gg7+gg8 + plot_annotation(tag_levels = 'A')& 
+  theme(plot.tag = element_text(size = 16, face = "bold"))
+
+ggsave(figs2,filename = "./Figs/observed_physio_param_parasitemia.png",units = "px", width = 3500, height = 3800)
+
+# Plotting effect sizes of 'infection stages' models
+
+pm1=plot_model(lmer_br,
+               sort.est = T,
+               se = T,
+               title = "Breathing rate",
+               axis.labels = rev(c("Increase : Treatment [Malarone]","Age (days)","Peak : Treatment [Malarone]","Decrease : Treatment [Malarone]","Uninfected : Treatment [Malarone]","Increasing parasitemia","Sex [Males]","Decreasing parasitemia","Sampling interval","Peak parasitemia","Weight (g)","Ambient temperature","Year [2019]","Year [2018]","Year [2020]")))
+
+pm2=plot_model(lmer_bt,
+               sort.est = T,
+               se = T,
+               title = "Body temperature",
+               axis.labels = rev(c("Peak : Treatment [Malarone]","Ambient temperature","Year [2020]","Age (days)","Decrease : Treatment [Malarone]","Weight (g)","Sex [Males]",
+"Decreasing parasitemia","Increase : Treatment [Malarone]","Increasing parasitemia","Uninfected : Treatment [Malarone]",
+"Peak parasitemia","Sampling interval")))
+
+pm3=plot_model(lmer_bc,
+               sort.est = T,
+               se = T,
+               title = "Δ Body condition",
+               axis.labels = rev(c("Year [2020]","Peak : Treatment [Malarone]","Year [2018]","Year [2019]","Sampling interval","Increase : Treatment [Malarone]","Decrease : Treatment [Malarone]","Age (days)", "Uninfected : Treatment [Malarone]","Sex [Males]","Increasing parasitemia","Decreasing parasitemia","Peak parasitemia")))
+
+pm4=plot_model(lmer_gr,
+               sort.est = T,
+               se = T,
+               title = "Growth rate", 
+               axis.labels = rev(c("Peak : Treatment [Malarone]","Year [2020]","Year [2018]","Sampling interval","Year [2019]","Decrease : Treatment [Malarone]","Increase : Treatment [Malarone]","Uninfected : Treatment [Malarone]","Increasing parasitemia","Decreasing parasitemia","Peak parasitemia","Sex [Males]","Age (days)")))
+
+# Figure S3
+
+figs3=pm1+pm2+pm3+pm4 + plot_annotation(tag_levels = 'A')& 
+  theme(plot.tag = element_text(size = 16, face = "bold"))
+
+ggsave(figs3,filename = "./Figs/effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)
+
+# Plotting effect sizes of 'infection intensities' models
+
+pm5=plot_model(lmer_br_para,
+               sort.est = T,
+               se = T,
+               title = "Breathing rate",
+               axis.labels = rev(c("Infection intensity [2] : Treatment [Malarone]","Age (days)","Infection intensity 1", "Infection intensity 4", "Infection intensity [1] : Treatment [Malarone]","Infection intensity [3] : Treatment [Malarone]", "Infection intensity [0] : Treatment [Malarone]","Sex [Males]","Infection intensity 3","Sampling interval","Infection intensity 2","Weight (g)","Ambient temperature","Year [2019]","Year [2018]","Year [2020]")))
+
+pm6=plot_model(lmer_bt_para,
+               sort.est = T,
+               se = T,
+               title = "Body temperature",
+               axis.labels = rev(c("Ambient temperature","Year [2020]","Age (days)", "Infection intensity [3] : Treatment [Malarone]","Infection intensity 1", "Infection intensity [2] : Treatment [Malarone]","Weight (g)","Infection intensity 2","Sex [Males]","Infection intensity [0] : Treatment [Malarone]","Infection intensity [1] : Treatment [Malarone]","Infection intensity 3", "Sampling interval","Infection intensity 4")))
+
+pm7=plot_model(lmer_bc_para,
+               sort.est = T,
+               se = T,
+               title = "Δ Body condition",
+               axis.labels = rev(c("Year [2020]","Year [2018]","Year [2019]","Infection intensity [2] : Treatment [Malarone]","Infection intensity 1","Sampling interval","Infection intensity [3] : Treatment [Malarone]","Infection intensity [0] : Treatment [Malarone]","Age (days)","Sex [Males]","Infection intensity 3","Infection intensity 2","Infection intensity [1] : Treatment [Malarone]","Infection intensity 4")))
+
+pm8=plot_model(lmer_gr_para,
+               sort.est = T,
+               se = T,
+               title = "Growth rate", 
+               axis.labels = rev(c("Year [2020]","Infection intensity [2] : Treatment [Malarone]","Year [2018]","Year [2019]","Sampling interval","Infection intensity 1","Infection intensity [3] : Treatment [Malarone]","Infection intensity [0] : Treatment [Malarone]","Infection intensity 3","Sex [Males]","Infection intensity 2","Age (days)","Infection intensity 4","Infection intensity [1] : Treatment [Malarone]")))
+
+# Figure S4
+
+figs4=pm5+pm6+pm7+pm8 + plot_annotation(tag_levels = 'A')& 
+  theme(plot.tag = element_text(size = 16, face = "bold"))
+
+ggsave(figs4,filename = "./Figs/effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
+
 ```

### 2022-02-11 MS_physiology_infection_MO.Rmd
Some suggested edits and a bit of formatting

---
title: "R code for 'Apparent physiological costs of early-life blood parasite infection in a vertebrate host'"
author: "Tony Rinaud, Meinolf Ottensmann, Oliver Krüger & Nayden Chakarov"
output: html_document
---

This document provides all the `R code` used in our paper. Both the Rmarkdown file and the data can be downloaded from the accompanying GitHub repository on (<https://github.com/TonyRinaud/MS_physiology_infection>) as a zip archive containing all the files. We recommend to download or clone this [GitHub repository](https://github.com/TonyRinaud/MS_physiology_infection) in order to access the documentation together with all the files that are needed to repeat analyses shown in this document. Just click on the link above and then on the green box `Clone or download`. In order to function properly, the same structure of folders must be kept. If you have any questions, don't hesitate to contact [tony.rinaud\@gmail.com](mailto:tony.rinaud@gmail.com){.email}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, strip.white = TRUE, collapse = TRUE, fig.align = "center",
                      warning = F, message = F, highlight = TRUE, tidy = TRUE)
```

## Required packages

A number of packages, all of which are available on CRAN are required to repeat analyses presented in this document. The code chunk below allows to load them for the analyses.

```{r packages, message=F, warning=F}
library(brms)
library(chron)
library(cowplot)
library(EnvStats)
library(forcats)
library(Hmisc)
library(FSA)
library(lme4)
library(lsmeans)
library(ggalt)
library(ggdist)
library(ggeffects)
library(ggpubr)
library(ggrepel)
library(ggridges)
library(ggsci)
library(ggsignif)
library(grid)
library(gridExtra)
library(magrittr)
library(modelr)
library(MuMIn)
#library(osmdata)
library(patchwork)
library(pdftools)
library(RColorBrewer)
library(rptR)
#library(rdwd)
library(rgdal)
library(RVAideMemoire)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(tidybayes)
library(tidyverse) 
library(wesanderson)
theme_set(theme_tidybayes() + panel_border())
```

## Load raw data

The raw data is comprised of 276 common buzzard (*Buteo buteo*) individuals. Each individual was sampled twice over the course of nestling period during the years 2016 and 2018 - 2020. First, the raw data is loaded from the file `physiology_infection_stage_full_wideformat.csv` and formatted (scaling variables, reordering factor levels etc.) for downstream analyses

```{r data}
## Load data from csv file and code variable classes
## -----------------------------------------------------------------------------
df <- 
  read.csv('./physiology_infection_stage_full_wideformat.csv', h = T, sep = ';', dec = ".") %>% 
  mutate(Nest = as.factor(Nest)) %>% 
  mutate(Date = chron(as.character(Date), format = "d/m/y")) %>% 
  mutate(Infection_intensity = as.factor(Infection_intensity)) %>% 
  mutate(Prevalence = as.factor(Prevalence)) %>% ## Prevalence at time point 2 ???
  mutate(Prevalence1 = as.factor(ifelse(Infection_intensity.1 == 0, 0, 1))) %>% 
  mutate(Breathing_rate = as.numeric(Breathing_rate)) %>% 
  mutate(Sex = as.factor(Sex)) %>% 
  mutate(Sampling_rank = as.factor(Sampling_rank)) %>% 
  mutate(Weight_g = scale(as.numeric(Weight.2))) %>% 
  mutate(Wing_cm = as.numeric(Wing)) %>% 
  mutate(body_temperature = as.numeric(body_temperature)) %>% 
  mutate(delta_body_condition = as.numeric(delta_body_condition)) %>% 
  mutate(Ambient_Temperature_AvgC = scale(as.numeric(TemperatureAvgC))) %>% 
  mutate(Treatment = as.factor(Treatment)) %>% 
  mutate(Year = as.factor(Year)) %>% 
  mutate(Growth_rate = as.numeric(Growth_rate_unlog)) %>% 
  mutate(days_resample = scale(days_resample)) %>% 
  mutate(Age_in_days = scale(as.numeric(Age_in_days))) %>% 
  mutate(Diff_Inf_Class = factor(Diff_Inf_Class, levels = c("Uninfected","Increase","Peak","Decrease")))

## Arrange data frame
## ----------------------------------------------------------------------------- 
df <- arrange(df, df$Diff_Inf_Class)

## Filtering non-applicable infection change
## -----------------------------------------------------------------------------
df <- df[!is.na(df$Diff_Inf_Class),]
```

## Effects on parasites

Investigating treatment effects on the prevalence of *Leucocytozoon* parasites:

```{r}
## Build contingency table: Infection prevalence and treatment: First sampling
## -----------------------------------------------------------------------------
pre_treatment <- with(df, table(Prevalence1, Treatment))
prop.test(pre_treatment)
pairwise.prop.test(pre_treatment)

## Build contingency table: Infection prevalence and treatment: Second sampling
## -----------------------------------------------------------------------------
post_treatment <- with(df, table(Prevalence, Treatment))
prop.test(post_treatment)
pairwise.prop.test(post_treatment)

## Proportion of infected individuals across time points
## -----------------------------------------------------------------------------
infected_treatment <- 
  matrix(c(pre_treatment[2,], post_treatment[2,]), nrow = 2) %>% 
  set_colnames(., c("Pre", "Post")) %>% 
  set_rownames(., c("Control", "Malarone"))
prop.test(infected_treatment)
pairwise.prop.test(infected_treatment)

## Proportion of uninfected individuals across time points
## -----------------------------------------------------------------------------
uninfected_treatment <- 
  matrix(c(pre_treatment[1,], post_treatment[1,]), nrow = 2) %>% 
  set_colnames(., c("Pre", "Post")) %>% 
  set_rownames(., c("Control", "Malarone"))
prop.test(uninfected_treatment)
pairwise.prop.test(uninfected_treatment)

## Plotting count of infected / uninfected nestlings across treatments
## -----------------------------------------------------------------------------
tab_cont = data.frame(
  Count = c(infected_treatment[1,], uninfected_treatment[1,], infected_treatment[2,], uninfected_treatment[2,]),
  Timepoint = rep(c("Pre-treatment","Post-treatment"), 4),
  Treatment = rep(c("Control", "Treatment"), each = 4),
  Prevalence = rep(rep(c("Infected", "Uninfected"), each = 2),2)) %>% 
  mutate(Timepoint = factor(Timepoint, levels = c("Pre-treatment","Post-treatment"))) %>% 
  mutate(Prevalence = factor(Prevalence, levels = c("Uninfected","Infected")))

##  Create Figure 2a
## -----------------------------------------------------------------------------
treatment_prevalence_changes  <- ggplot(tab_cont) +  
  aes(Timepoint, Count, fill = Prevalence) +  
  facet_wrap(facets = "Treatment") +  
  geom_bar(stat = 'identity',  width = 0.3) +  
  labs(y = "Count of nestlings") +  
  geom_text(aes(label = Count),position  = position_stack(0.5)) +  
  scale_fill_manual(values = c("#D0D0D0","#A8A8A8")) +  
  theme(axis.title.x  =  element_blank(), 
        strip.text = element_text(size = 16, face = "bold"),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 16),
        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 16))

## Plotting mean infection intensity values of nestlings across treatments
## -----------------------------------------------------------------------------
mean_infint = data.frame(
  Sampling_rank = factor(c(rep("1",length(df$Sampling_rank)),as.character(df$Sampling_rank)),levels = c("1","2"),
                         labels  =  c("Pre-treatment","Post-treatment")),
  Infection_intensity = as.numeric(c(as.character(df$Infection_intensity.1),as.character(df$Infection_intensity))),
  Treatment = factor(c(as.character(rep(df$Treatment,2))),levels  =  c("Control","Malarone")))

## Figure 2b
## -----------------------------------------------------------------------------
treatment_meaninf_changes = ggplot(mean_infint) +
  aes(Sampling_rank, Infection_intensity, group = Treatment) +
  geom_vline(xintercept  =  "Pre-treatment", linetype = "dashed", color = 'darkgrey') +
  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color = 'darkgrey') +
  labs(y = "Mean infection intensity") +
  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1)) +
  stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey")) +
  stat_summary(fun = mean, geom = "point",size = 5) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.04, size = 2) + 
  scale_color_manual(values = c("lightgrey","black")) + 
  theme_classic() + 
  theme(axis.title.x = element_blank(),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 16),
        plot.margin = unit(c(0,0,0,30), "pt"))

## Panel wrapping Fig2 a & b:
## ----------------------------------------------------------------------------- 
Fig2 <- treatment_prevalence_changes + 
  treatment_meaninf_changes +
  plot_annotation(tag_levels = 'A') + 
  theme(plot.tag = element_text(size = 16, face = "bold"))
ggsave(Fig2,filename = "./Figs/efficiency_malarone.png",units = "px", width = 6000, height = 3000)

## Testing for difference in mean infection intensity between Pre and Post treatment
## -----------------------------------------------------------------------------
mean_before_after <- data.frame(
  Ring_no = 
    c(df$Ring_no[df$Sampling_rank %in% 2], df$Ring_no[df$Sampling_rank %in% 2]),
  Infection_intensity = c(as.character(df$Infection_intensity.1), as.character(df$Infection_intensity)),
  Treatment = 
    c(as.character(df$Treatment[df$Sampling_rank %in% 2]), as.character(df$Treatment[df$Sampling_rank %in% 2])),
  Timepoint = 
    c(rep("Pre-treatment", times = length(df$Treatment)), rep("Post-treatment", times = length(df$Infection_intensity)))) %>% 
  mutate(Treatment = as.factor(Treatment)) %>% 
  mutate(Timepoint = as.factor(Timepoint))

mal = mean_before_after[mean_before_after$Treatment %in% "Malarone",]
ctrl = mean_before_after[mean_before_after$Treatment %in% "Control",]
first = mean_before_after[mean_before_after$Timepoint %in% "Pre-treatment",]

## Pre-treatment difference in parasitic load between Treatments
## -----------------------------------------------------------------------------
perm.t.test(as.numeric(as.character(first$Infection_intensity)) ~ first$Treatment, progress = F)
sd(first$Infection_intensity[first$Treatment %in% "Control"])

## In malarone treated nestlings
## -----------------------------------------------------------------------------
perm.t.test(as.numeric(as.character(mal$Infection_intensity)) ~ mal$Timepoint, progress = F)

# In control nestlings
## -----------------------------------------------------------------------------
perm.t.test(as.numeric(as.character(ctrl$Infection_intensity))~ctrl$Timepoint, progress = F)
```

## Effects on physiology

Exploring effects on physiology of nestlings due to the treatment:

### Breathing rate

No treatment effect on breathing rate!

```{r}
lm_d1 = lm(Breathing_rate ~ Treatment, data = df)
summary(lm_d1)
```

### Body temperature

No treatment effect on body temperature

```{r}
lm_d2 <- lm(body_temperature~Treatment, data = df)
summary(lm_d2)
```

### Body condition change

No treatment effect on body condition change

```{r}
lm_d3 <- lm(delta_body_condition~Treatment, data = df)
summary(lm_d3)
```

### Growth rate

No treatment effect on growth rates

```{r}
lm_d4 <- lm(Growth_rate~Treatment, data = df)
summary(lm_d4)

## Create Table S1
## -----------------------------------------------------------------------------
tab_model(
  lm_d1,lm_d2,lm_d3,lm_d4,
  show.reflvl = T,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  pred.labels = c("Intercept","Treatment [Malarone]"),
  dv.labels = c("Breathing rate","Body temperature", "Δ Body condition","Growth rate"),
  file = "./Physiological_parameters_in_decreasing_control_treated.html")
```

## Infection stages as explanatory variable

Exploring differences in physiological measures that are associated with the infection stage (increase, peak or decreasing) of tested individuals.

### Breathing rate

```{r mixed model breathing rate, warning=F, message=F}
## Run model
## ----------------------------------------------------------------------------- 
lmer_br <- lmer(
  Breathing_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + 
    days_resample + Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest),
  data = df)

## Obtain predicted values for each infection stage
## -----------------------------------------------------------------------------
mod_br <- get_model_data(lmer_br, type = 'pred', terms = "Diff_Inf_Class") %>% 
   mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), 
                     levels = c("Uninfected","Increase","Peak","Decrease")))

## Extract sample size for infection stage
## -----------------------------------------------------------------------------
n <- table(df$Diff_Inf_Class[!is.na(df$Breathing_rate)])

## ad sample size as label
## -----------------------------------------------------------------------------
mod_br <- mod_br %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n)), levels = c(paste0(x,"\nn= ",n))))

## Plotting predicted values across infection stages
## -----------------------------------------------------------------------------
gg1_pred <- ggplot(mod_br) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_br$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  ylim(c(min(mod_br$conf.low) - 1.5,max(mod_br$conf.high) + 1.5)) + 
  geom_errorbar(aes(ymin = mod_br$conf.low,ymax = mod_br$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br$predicted - mod_br$std.error, ymax = mod_br$predicted + mod_br$std.error),
                size = 8, colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        plot.margin = margin(0, 0, 0, 0, "cm"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
  aes(x = 1, y = max(mod_br$conf.high) + 1, xend = 4, yend = max(mod_br$conf.high) + 1)) + 
  geom_text(aes(x = 2.5, y = max(mod_br$conf.high) + 1.5),
  label = "n.s.", size = 5)
```

### Body temperature

```{r mixed model body temp after, warning=FALSE, message=F}
## Model 
## -----------------------------------------------------------------------------
lmer_bt = lmer(
  body_temperature ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Ambient_Temperature_AvgC + 
    days_resample + Age_in_days + Weight_g + Sex + Year + (1|Nest),
  data = df)

## Predicted values for each infection stage
## -----------------------------------------------------------------------------
mod_bt = get_model_data(lmer_bt,type = 'pred',terms = "Diff_Inf_Class") %>%
  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"),
                    levels = c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for body temperature data
n2 = table(df$Diff_Inf_Class[!is.na(df$body_temperature)])

mod_bt <- mod_bt %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n2)), levels = c(paste0(x,"\nn= ",n2))))

# Plotting predicted values across infection stages
gg2_pred <- ggplot(mod_bt) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bt$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body temperature") + 
  geom_errorbar(aes(ymin = mod_bt$conf.low,ymax = mod_bt$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt$predicted - mod_bt$std.error,ymax = mod_bt$predicted + mod_bt$std.error),
                size = 8,colour = wes_palette("Zissou1",4), width = 0) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title.y = element_text(size = 14, margin = unit(c(0,3,0,0),"mm")), 
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y = 40.6, xend = 4, yend = 40.6)) + 
    geom_text(aes(x = 2.5, y = 40.7),
              label = "n.s.", size = 5)
```

### Body condition change

```{r mixed model body condition, warning=FALSE, message=F}
## Model 
## -----------------------------------------------------------------------------
lmer_bc <- lmer(
  delta_body_condition ~ Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample + 
    Age_in_days+Sex+Year+(1|Nest),
  data = df)

# Predicted values for each infection stage
mod_bc = get_model_data(lmer_bc,type = 'pred',terms = "Diff_Inf_Class") %>%
  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), 
                  levels = c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for body condition change data
n3 = table(df$Diff_Inf_Class[!is.na(df$delta_body_condition)])

mod_bc <- mod_bc %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n3)), levels = c(paste0(x,"\nn= ",n3))))

# Plotting predicted values across infection stages

gg3_pred = ggplot(mod_bc) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_bc$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc$conf.low,ymax = mod_bc$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bc$predicted - mod_bc$std.error,ymax = mod_bc$predicted + mod_bc$std.error),
                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bc$conf.high) + 17, xend = 4, yend = max(mod_bc$conf.high) + 17)) + 
  geom_text(aes(x = 2.5, y = max(mod_bc$conf.high) + 23),
              label = "n.s.", size = 5)
```

### Growth rate

```{r mixed model body temp, warning=FALSE, message=F}
# Model 
lmer_gr = lmer(Growth_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Sex + days_resample + Age_in_days + Year + (1|Nest), data= df)

# Predicted values for each infection stages
mod_gr = get_model_data(lmer_gr,type = 'pred',terms = "Diff_Inf_Class") %>%
  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), levels = c("Uninfected","Increase","Peak","Decrease")))

# Table with sample sizes specific for growth rate data
n4 = table(df$Diff_Inf_Class[!is.na(df$Growth_rate)])

mod_gr <- mod_gr %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",n4)), levels = c(paste0(x,"\nn= ",n4))))

# Plotting predicted values across infection stages

gg4_pred = ggplot(mod_gr) + 
  aes(x,predicted) + 
  geom_hline(yintercept = mean(mod_gr$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr$conf.low,ymax = mod_gr$conf.high),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_gr$predicted - mod_gr$std.error,ymax = mod_gr$predicted + mod_gr$std.error), 
                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title.y = element_text(size = 14, margin = unit(c(0, 3, 0, 0), "mm")),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.margin = margin(0, 0, 0, 30, "pt"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_gr$conf.high) + 1.2, xend = 4, yend = max(mod_gr$conf.high) + 1.2)) + 
    geom_text(aes(x = 2.5, y = max(mod_gr$conf.high) + 2),
              label = "n.s.", size = 5)
```

## Summarise models

The code below is used to summarise the model output and create Figure 4 and Table 3 as shown in the manuscript.

```{r}
## Figure 4 
## -----------------------------------------------------------------------------
fig4 <- gg1_pred + gg2_pred + gg3_pred + gg4_pred + plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 16, face = "bold"))
ggsave(fig4,filename = "./Figs/predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)

# Table 3
## -----------------------------------------------------------------------------
sjPlot::tab_model(
  lmer_br,lmer_bt,lmer_bc,lmer_gr,
  show.ci50 = T ,
  show.stat = T,
  string.stat = "t",
  df.method = "kr",
  dv.labels = c("Breathing rate","Body temperature","Δ Body condition","Growth rate"),
  file = "Table_results_lmer_physiological_parameters_p.val_kr.html")
```

## Parasitemia as explanatory variable

Exploration of effects by parasitemia levels on physiology of individuals.

### Breathing rate

```{r mixed model breathing rate 2, warning=F, message=F}
## Model 
## -----------------------------------------------------------------------------
lmer_br_para = lmer(
  Breathing_rate ~ Infection_intensity + Infection_intensity:Treatment + days_resample + 
    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data= df)

# Predicted values for post-treament parasitemia

mod_br_para=get_model_data(lmer_br_para,type = 'pred',terms = "Infection_intensity") %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

# Table with sample sizes specific for breathing rate change data

m1 = table(df$Infection_intensity[!is.na(df$Breathing_rate)])

mod_br_para <- mod_br_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m1)), levels = c(paste0(x,"\nn= ",m1))))
mod_br_para$lower_CI= c(31.11, mod_br_para$predicted[1] - 2.96, mod_br_para$predicted[1] - 6.49,mod_br_para$predicted[1] - 4.67, mod_br_para$predicted[1] - 4.63)
mod_br_para$higher_CI= c(41.42,mod_br_para$predicted[1]+3.90,mod_br_para$predicted[1]+1.75,mod_br_para$predicted[1]+1.46,mod_br_para$predicted[1]+4.45)
mod_br_para$se= c(2.61,1.74,2.09,1.56,2.31)

# Plotting predicted values across infection intensities

gg1_pred_para = ggplot(mod_br_para) + 
  aes(as.factor(mod_br_para$x),mod_br_para$predicted) + 
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_errorbar(aes(ymin = mod_br_para$lower_CI,ymax = mod_br_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_br_para$predicted - mod_br_para$se, ymax = mod_br_para$predicted + mod_br_para$se),
                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size = 4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_br_para$higher_CI, na.rm = T) + 1.2,
                              xend=5, yend = max(mod_br_para$higher_CI, na.rm = T) + 1.2)) + 
    geom_text(aes(x = 3, y = max(mod_br_para$higher_CI, na.rm = T) + 2),
              label = "n.s.", size = 5)
```

### Body temperature

```{r  mixed model body temperature 2, warning=FALSE, message=F, echo=T}
# Model

lmer_bt_para = lmer(
  body_temperature ~ Infection_intensity + Infection_intensity:Treatment + days_resample +
    Ambient_Temperature_AvgC + Age_in_days + Weight_g + Sex + Year + (1|Nest), data= df)

# Predicted values for post-treament parasitemia

mod_bt_para = get_model_data(lmer_bt_para, 
                             type = 'pred',
                             terms = "Infection_intensity") %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

# Table with sample sizes specific for body temperature change data

m2 = table(df$Infection_intensity[!is.na(df$body_temperature)])

mod_bt_para <- mod_bt_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m2)), levels = c(paste0(x,"\nn= ",m2))))
mod_bt_para$lower_CI= c(39.40,mod_bt_para$predicted[1] - 0.40,mod_bt_para$predicted[1] - 0.60,mod_bt_para$predicted[1] - 0.65,mod_bt_para$predicted[1] - 1.38)
mod_bt_para$higher_CI= c(40.40,mod_bt_para$predicted[1]+0.55,mod_bt_para$predicted[1]+0.36,mod_bt_para$predicted[1]+0.19,mod_bt_para$predicted[1]+(-0.24))
mod_bt_para$se= c(0.23,0.24,0.24,0.21,0.29)

# Plotting predicted values across infection intensities

gg2_pred_para = ggplot(mod_bt_para) + 
  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted) + 
  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm = T), linetype = "dashed") + 
  geom_errorbar(aes(ymin = mod_bt_para$lower_CI,ymax = mod_bt_para$higher_CI),colour = "black",size = 2, width = .1) + 
  geom_errorbar(aes(ymin = mod_bt_para$predicted - mod_bt_para$se,ymax = mod_bt_para$predicted + mod_bt_para$se),
                size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
  labs(x = "", y = "Body temperature") + 
  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8, aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
                              xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2)) + 
    geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.25),
              label = "**", size = 8) + 
  geom_segment(size = .8,
                 aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2, xend=1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.05)) + 
  geom_segment(size = .8,
                 aes(x =5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.05, xend=5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2))
```

### Body condition change

```{r mixed model body condition change 2, warning=FALSE, message=F, echo=T}
# Model 
lmer_bc_para <- lmer(
  delta_body_condition ~ Infection_intensity + Infection_intensity:Treatment + days_resample +
    Age_in_days + Sex + Year + (1|Nest), data= df)

# Predicted values for post-treament parasitemia

mod_bc_para=get_model_data(lmer_bc_para,type = 'pred',terms = "Infection_intensity") %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

# Table with sample sizes specific for body condition change data

m3 = table(df$Infection_intensity[!is.na(df$delta_body_condition)])

mod_bc_para <- mod_bc_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m3)), levels = c(paste0(x,"\nn= ",m3))))
mod_bc_para$lower_CI= c(-65.99,mod_bc_para$predicted[1] - 5.71,mod_bc_para$predicted[1] - 53.27,mod_bc_para$predicted[1] - 37.05,mod_bc_para$predicted[1] - 71.88)
mod_bc_para$higher_CI= c(25.59,mod_bc_para$predicted[1]+51.67,mod_bc_para$predicted[1]+16.43,mod_bc_para$predicted[1]+16.17,mod_bc_para$predicted[1]+4.09)
mod_bc_para$se= c(23.20,14.57,17.69,13.51,19.29)

# Plotting predicted values across infection intensities

gg3_pred_para = ggplot(mod_bc_para) + 
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Δ Body condition") + 
  geom_errorbar(aes(ymin = mod_bc_para$lower_CI,ymax = mod_bc_para$higher_CI),colour = "black",size = 2, width =.1) + 
  geom_errorbar(aes(ymin = mod_bc_para$predicted-mod_bc_para$se,ymax = mod_bc_para$predicted+mod_bc_para$se),size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),  
        axis.text = element_text(size = 12), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y =-105, xend=5, yend =-105)) + 
    geom_text(aes(x =3, y =-110),
              label= "p=0.08", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y =-105, xend=1, yend =-105+5)) + 
  geom_segment(size = .8,
                 aes(x =5, y =-105, xend=5, yend =-105+5))
```

### Growth rate

```{r mixed model growth rate 2, warning=FALSE, message=F, echo=T}
# Model 
lmer_gr_para = lmer(
  Growth_rate ~ Infection_intensity + Infection_intensity:Treatment +
    days_resample + Sex + Age_in_days + Year + (1|Nest), data= df)

# Predicted values for post-treament parasitemia
mod_gr_para=get_model_data(lmer_gr_para,type = 'pred',terms = "Infection_intensity") %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))

# Table with sample sizes specific for growth rate data

m4 = table(df$Infection_intensity[!is.na(df$Growth_rate)])

mod_gr_para <- mod_gr_para %>% 
  mutate(x = factor(c(paste0(x,"\nn= ",m4)), levels = c(paste0(x,"\nn= ",m4))))
mod_gr_para$lower_CI= c(11.44,mod_gr_para$predicted[1] - 2.22,mod_gr_para$predicted[1] - 10.47,mod_gr_para$predicted[1] - 6.60,mod_gr_para$predicted[1] - 11.39)
mod_gr_para$higher_CI= c(25.14,mod_gr_para$predicted[1]+7.08,mod_gr_para$predicted[1]+0.92,mod_gr_para$predicted[1]+1.91,mod_gr_para$predicted[1]+0.89)
mod_gr_para$se= c(3.47,2.36,2.89,2.16,3.12)

# Plotting predicted values across infection intensities

gg4_pred_para = ggplot(mod_gr_para) + 
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted) + 
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_errorbar(aes(ymin = mod_gr_para$lower_CI,ymax = mod_gr_para$higher_CI),colour = "black",size = 2, width =.1) + 
  geom_errorbar(aes(ymin = mod_gr_para$predicted-mod_gr_para$se,ymax = mod_gr_para$predicted+mod_gr_para$se),size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
  geom_segment(size = .8,
                 aes(x = 1, y =5, xend=5, yend =5)) + 
    geom_text(aes(x =3, y =5-0.63),
              label= "p=0.09", size = 5) + 
  geom_segment(size = .8,
                 aes(x = 1, y =5, xend=1, yend =5+0.5)) + 
  geom_segment(size = .8,
                 aes(x =5, y =5, xend=5, yend =5+0.5))

```

### Summary four models

```{r summary}
# Figure 5
fig5=gg1_pred_para+gg2_pred_para+gg3_pred_para+gg4_pred_para + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(fig5,filename = "./Figs/predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)

# Table 4

sjPlot::tab_model(lmer_br_para,lmer_bt_para,lmer_bc_para,lmer_gr_para,
                  show.ci50 = T ,
                  show.se = T,
                  show.stat = T,
                  string.stat = "t",
                  p.val = "kr",
                  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
                  file = "table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")

```

## Host health to parasitemia

```{r, warning=F,message=F}
tol_resdata = df
tol_resdata$Infection_intensity = as.numeric(tol_resdata$Infection_intensity)
tol_resdata$Diff_Inf_Class = factor(tol_resdata$Diff_Inf_Class, levels = c("Increase","Peak","Decrease"))

# Second sampling parasitemia

## linear model testing effect of infection intensity at second sampling on body condition change

tolres_mod=lm(delta_body_condition~Infection_intensity, data=tol_resdata)

summary(tolres_mod)

## Testing the interaction between infection stages and infection intensities

## with delta body condition

tolres_deltamod=lm(delta_body_condition~Infection_intensity*Diff_Inf_Class, data=tol_resdata)

## comparison of slopes among infection stages

lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity, var= "Infection_intensity")

contrast(lms_delta,"pairwise")

tolre_deltasum=summary(lms_delta)

## comparison of slopes to zero

summary(lms_delta, infer=T)

# Plotting body condition change - second infection intensity

tolres <- ggplot(data = df[!df$Infection_intensity %in% c(NA,0) & !df$Diff_Inf_Class %in% NA,],
                aes(y = delta_body_condition, x = as.numeric(Infection_intensity), col = Diff_Inf_Class)) + 
    geom_jitter(size = 3, alpha=0.5) + 
    geom_smooth(alpha = 0.2, size =1.5, method='lm',se = T) + 
    labs(y = "Body condition change",x = "Parasitemia \n at second sampling", col='Infection stages') + 
    scale_x_continuous(breaks=seq(2,5,1),labels= c("1","2","3","4")) + 
    scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
    theme_classic() + 
    theme(legend.text = element_text(size =19),legend.title = element_text(size =22), axis.text = element_text(size =16), axis.title = element_text(size =18))

# Figure 3

fig3=tolres + 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(fig3,filename = "./Figs/delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
```

## Supplementary figures

Creating supplementary figures:

```{r}
# Plotting observed values across infection stages
gg1 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,Breathing_rate) + 
  geom_hline(yintercept = mean(df$Breathing_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

gg2 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,body_temperature) + 
  geom_hline(yintercept = mean(df$body_temperature, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body temperature") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

gg3 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,delta_body_condition) + 
  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "\U0394 Body condition") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

gg4 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
  aes(Diff_Inf_Class,Growth_rate) + 
  geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

# Figure S1

figs1=gg1+gg2+gg3+gg4 + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(figs1,filename = "./Figs/observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)

# Plotting observed values across infection intensities

gg5 = ggplot(df[!df$Infection_intensity %in% NA,]) + 
  aes(Infection_intensity,Breathing_rate) + 
  geom_hline(yintercept = mean(df$Breathing_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Breathing rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

gg6 <- ggplot(df[!df$Infection_intensity %in% NA,]) + 
  aes(Infection_intensity,body_temperature) + 
  geom_hline(yintercept = mean(df$body_temperature, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Body temperature") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none",
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12), 
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

gg7 = ggplot(df[!df$Infection_intensity %in% NA,]) + 
  aes(Infection_intensity,delta_body_condition) + 
  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "\U0394 Body condition") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", 
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12), 
        axis.line.x = element_blank(), 
        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
        plot.title = element_text(hjust = 0.5, face = "bold"))

gg8 = ggplot(df[!df$Infection_intensity %in% NA,]) + 
  aes(Infection_intensity,Growth_rate) + 
  geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
  labs(x = "", y = "Growth rate") + 
  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
               size =2.8 , width = 0.05, show.legend = FALSE, 
               fun.max = function(x) mean(x) + sd(x),
               fun.min = function(x) mean(x) - sd(x)) + 
  stat_summary(fun = mean, colour = "black", geom = "point", 
               size =5 ,show.legend = FALSE) + 
  stat_n_text() + 
  theme_classic() + 
  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))

# Figure S2

figs2=gg5+gg6+gg7+gg8 + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(figs2,filename = "./Figs/observed_physio_param_parasitemia.png",units = "px", width = 3500, height = 3800)

# Plotting effect sizes of 'infection stages' models

pm1=plot_model(lmer_br,
               sort.est = T,
               se = T,
               title = "Breathing rate",
               axis.labels = rev(c("Increase : Treatment [Malarone]","Age (days)","Peak : Treatment [Malarone]","Decrease : Treatment [Malarone]","Uninfected : Treatment [Malarone]","Increasing parasitemia","Sex [Males]","Decreasing parasitemia","Sampling interval","Peak parasitemia","Weight (g)","Ambient temperature","Year [2019]","Year [2018]","Year [2020]")))

pm2=plot_model(lmer_bt,
               sort.est = T,
               se = T,
               title = "Body temperature",
               axis.labels = rev(c("Peak : Treatment [Malarone]","Ambient temperature","Year [2020]","Age (days)","Decrease : Treatment [Malarone]","Weight (g)","Sex [Males]",
"Decreasing parasitemia","Increase : Treatment [Malarone]","Increasing parasitemia","Uninfected : Treatment [Malarone]",
"Peak parasitemia","Sampling interval")))

pm3=plot_model(lmer_bc,
               sort.est = T,
               se = T,
               title = "Δ Body condition",
               axis.labels = rev(c("Year [2020]","Peak : Treatment [Malarone]","Year [2018]","Year [2019]","Sampling interval","Increase : Treatment [Malarone]","Decrease : Treatment [Malarone]","Age (days)", "Uninfected : Treatment [Malarone]","Sex [Males]","Increasing parasitemia","Decreasing parasitemia","Peak parasitemia")))

pm4=plot_model(lmer_gr,
               sort.est = T,
               se = T,
               title = "Growth rate", 
               axis.labels = rev(c("Peak : Treatment [Malarone]","Year [2020]","Year [2018]","Sampling interval","Year [2019]","Decrease : Treatment [Malarone]","Increase : Treatment [Malarone]","Uninfected : Treatment [Malarone]","Increasing parasitemia","Decreasing parasitemia","Peak parasitemia","Sex [Males]","Age (days)")))

# Figure S3

figs3=pm1+pm2+pm3+pm4 + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(figs3,filename = "./Figs/effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)

# Plotting effect sizes of 'infection intensities' models

pm5=plot_model(lmer_br_para,
               sort.est = T,
               se = T,
               title = "Breathing rate",
               axis.labels = rev(c("Infection intensity [2] : Treatment [Malarone]","Age (days)","Infection intensity 1", "Infection intensity 4", "Infection intensity [1] : Treatment [Malarone]","Infection intensity [3] : Treatment [Malarone]", "Infection intensity [0] : Treatment [Malarone]","Sex [Males]","Infection intensity 3","Sampling interval","Infection intensity 2","Weight (g)","Ambient temperature","Year [2019]","Year [2018]","Year [2020]")))

pm6=plot_model(lmer_bt_para,
               sort.est = T,
               se = T,
               title = "Body temperature",
               axis.labels = rev(c("Ambient temperature","Year [2020]","Age (days)", "Infection intensity [3] : Treatment [Malarone]","Infection intensity 1", "Infection intensity [2] : Treatment [Malarone]","Weight (g)","Infection intensity 2","Sex [Males]","Infection intensity [0] : Treatment [Malarone]","Infection intensity [1] : Treatment [Malarone]","Infection intensity 3", "Sampling interval","Infection intensity 4")))

pm7=plot_model(lmer_bc_para,
               sort.est = T,
               se = T,
               title = "Δ Body condition",
               axis.labels = rev(c("Year [2020]","Year [2018]","Year [2019]","Infection intensity [2] : Treatment [Malarone]","Infection intensity 1","Sampling interval","Infection intensity [3] : Treatment [Malarone]","Infection intensity [0] : Treatment [Malarone]","Age (days)","Sex [Males]","Infection intensity 3","Infection intensity 2","Infection intensity [1] : Treatment [Malarone]","Infection intensity 4")))

pm8=plot_model(lmer_gr_para,
               sort.est = T,
               se = T,
               title = "Growth rate", 
               axis.labels = rev(c("Year [2020]","Infection intensity [2] : Treatment [Malarone]","Year [2018]","Year [2019]","Sampling interval","Infection intensity 1","Infection intensity [3] : Treatment [Malarone]","Infection intensity [0] : Treatment [Malarone]","Infection intensity 3","Sex [Males]","Infection intensity 2","Age (days)","Infection intensity 4","Infection intensity [1] : Treatment [Malarone]")))

# Figure S4

figs4=pm5+pm6+pm7+pm8 + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(figs4,filename = "./Figs/effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
```

### 2022-02-12 MS_physiology_infection.Rmd
Add files via upload

@@
 ---
-title: "Manuscript_physiological_consequences_blood_parasite_infection"
-author: "Tony Rinaud"
-date: "`r Sys.Date()`"
-output: pdf_document
+title: "R code for 'Apparent physiological costs of early-life blood parasite infection in a vertebrate host'"
+author: "Tony Rinaud, Meinolf Ottensmann, Oliver Krüger & Nayden Chakarov"
+output: html_document
 ---
 
-# Analysis of blood parasite infection effect on physiological change of common buzzard nestlings:
-
-  Data from common buzzard's (*Buteo buteo*) nestling of the years 2016, 2018, 2019 and 2020 which have been sampled twice during their nesting phase.
+This document provides all the `R code` used in our paper.
+Both the Rmarkdown file and the data can be downloaded from the accompanying GitHub repository on (<https://github.com/TonyRinaud/MS_physiology_infection>) as a zip archive containing all the files.
+We recommend to download or clone this [GitHub repository](https://github.com/TonyRinaud/MS_physiology_infection) in order to access the documentation together with all the files that are needed to repeat analyses shown in this document.
+Just click on the link above and then on the green box `Clone or download`.
+In order to function properly, the same structure of folders must be kept.
+If you have any questions, don't hesitate to contact [tony.rinaud\@gmail.com](mailto:tony.rinaud@gmail.com){.email}
 
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, strip.white = TRUE, collapse = TRUE, fig.align = "center",
+                      warning = F, message = F, highlight = TRUE, tidy = TRUE)
+
+# Routine clean-up upon start
+
+rm(list=ls())
 ```
@@
 
+A number of packages, all of which are available on CRAN are required to repeat analyses presented in this document. The code chunk below allows to load them for the analyses.
+
 ```{r packages, message=F, warning=F}
-library(easypackages)
-libraries('plotly','ggplot2','Hmisc','ggalt','plyr','chron','dplyr','stringr','tidyr','FSA','grid','gridExtra','ggsci','lme4','RVAideMemoire','lsmeans','MuMIn','EnvStats','devtools','RColorBrewer','tidyverse','brms','tidybayes','patchwork','pdftools','osmdata','rgdal','magrittr','purrr','forcats','modelr','ggstance','ggridges','cowplot','ggrepel','gganimate','ggridges','rptR','rdwd','sjPlot','sjlabelled','sjmisc','wesanderson', "ggpubr","ggsignif",'ggdist','ggeffect')
+library(chron)
+library(cowplot)
+library(EnvStats)
+library(lme4)
+library(lsmeans)
+library(ggalt)
+library(ggdist)
+library(ggeffects)
+library(ggplot2)
+library(ggpubr)
+library(ggrepel)
+library(ggridges)
+library(ggsci)
+library(ggsignif)
+library(grid)
+library(gridExtra)
+library(magrittr)
+library(patchwork)
+library(rptR)
+library(RVAideMemoire)
+library(sjPlot)
+library(sjlabelled)
+library(sjmisc)
+library(tidybayes)
+library(tidyverse)
+library(wesanderson)
+theme_set(theme_tidybayes() + panel_border())
+```
 
-# Routine clean-up upon start
-rm(list=ls())
+## Load raw data
 
-theme_set(theme_tidybayes() + panel_border())
+The raw data is comprised of 276 common buzzard (*Buteo buteo*) individuals.
+Each individual was sampled twice over the course of nestling period during the years 2016 and 2018 - 2020.
+First, the raw data is loaded from the file `physiology_infection_stage_full_wideformat.csv` and formatted (scaling variables, reordering factor levels etc.) for downstream analyses
+
+```{r data}
+## Load data from csv file and code variable classes
+## -----------------------------------------------------------------------------
+df <- 
+  read.csv('./physiology_infection_stage_full_wideformat.csv', h = T, sep = ';', dec = ".") %>% 
+  mutate(Nest = as.factor(Nest)) %>% 
+  mutate(Date = chron(as.character(Date), format = "d/m/y")) %>% 
+  mutate(Infection_intensity.1 = as.factor(Infection_intensity.1)) %>% 
+  mutate(Infection_intensity.2 = as.factor(Infection_intensity.2)) %>%
+  mutate(Prevalence2 = as.factor(ifelse(Infection_intensity.2 == 0, 0, 1))) %>%
+  mutate(Prevalence1 = as.factor(ifelse(Infection_intensity.1 == 0, 0, 1))) %>% 
+  mutate(Breathing_rate = as.numeric(Breathing_rate)) %>% 
+  mutate(Sex = as.factor(Sex)) %>% 
+  mutate(Sampling_rank = as.factor(Sampling_rank)) %>% 
+  mutate(Weight_g = scale(as.numeric(Weight.2))) %>% 
+  mutate(Wing_cm = as.numeric(Wing.2)) %>% 
+  mutate(body_temperature = as.numeric(body_temperature)) %>% 
+  mutate(delta_body_condition = as.numeric(delta_body_condition)) %>% 
+  mutate(Ambient_Temperature_AvgC = scale(as.numeric(TemperatureAvgC))) %>% 
+  mutate(Treatment = as.factor(Treatment)) %>% 
+  mutate(Year = as.factor(Year)) %>% 
+  mutate(Growth_rate = as.numeric(Growth_rate)) %>% 
+  mutate(days_resample = scale(days_resample)) %>% 
+  mutate(Age_in_days = scale(as.numeric(Age_in_days))) %>% 
+  mutate(Diff_Inf_Class = factor(Diff_Inf_Class, levels = c("Uninfected","Increase","Peak","Decrease")))
+
+## Arrange data frame
+## ----------------------------------------------------------------------------- 
+df <- arrange(df, df$Diff_Inf_Class)
 
@@
 
-```{r data, echo=F}
+## Effects on parasites
 
-## Data source
-
-data2016_2020=read.csv('./physiology_infection_stage_full_wideformat.csv', h=T, sep=';', dec=".")
-
-### Setting classes of variables
-
-data2016_2020$Nest=as.factor(data2016_2020$Nest)
-data2016_2020$Date=chron(as.character(data2016_2020$Date), format="d/m/y")
-data2016_2020$Infection_intensity=as.factor(data2016_2020$Infection_intensity)
-data2016_2020$Prevalence=as.factor(data2016_2020$Prevalence)
-data2016_2020$Breathing_rate=as.numeric(data2016_2020$Breathing_rate)
-data2016_2020$Sex=as.factor(data2016_2020$Sex)
-data2016_2020$Sampling_rank=as.factor(data2016_2020$Sampling_rank)
-data2016_2020$Weight_g=scale(as.numeric(data2016_2020$Weight.2))
-data2016_2020$Wing_cm=as.numeric(data2016_2020$Wing)
-data2016_2020$body_temperature=as.numeric(data2016_2020$body_temperature)
-data2016_2020$delta_body_condition=as.numeric(data2016_2020$delta_body_condition)
-data2016_2020$Ambient_Temperature_AvgC=scale(as.numeric(data2016_2020$TemperatureAvgC))
-data2016_2020$Treatment=as.factor(data2016_2020$Treatment)
-data2016_2020$Year=as.factor(data2016_2020$Year)
-data2016_2020$Growth_rate=as.numeric(data2016_2020$Growth_rate_unlog)
-data2016_2020$days_resample=scale(data2016_2020$days_resample)
-data2016_2020$Age_in_days=scale(as.numeric(data2016_2020$Age_in_days))
-
-data2016_2020$Diff_Inf_Class=factor(data2016_2020$Diff_Inf_Class, levels=c("Uninfected","Increase","Peak","Decrease"))
-data2016_2020=arrange(data2016_2020,data2016_2020$Diff_Inf_Class)
-
-# Filtering non-applicable infection change
-
-data2016_2020=data2016_2020[!is.na(data2016_2020$Diff_Inf_Class),]
-
-```
-
-**Analyses**
-
-## Testing for effectiveness of treatment
+Investigating treatment effects on the prevalence of *Leucocytozoon* parasites:
 
 ```{r}
+## Build contingency table: Infection prevalence and treatment: First sampling
+## -----------------------------------------------------------------------------
+pre_treatment <- with(df, table(Prevalence1, Treatment))
+prop.test(pre_treatment)
+pairwise.prop.test(pre_treatment)
 
-# Contingency table of control versus treated but uninfected nestlings at the two samplings
+## Build contingency table: Infection prevalence and treatment: Second sampling
+## -----------------------------------------------------------------------------
+post_treatment <- with(df, table(Prevalence2, Treatment))
+prop.test(post_treatment)
+pairwise.prop.test(post_treatment)
 
-tab.cont_noinfect=matrix(c(length(data2016_2020$Infection_intensity.1[data2016_2020$Infection_intensity.1 %in% 0 & data2016_2020$Treatment %in% "Control"]),length(data2016_2020$Infection_intensity.1[data2016_2020$Infection_intensity.1 %in% 0 & data2016_2020$Treatment %in% "Malarone"]),length(data2016_2020$Prevalence[data2016_2020$Prevalence %in% 0 & data2016_2020$Treatment %in% "Control" & data2016_2020$Sampling_rank %in% 2]),length(data2016_2020$Prevalence[data2016_2020$Prevalence %in% 0 & data2016_2020$Treatment %in% "Malarone" & data2016_2020$Sampling_rank %in% 2])),nrow = 2,ncol = 2,dimnames = list(c("Control","Malarone"),c("Before","After")))
+## Proportion of infected individuals across time points
+## -----------------------------------------------------------------------------
+infected_treatment <- 
+  matrix(c(pre_treatment[2,], post_treatment[2,]), nrow = 2) %>% 
+  set_colnames(., c("Pre", "Post")) %>% 
+  set_rownames(., c("Control", "Malarone"))
+prop.test(infected_treatment)
+pairwise.prop.test(infected_treatment)
 
-# Testing whether proportions of uninfected nestlings at first and second samplings differs between treatments
-
-tab.cont_noinfect=t(tab.cont_noinfect)
-
-prop.test(tab.cont_noinfect)
-
-pairwise.prop.test(tab.cont_noinfect)
-
-# Contingency table of control versus treated but infected at the two samplings
-
-tab.cont_infected=matrix(c(length(data2016_2020$Infection_intensity.1[data2016_2020$Infection_intensity.1 %in% c(1,2,3,4) & data2016_2020$Treatment %in% "Control"]),length(data2016_2020$Infection_intensity.1[data2016_2020$Infection_intensity.1 %in% c(1,2,3,4) & data2016_2020$Treatment %in% "Malarone"]),length(data2016_2020$Prevalence[data2016_2020$Prevalence %in% 1 & data2016_2020$Treatment %in% "Control"]),length(data2016_2020$Prevalence[data2016_2020$Prevalence %in% 1 & data2016_2020$Treatment %in% "Malarone"])), nrow = 2, ncol = 2, dimnames = list(c("Control","Malarone"),c("Pre","Post")))
-
-# Testing whether proportions of infected nestlings at first and second samplings differs between treatments
-
-tab.cont_infected=t(tab.cont_infected)
-
-prop.test(tab.cont_infected)
-
-pairwise.prop.test(tab.cont_infected)
+## Proportion of uninfected individuals across time points
+## -----------------------------------------------------------------------------
+uninfected_treatment <- 
+  matrix(c(pre_treatment[1,], post_treatment[1,]), nrow = 2) %>% 
+  set_colnames(., c("Pre", "Post")) %>% 
+  set_rownames(., c("Control", "Malarone"))
+prop.test(uninfected_treatment)
+pairwise.prop.test(uninfected_treatment)
 
 ## Plotting count of infected / uninfected nestlings across treatments
+## -----------------------------------------------------------------------------
+tab_cont = data.frame(
+  Count = c(infected_treatment[1,], uninfected_treatment[1,], infected_treatment[2,], uninfected_treatment[2,]),
+  Timepoint = rep(c("Pre-treatment","Post-treatment"), 4),
+  Treatment = rep(c("Control", "Treatment"), each = 4),
+  Prevalence = rep(rep(c("Infected", "Uninfected"), each = 2),2)) %>% 
+  mutate(Timepoint = factor(Timepoint, levels = c("Pre-treatment","Post-treatment"))) %>% 
+  mutate(Prevalence = factor(Prevalence, levels = c("Uninfected","Infected")))
 
-tab_cont=data.frame(Timepoint=c("Pre-treatment","Post-treatment","Pre-treatment","Post-treatment","Pre-treatment","Post-treatment","Pre-treatment","Post-treatment"),Count=c(tab.cont_noinfect[1,1],tab.cont_noinfect[2,1],tab.cont_noinfect[1,2],tab.cont_noinfect[2,2],tab.cont_infected[1,1],tab.cont_infected[2,1],tab.cont_infected[1,2],tab.cont_infected[2,2]),Treatment=c("Control","Control","Malarone","Malarone","Control","Control","Malarone","Malarone"),Prevalence=c("Uninfected","Uninfected","Uninfected","Uninfected","Infected","Infected","Infected","Infected"))
-
-tab_cont$Timepoint=factor(tab_cont$Timepoint,levels = c("Pre-treatment","Post-treatment"))
-tab_cont$Prevalence=factor(tab_cont$Prevalence,levels = c("Uninfected","Infected"))
-
-# Figure 2a
-
-treatment_prevalence_changes=ggplot(tab_cont)+
-  aes(Timepoint,Count,fill=Prevalence)+
-  facet_wrap(facets = "Treatment")+
-  geom_bar(stat = 'identity',  width = 0.3)+
-  labs(y="Count of nestlings")+
-  geom_text(aes(label=Count),position = position_stack(0.5))+
-  scale_fill_manual(values=c("#D0D0D0","#A8A8A8"))+
-  theme(axis.title.x = element_blank(), strip.text = element_text(size=16, face="bold"),legend.text = element_text(size=14), legend.title = element_text(size=16),axis.title.y=element_text(size=18, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=16))
+##  Create Figure 2a
+## -----------------------------------------------------------------------------
+treatment_prevalence_changes  <- ggplot(tab_cont) +  
+  aes(Timepoint, Count, fill = Prevalence) +  
+  facet_wrap(facets = "Treatment") +  
+  geom_bar(stat = 'identity',  width = 0.3) +  
+  labs(y = "Count of nestlings") +  
+  geom_text(aes(label = Count),position  = position_stack(0.5)) +  
+  scale_fill_manual(values = c("#D0D0D0","#A8A8A8")) +  
+  theme(axis.title.x  =  element_blank(), 
+        strip.text = element_text(size = 16, face = "bold"),
+        legend.text = element_text(size = 14),
+        legend.title = element_text(size = 16),
+        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
+        axis.text = element_text(size = 16))
 
 ## Plotting mean infection intensity values of nestlings across treatments
+## -----------------------------------------------------------------------------
+mean_infint = data.frame(
+  Sampling_rank = factor(c(rep("1",length(df$Sampling_rank)),as.character(df$Sampling_rank)),levels = c("1","2"),
+                         labels  =  c("Pre-treatment","Post-treatment")),
+  Infection_intensity = as.numeric(c(as.character(df$Infection_intensity.1),as.character(df$Infection_intensity))),
+  Treatment = factor(c(as.character(rep(df$Treatment,2))),levels  =  c("Control","Malarone")))
 
-mean_infint=data.frame(Sampling_rank=factor(c(rep("1",length(data2016_2020$Sampling_rank)),as.character(data2016_2020$Sampling_rank)),levels=c("1","2"), labels = c("Pre-treatment","Post-treatment")),Infection_intensity=as.numeric(c(as.character(data2016_2020$Infection_intensity.1),as.character(data2016_2020$Infection_intensity))),Treatment=factor(c(as.character(rep(data2016_2020$Treatment,2))),levels = c("Control","Malarone")))
+## Figure 2b
+## -----------------------------------------------------------------------------
+treatment_meaninf_changes = ggplot(mean_infint) +
+  aes(Sampling_rank, Infection_intensity, group = Treatment) +
+  geom_vline(xintercept  =  "Pre-treatment", linetype = "dashed", color = 'darkgrey') +
+  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color = 'darkgrey') +
+  labs(y = "Mean infection intensity") +
+  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1)) +
+  stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey")) +
+  stat_summary(fun = mean, geom = "point",size = 5) +
+  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.04, size = 2) + 
+  scale_color_manual(values = c("lightgrey","black")) + 
+  theme_classic() + 
+  theme(axis.title.x = element_blank(),
+        legend.text = element_text(size = 16),
+        legend.title = element_text(size = 16),
+        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
+        axis.text = element_text(size = 16),
+        plot.margin = unit(c(0,0,0,30), "pt"))
 
-# Figure 2b
-
-treatment_meaninf_changes=ggplot(mean_infint)+
-  aes(Sampling_rank,Infection_intensity, group=Treatment)+
-  geom_vline(xintercept = "Pre-treatment", linetype = "dashed", color='darkgrey')+
-  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color='darkgrey')+
-  labs(y="Mean infection intensity")+
-  geom_point(aes(colour=Treatment),position=position_jitterdodge(jitter.height = 0.1))+  #jitter.width = 0.2, jitter.height = 0.5) position=position_jitterdodge()
-  # geom_line(aes(group=Treatment,color=Treatment, fill=Treatment),size=2)+
-  stat_summary(fun=mean, geom="line",size=2,color=c("lightgrey","black","black","lightgrey"))+
-  stat_summary(fun=mean, geom="point",size=5)+
-  stat_summary(fun.data=mean_se, geom="errorbar", width=0.04, size=2)+
-  scale_color_manual(values=c("lightgrey","black"))+
-  theme_classic()+
-  theme(axis.title.x = element_blank(), legend.text = element_text(size=16), legend.title = element_text(size=16), axis.title.y=element_text(size=18, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=16), plot.margin = unit(c(0,0,0,30), "pt"))
-
-# Panel wrapping Fig2 a & b:
-
-Fig2=treatment_prevalence_changes+treatment_meaninf_changes+ plot_annotation(tag_levels = 'A')& 
+## Panel wrapping Fig2 a & b:
+## ----------------------------------------------------------------------------- 
+Fig2 <- treatment_prevalence_changes + 
+  treatment_meaninf_changes +
+  plot_annotation(tag_levels = 'A') + 
   theme(plot.tag = element_text(size = 16, face = "bold"))
-
 ggsave(Fig2,filename = "./Figs/efficiency_malarone.png",units = "px", width = 6000, height = 3000)
 
-# Testing for difference in mean infection intensity between Pre and Post treatment
+## Testing for difference in mean infection intensity between Pre and Post treatment
+## -----------------------------------------------------------------------------
+mean_before_after <- data.frame(
+  Ring_no = 
+    c(df$Ring_no[df$Sampling_rank %in% 2], df$Ring_no[df$Sampling_rank %in% 2]),
+  Infection_intensity = c(as.character(df$Infection_intensity.1), as.character(df$Infection_intensity.2)),
+  Treatment = 
+    c(as.character(df$Treatment[df$Sampling_rank %in% 2]), as.character(df$Treatment[df$Sampling_rank %in% 2])),
+  Timepoint = 
+    c(rep("Pre-treatment", times = length(df$Treatment)), rep("Post-treatment", times = length(df$Infection_intensity.2)))) %>% 
+  mutate(Treatment = as.factor(Treatment)) %>% 
+  mutate(Timepoint = as.factor(Timepoint))
 
-mean_before_after=data.frame(Ring_no=c(data2016_2020$Ring_no[data2016_2020$Sampling_rank %in% 2], data2016_2020$Ring_no[data2016_2020$Sampling_rank %in% 2]), Infection_intensity=c(as.character(data2016_2020$Infection_intensity.1), as.character(data2016_2020$Infection_intensity)),Treatment=c(as.character(data2016_2020$Treatment[data2016_2020$Sampling_rank %in% 2]), as.character(data2016_2020$Treatment[data2016_2020$Sampling_rank %in% 2])),Timepoint=c(rep("Pre-treatment",times=length(data2016_2020$Treatment)),rep("Post-treatment",times=length(data2016_2020$Infection_intensity))))
-
-mean_before_after$Treatment=as.factor(mean_before_after$Treatment)
-mean_before_after$Timepoint=as.factor(mean_before_after$Timepoint)
-
-mal=mean_before_after[mean_before_after$Treatment %in% "Malarone",]
-ctrl=mean_before_after[mean_before_after$Treatment %in% "Control",]
-
-first=mean_before_after[mean_before_after$Timepoint %in% "Pre-treatment",]
+mal = mean_before_after[mean_before_after$Treatment %in% "Malarone",]
+ctrl = mean_before_after[mean_before_after$Treatment %in% "Control",]
+first = mean_before_after[mean_before_after$Timepoint %in% "Pre-treatment",]
 
 ## Pre-treatment difference in parasitic load between Treatments
-
-perm.t.test(as.numeric(as.character(first$Infection_intensity))~first$Treatment)
-
+## -----------------------------------------------------------------------------
+perm.t.test(as.numeric(as.character(first$Infection_intensity)) ~ first$Treatment, progress = F)
 sd(first$Infection_intensity[first$Treatment %in% "Control"])
@@
 ## In malarone treated nestlings
-
-perm.t.test(as.numeric(as.character(mal$Infection_intensity))~mal$Timepoint)
+## -----------------------------------------------------------------------------
+perm.t.test(as.numeric(as.character(mal$Infection_intensity)) ~ mal$Timepoint, progress = F)
 
 # In control nestlings
-
-perm.t.test(as.numeric(as.character(ctrl$Infection_intensity))~ctrl$Timepoint)
-
+## -----------------------------------------------------------------------------
+perm.t.test(as.numeric(as.character(ctrl$Infection_intensity))~ctrl$Timepoint, progress = F)
 ```
 
-## Testing the effect of antimalarial treatment on the four physiological parameters in nestlings
+## Effects on physiology
+
+Exploring effects on physiology of nestlings due to the treatment:
 
@@
 
+No treatment effect on breathing rate!
+
 ```{r}
-
-# Model 
-# No effect of treatment on the breathing rate of nestlings
-
-lm_d1=lm(Breathing_rate~Treatment, data=data2016_2020)
+lm_d1 = lm(Breathing_rate ~ Treatment, data = df)
+summary(lm_d1)
 ```
@@
 
+No treatment effect on body temperature
+
 ```{r}
-
-# Model 
-# No effect of treatment on the body temperature of nestlings
-
-lm_d2=lm(body_temperature~Treatment, data=data2016_2020)
+lm_d2 <- lm(body_temperature~Treatment, data = df)
+summary(lm_d2)
 ```
@@
 
+No treatment effect on body condition change
+
 ```{r}
-
-# Model 
-# No effect of treatment on the body condition change of nestlings
-
-lm_d3=lm(delta_body_condition~Treatment, data=data2016_2020)
+lm_d3 <- lm(delta_body_condition~Treatment, data = df)
+summary(lm_d3)
 ```
@@
 
+No treatment effect on growth rates
+
 ```{r}
+lm_d4 <- lm(Growth_rate~Treatment, data = df)
+summary(lm_d4)
 
-# Model 
-# No effect of the antimalarial treatment on the growth rate
-
-lm_d4=lm(Growth_rate~Treatment, data=data2016_2020)
-
-# Table S1
-
-tab_model(lm_d1,lm_d2,lm_d3,lm_d4,
+## Create Table S1
+## -----------------------------------------------------------------------------
+tab_model(
+  lm_d1,lm_d2,lm_d3,lm_d4,
   show.reflvl = T,
@@
   pred.labels = c("Intercept","Treatment [Malarone]"),
-          dv.labels = c("Breathing rate","Body temperature", "Δ Body condition","Growth rate"),
-          file = "./table_results/Physiological_parameters_in_decreasing_control_treated.html")
+  dv.labels = c("Breathing rate","Body temperature", "\U0394 Body condition","Growth rate"),
+  file = "./Physiological_parameters_in_decreasing_control_treated.html")
 ```
 
-# Infection stages as explanatory variable
+## Infection stages as explanatory variable
 
-## Breathing rate
+Exploring differences in physiological measures that are associated with the infection stage (increase, peak or decreasing) of tested individuals.
 
-```{r mixed model breathing rate, warning=F, message=F, echo=F}
+### Breathing rate
 
-# Model
+```{r mixed model breathing rate, warning=F, message=F}
+## Run model
+## ----------------------------------------------------------------------------- 
+lmer_br <- lmer(
+  Breathing_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + 
+    days_resample + Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest),
+  data = df)
 
-lmer_br=lmer(data= data2016_2020, Breathing_rate~Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample+Age_in_days+Weight_g+Sex+Ambient_Temperature_AvgC+Year+(1|Nest))
+## Obtain predicted values for each infection stage
+## -----------------------------------------------------------------------------
+mod_br <- get_model_data(lmer_br, type = 'pred', terms = "Diff_Inf_Class") %>% 
+   mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), 
+                     levels = c("Uninfected","Increase","Peak","Decrease")))
+
+## Extract sample size for infection stage
+## -----------------------------------------------------------------------------
+n <- table(df$Diff_Inf_Class[!is.na(df$Breathing_rate)])
+
+## ad sample size as label
+## -----------------------------------------------------------------------------
+mod_br <- mod_br %>% 
+  mutate(x = factor(c(paste0(x,"\nn= ",n)), levels = c(paste0(x,"\nn= ",n))))
+
+## Plotting predicted values across infection stages
+## -----------------------------------------------------------------------------
+gg1_pred <- ggplot(mod_br) + 
+  aes(x,predicted) + 
+  geom_hline(yintercept = mean(mod_br$predicted, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Breathing rate") + 
+  ylim(c(min(mod_br$conf.low) - 1.5,max(mod_br$conf.high) + 1.5)) + 
+  geom_errorbar(aes(ymin = mod_br$conf.low,ymax = mod_br$conf.high),colour = "black",size = 2, width = .1) + 
+  geom_errorbar(aes(ymin = mod_br$predicted - mod_br$std.error, ymax = mod_br$predicted + mod_br$std.error),
+                size = 8, colour = wes_palette("Zissou1",4), width = 0,) + 
+  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
+  theme_classic() + 
+  theme(legend.position = "none",
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12),
+        axis.line.x = element_blank(), 
+        axis.ticks.x = element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "cm"), 
+        plot.title = element_text(hjust = 0.5, face = "bold")) + 
+  geom_segment(size = .8,
+  aes(x = 1, y = max(mod_br$conf.high) + 1, xend = 4, yend = max(mod_br$conf.high) + 1)) + 
+  geom_text(aes(x = 2.5, y = max(mod_br$conf.high) + 1.5),
+  label = "n.s.", size = 5)
+```
+
+### Body temperature
+
+```{r mixed model body temp after, warning=FALSE, message=F}
+## Model 
+## -----------------------------------------------------------------------------
+lmer_bt = lmer(
+  body_temperature ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Ambient_Temperature_AvgC + 
+    days_resample + Age_in_days + Weight_g + Sex + Year + (1|Nest),
+  data = df)
+
+## Predicted values for each infection stage
+## -----------------------------------------------------------------------------
+mod_bt = get_model_data(lmer_bt,type = 'pred',terms = "Diff_Inf_Class") %>%
+  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"),
+                    levels = c("Uninfected","Increase","Peak","Decrease")))
+
+# Table with sample sizes specific for body temperature data
+n2 = table(df$Diff_Inf_Class[!is.na(df$body_temperature)])
+
+mod_bt <- mod_bt %>% 
+  mutate(x = factor(c(paste0(x,"\nn= ",n2)), levels = c(paste0(x,"\nn= ",n2))))
+
+# Plotting predicted values across infection stages
+gg2_pred <- ggplot(mod_bt) + 
+  aes(x,predicted) + 
+  geom_hline(yintercept = mean(mod_bt$predicted, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Body temperature") + 
+  geom_errorbar(aes(ymin = mod_bt$conf.low,ymax = mod_bt$conf.high),colour = "black",size = 2, width = .1) + 
+  geom_errorbar(aes(ymin = mod_bt$predicted - mod_bt$std.error,ymax = mod_bt$predicted + mod_bt$std.error),
+                size = 8,colour = wes_palette("Zissou1",4), width = 0) + 
+  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
+  theme_classic() + 
+  theme(legend.position = "none",
+        axis.title.y = element_text(size = 14, margin = unit(c(0,3,0,0),"mm")), 
+        axis.text = element_text(size = 12),
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold")) + 
+  geom_segment(size = .8,
+                 aes(x = 1, y = 40.6, xend = 4, yend = 40.6)) + 
+    geom_text(aes(x = 2.5, y = 40.7),
+              label = "n.s.", size = 5)
+```
+
+### Body condition change
+
+```{r mixed model body condition, warning=FALSE, message=F}
+## Model 
+## -----------------------------------------------------------------------------
+lmer_bc <- lmer(
+  delta_body_condition ~ Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample + 
+    Age_in_days+Sex+Year+(1|Nest),
+  data = df)
 
 # Predicted values for each infection stage
+mod_bc = get_model_data(lmer_bc,type = 'pred',terms = "Diff_Inf_Class") %>%
+  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), 
+                  levels = c("Uninfected","Increase","Peak","Decrease")))
 
-mod_br=get_model_data(lmer_br,type='pred',terms="Diff_Inf_Class") %>% 
-   mutate(x=factor(c("Uninfected","Increase","Peak","Decrease"), levels=c("Uninfected","Increase","Peak","Decrease")))
+# Table with sample sizes specific for body condition change data
+n3 = table(df$Diff_Inf_Class[!is.na(df$delta_body_condition)])
 
-# Table with sample sizes specific for breathing rate data
-
-n=table(data2016_2020$Diff_Inf_Class[!is.na(data2016_2020$Breathing_rate)])
-
-mod_br <- mod_br %>% 
-  mutate(x = factor(c(paste0(x,"\nn=",n)), levels=c(paste0(x,"\nn=",n))))
+mod_bc <- mod_bc %>% 
+  mutate(x = factor(c(paste0(x,"\nn= ",n3)), levels = c(paste0(x,"\nn= ",n3))))
 
@@
 
-gg1_pred=ggplot(mod_br)+
-  aes(x,predicted)+
-  geom_hline(yintercept = mean(mod_br$predicted, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Breathing rate")+
-  ylim(c(min(mod_br$conf.low)-1.5,max(mod_br$conf.high)+1.5))+
-  geom_errorbar(aes(ymin=mod_br$conf.low,ymax=mod_br$conf.high),colour="black",size=2, width=.1)+
-  geom_errorbar(aes(ymin=mod_br$predicted-mod_br$std.error,ymax=mod_br$predicted+mod_br$std.error),size=8, colour=wes_palette("Zissou1",4), width=0,)+
-  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
-  geom_segment(size = .8,
-  aes(x=1, y=max(mod_br$conf.high)+1, xend=4, yend=max(mod_br$conf.high)+1))+
-  geom_text(aes(x=2.5, y=max(mod_br$conf.high)+1.5),
-  label="n.s.", size = 5)
+gg3_pred = ggplot(mod_bc) + 
+  aes(x,predicted) + 
+  geom_hline(yintercept = mean(mod_bc$predicted, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Δ Body condition") + 
+  geom_errorbar(aes(ymin = mod_bc$conf.low,ymax = mod_bc$conf.high),colour = "black",size = 2, width = .1) + 
+  geom_errorbar(aes(ymin = mod_bc$predicted - mod_bc$std.error,ymax = mod_bc$predicted + mod_bc$std.error),
+                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
+  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
+  theme_classic() + 
+  theme(legend.position = "none",
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12),
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold")) + 
+  geom_segment(size = .8, aes(x = 1, y = max(mod_bc$conf.high) + 17, xend = 4, yend = max(mod_bc$conf.high) + 17)) + 
+  geom_text(aes(x = 2.5, y = max(mod_bc$conf.high) + 23),
+              label = "n.s.", size = 5)
 ```
 
-## Body temperature
+### Growth rate
 
-```{r mixed model body temp after, warning=FALSE, message=F, echo=F}
+```{r mixed model body temp, warning=FALSE, message=F}
+# Model 
+lmer_gr = lmer(Growth_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Sex + days_resample + Age_in_days + Year + (1|Nest), data= df)
 
-# Model
+# Predicted values for each infection stages
+mod_gr = get_model_data(lmer_gr,type = 'pred',terms = "Diff_Inf_Class") %>%
+  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), levels = c("Uninfected","Increase","Peak","Decrease")))
 
-lmer_bt=lmer(data = data2016_2020,body_temperature~Diff_Inf_Class+Diff_Inf_Class:Treatment+Ambient_Temperature_AvgC+days_resample+Age_in_days+Weight_g+Sex+Year+(1|Nest))
+# Table with sample sizes specific for growth rate data
+n4 = table(df$Diff_Inf_Class[!is.na(df$Growth_rate)])
 
-# Predicted values for each infection stage
-
-mod_bt=get_model_data(lmer_bt,type='pred',terms="Diff_Inf_Class") %>%
-  mutate(x=factor(c("Uninfected","Increase","Peak","Decrease"), levels=c("Uninfected","Increase","Peak","Decrease")))
-
-# Table with sample sizes specific for body temperature data
-
-n2=table(data2016_2020$Diff_Inf_Class[!is.na(data2016_2020$body_temperature)])
-
-mod_bt <- mod_bt %>% 
-  mutate(x = factor(c(paste0(x,"\nn=",n2)), levels=c(paste0(x,"\nn=",n2))))
+mod_gr <- mod_gr %>% 
+  mutate(x = factor(c(paste0(x,"\nn= ",n4)), levels = c(paste0(x,"\nn= ",n4))))
 
@@
 
-gg2_pred=ggplot(mod_bt)+
-  aes(x,predicted)+
-  geom_hline(yintercept = mean(mod_bt$predicted, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Body temperature")+
-  geom_errorbar(aes(ymin=mod_bt$conf.low,ymax=mod_bt$conf.high),colour="black",size=2, width=.1)+
-  geom_errorbar(aes(ymin=mod_bt$predicted-mod_bt$std.error,ymax=mod_bt$predicted+mod_bt$std.error),size=8,colour=wes_palette("Zissou1",4), width=0)+
-  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
-  theme_classic()+
-  theme(legend.position="none", axis.title.y=element_text(size=14, margin=unit(c(0,3,0,0),"mm")),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
-  geom_segment(size = .8,
-                 aes(x=1, y=40.6, xend=4, yend=40.6))+
-    geom_text(aes(x=2.5, y=40.7),
-              label="n.s.", size = 5)
-
+gg4_pred = ggplot(mod_gr) + 
+  aes(x,predicted) + 
+  geom_hline(yintercept = mean(mod_gr$predicted, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Growth rate") + 
+  geom_errorbar(aes(ymin = mod_gr$conf.low,ymax = mod_gr$conf.high),colour = "black",size = 2, width = .1) + 
+  geom_errorbar(aes(ymin = mod_gr$predicted - mod_gr$std.error,ymax = mod_gr$predicted + mod_gr$std.error), 
+                size = 8,colour = wes_palette("Zissou1",4), width = 0,) + 
+  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
+  theme_classic() + 
+  theme(legend.position = "none", 
+        axis.title.y = element_text(size = 14, margin = unit(c(0, 3, 0, 0), "mm")),
+        axis.text = element_text(size = 12),
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        plot.margin = margin(0, 0, 0, 30, "pt"),
+        plot.title = element_text(hjust = 0.5, face = "bold")) + 
+  geom_segment(size = .8, aes(x = 1, y = max(mod_gr$conf.high) + 1.2, xend = 4, yend = max(mod_gr$conf.high) + 1.2)) + 
+    geom_text(aes(x = 2.5, y = max(mod_gr$conf.high) + 2),
+              label = "n.s.", size = 5)
 ```
 
-## Body condition change
+## Summarise models
 
-```{r mixed model body condition, warning=FALSE, message=F, echo=F}
+The code below is used to summarise the model output and create Figure 4 and Table 3 as shown in the manuscript.
 
-# Model
-
-lmer_bc=lmer(data= data2016_2020,delta_body_condition~Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample+Age_in_days+Sex+Year+(1|Nest))
-
-# Predicted values for each infection stage
-
-mod_bc=get_model_data(lmer_bc,type='pred',terms="Diff_Inf_Class") %>%
-  mutate(x=factor(c("Uninfected","Increase","Peak","Decrease"), levels=c("Uninfected","Increase","Peak","Decrease")))
-
-# Table with sample sizes specific for body condition change data
-
-n3=table(data2016_2020$Diff_Inf_Class[!is.na(data2016_2020$delta_body_condition)])
-
-mod_bc <- mod_bc %>% 
-  mutate(x = factor(c(paste0(x,"\nn=",n3)), levels=c(paste0(x,"\nn=",n3))))
-
-# Plotting predicted values across infection stages
-
-gg3_pred=ggplot(mod_bc)+
-  aes(x,predicted)+
-  geom_hline(yintercept = mean(mod_bc$predicted, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Δ Body condition")+
-  geom_errorbar(aes(ymin=mod_bc$conf.low,ymax=mod_bc$conf.high),colour="black",size=2, width=.1)+
-  geom_errorbar(aes(ymin=mod_bc$predicted-mod_bc$std.error,ymax=mod_bc$predicted+mod_bc$std.error),size=8,colour=wes_palette("Zissou1",4), width=0,)+
-  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
-  geom_segment(size = .8,
-                 aes(x=1, y=max(mod_bc$conf.high)+17, xend=4, yend=max(mod_bc$conf.high)+17))+
-    geom_text(aes(x=2.5, y=max(mod_bc$conf.high)+23),
-              label="n.s.", size = 5)
-
-```
-
-## Growth rate
-
-```{r mixed model body temp, warning=FALSE, message=F, echo=F}
-
-# Model
-
-lmer_gr=lmer(data=data2016_2020,Growth_rate~Diff_Inf_Class+Diff_Inf_Class:Treatment+Sex+days_resample+Age_in_days+Year+(1|Nest))
-
-# Predicted values for each infection stages
-
-mod_gr=get_model_data(lmer_gr,type='pred',terms="Diff_Inf_Class")%>%
-  mutate(x=factor(c("Uninfected","Increase","Peak","Decrease"), levels=c("Uninfected","Increase","Peak","Decrease")))
-
-# Table with sample sizes specific for growth rate data
-
-n4=table(data2016_2020$Diff_Inf_Class[!is.na(data2016_2020$Growth_rate)])
-
-mod_gr <- mod_gr %>% 
-  mutate(x = factor(c(paste0(x,"\nn=",n4)), levels=c(paste0(x,"\nn=",n4))))
-
-# Plotting predicted values across infection stages
-
-gg4_pred=ggplot(mod_gr)+
-  aes(x,predicted)+
-  geom_hline(yintercept = mean(mod_gr$predicted, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Growth rate")+
-  geom_errorbar(aes(ymin=mod_gr$conf.low,ymax=mod_gr$conf.high),colour="black",size=2, width=.1)+
-  geom_errorbar(aes(ymin=mod_gr$predicted-mod_gr$std.error,ymax=mod_gr$predicted+mod_gr$std.error),size=8,colour=wes_palette("Zissou1",4), width=0,)+
-  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
-  theme_classic()+
-  theme(legend.position="none", axis.title.y=element_text(size=14,margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 30, "pt"), plot.title = element_text(hjust = 0.5, face="bold"))+
-  geom_segment(size = .8,
-                 aes(x=1, y=max(mod_gr$conf.high)+1.2, xend=4, yend=max(mod_gr$conf.high)+1.2))+
-    geom_text(aes(x=2.5, y=max(mod_gr$conf.high)+2),
-              label="n.s.", size = 5)
-
-```
-
-# Summary four models
-
-```{r, summary}
-
-# Figure 4
-
-fig4=gg1_pred+gg2_pred+gg3_pred+gg4_pred + plot_annotation(tag_levels = 'A')& 
+```{r}
+## Figure 4 
+## -----------------------------------------------------------------------------
+fig4 <- gg1_pred + gg2_pred + gg3_pred + gg4_pred + plot_annotation(tag_levels = 'A') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
-
 ggsave(fig4,filename = "./Figs/predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)
@@
 # Table 3
-
-sjPlot::tab_model(lmer_br,lmer_bt,lmer_bc,lmer_gr,
+## -----------------------------------------------------------------------------
+sjPlot::tab_model(
+  lmer_br,lmer_bt,lmer_bc,lmer_gr,
   show.ci50 = T ,
@@
   df.method = "kr",
-                  dv.labels = c("Breathing rate","Body temperature","Δ Body condition","Growth rate"),
-                  file = "./table_results/Table_results_lmer_physiological_parameters_p.val_kr.html")
+  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
+  file = "Table_results_lmer_physiological_parameters_p.val_kr.html")
+```
+
+## Parasitemia as explanatory variable
+
+Exploration of effects by parasitemia levels on physiology of individuals.
+
+### Breathing rate
+
+```{r mixed model breathing rate 2, warning=F, message=F}
+## Model 
+## -----------------------------------------------------------------------------
+lmer_br_para = lmer(
+  Breathing_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample + 
+    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data= df)
+
+# Predicted values for post-treament parasitemia
+
+mod_br_para=get_model_data(lmer_br_para,type = 'pred',terms = "Infection_intensity.2") %>% 
+   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))
+
+# Table with sample sizes specific for breathing rate change data
+
+m1 = table(df$Infection_intensity.2[!is.na(df$Breathing_rate)])
+
+mod_br_para <- mod_br_para %>% 
+  mutate(x = factor(c(paste0(x,"\nn= ",m1)), levels = c(paste0(x,"\nn= ",m1))))
+mod_br_para$lower_CI= c(31.11, mod_br_para$predicted[1] - 2.96, mod_br_para$predicted[1] - 6.49,mod_br_para$predicted[1] - 4.67, mod_br_para$predicted[1] - 4.63)
+mod_br_para$higher_CI= c(41.42,mod_br_para$predicted[1]+3.90,mod_br_para$predicted[1]+1.75,mod_br_para$predicted[1]+1.46,mod_br_para$predicted[1]+4.45)
+mod_br_para$se= c(2.61,1.74,2.09,1.56,2.31)
+
+# Plotting predicted values across infection intensities
+
+gg1_pred_para = ggplot(mod_br_para) + 
+  aes(as.factor(mod_br_para$x),mod_br_para$predicted) + 
+  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Breathing rate") + 
+  geom_errorbar(aes(ymin = mod_br_para$lower_CI,ymax = mod_br_para$higher_CI),colour = "black",size = 2, width = .1) + 
+  geom_errorbar(aes(ymin = mod_br_para$predicted - mod_br_para$se, ymax = mod_br_para$predicted + mod_br_para$se),
+                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
+  geom_point(color = "black", outlier.shape = NA, size = 4, width = .3) + 
+  theme_classic() + 
+  theme(legend.position = "none",
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12),
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold")) + 
+  geom_segment(size = .8, aes(x = 1, y = max(mod_br_para$higher_CI, na.rm = T) + 1.2,
+                              xend=5, yend = max(mod_br_para$higher_CI, na.rm = T) + 1.2)) + 
+    geom_text(aes(x = 3, y = max(mod_br_para$higher_CI, na.rm = T) + 2),
+              label = "n.s.", size = 5)
+```
+
+### Body temperature
+
+```{r  mixed model body temperature 2, warning=FALSE, message=F, echo=T}
+# Model
+
+lmer_bt_para = lmer(
+  body_temperature ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
+    Ambient_Temperature_AvgC + Age_in_days + Weight_g + Sex + Year + (1|Nest), data= df)
+
+# Predicted values for post-treament parasitemia
+
+mod_bt_para = get_model_data(lmer_bt_para, 
+                             type = 'pred',
+                             terms = "Infection_intensity.2") %>% 
+   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))
+
+# Table with sample sizes specific for body temperature change data
+
+m2 = table(df$Infection_intensity.2[!is.na(df$body_temperature)])
+
+mod_bt_para <- mod_bt_para %>% 
+  mutate(x = factor(c(paste0(x,"\nn= ",m2)), levels = c(paste0(x,"\nn= ",m2))))
+mod_bt_para$lower_CI= c(39.40,mod_bt_para$predicted[1] - 0.40,mod_bt_para$predicted[1] - 0.60,mod_bt_para$predicted[1] - 0.65,mod_bt_para$predicted[1] - 1.38)
+mod_bt_para$higher_CI= c(40.40,mod_bt_para$predicted[1]+0.55,mod_bt_para$predicted[1]+0.36,mod_bt_para$predicted[1]+0.19,mod_bt_para$predicted[1]+(-0.24))
+mod_bt_para$se= c(0.23,0.24,0.24,0.21,0.29)
+
+# Plotting predicted values across infection intensities
+
+gg2_pred_para = ggplot(mod_bt_para) + 
+  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted) + 
+  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm = T), linetype = "dashed") + 
+  geom_errorbar(aes(ymin = mod_bt_para$lower_CI,ymax = mod_bt_para$higher_CI),colour = "black",size = 2, width = .1) + 
+  geom_errorbar(aes(ymin = mod_bt_para$predicted - mod_bt_para$se,ymax = mod_bt_para$predicted + mod_bt_para$se),
+                size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
+  labs(x = "", y = "Body temperature") + 
+  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
+  theme_classic() + 
+  theme(legend.position = "none",
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12),
+        axis.line.x = element_blank(), 
+        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold")) + 
+  geom_segment(size = .8, aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
+                              xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2)) + 
+    geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.25),
+              label = "**", size = 8) + 
+  geom_segment(size = .8,
+                 aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2, xend=1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.05)) + 
+  geom_segment(size = .8,
+                 aes(x =5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.05, xend=5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2))
+```
+
+### Body condition change
+
+```{r mixed model body condition change 2, warning=FALSE, message=F, echo=T}
+# Model 
+lmer_bc_para <- lmer(
+  delta_body_condition ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
+    Age_in_days + Sex + Year + (1|Nest), data= df)
+
+# Predicted values for post-treament parasitemia
+
+mod_bc_para=get_model_data(lmer_bc_para,type = 'pred',terms = "Infection_intensity.2") %>% 
+   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))
+
+# Table with sample sizes specific for body condition change data
+
+m3 = table(df$Infection_intensity.2[!is.na(df$delta_body_condition)])
+
+mod_bc_para <- mod_bc_para %>% 
+  mutate(x = factor(c(paste0(x,"\nn= ",m3)), levels = c(paste0(x,"\nn= ",m3))))
+mod_bc_para$lower_CI= c(-65.99,mod_bc_para$predicted[1] - 5.71,mod_bc_para$predicted[1] - 53.27,mod_bc_para$predicted[1] - 37.05,mod_bc_para$predicted[1] - 71.88)
+mod_bc_para$higher_CI= c(25.59,mod_bc_para$predicted[1]+51.67,mod_bc_para$predicted[1]+16.43,mod_bc_para$predicted[1]+16.17,mod_bc_para$predicted[1]+4.09)
+mod_bc_para$se= c(23.20,14.57,17.69,13.51,19.29)
+
+# Plotting predicted values across infection intensities
+
+gg3_pred_para = ggplot(mod_bc_para) + 
+  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
+  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Δ Body condition") + 
+  geom_errorbar(aes(ymin = mod_bc_para$lower_CI,ymax = mod_bc_para$higher_CI),colour = "black",size = 2, width =.1) + 
+  geom_errorbar(aes(ymin = mod_bc_para$predicted-mod_bc_para$se,ymax = mod_bc_para$predicted+mod_bc_para$se),size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
+  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
+  theme_classic() + 
+  theme(legend.position = "none",
+        axis.title = element_text(size = 14),  
+        axis.text = element_text(size = 12), 
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold")) + 
+  geom_segment(size = .8,
+                 aes(x = 1, y =-105, xend=5, yend =-105)) + 
+    geom_text(aes(x =3, y =-110),
+              label= "p=0.08", size = 5) + 
+  geom_segment(size = .8,
+                 aes(x = 1, y =-105, xend=1, yend =-105+5)) + 
+  geom_segment(size = .8,
+                 aes(x =5, y =-105, xend=5, yend =-105+5))
+```
+
+### Growth rate
+
+```{r mixed model growth rate 2, warning=FALSE, message=F, echo=T}
+# Model 
+lmer_gr_para = lmer(
+  Growth_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment +
+    days_resample + Sex + Age_in_days + Year + (1|Nest), data= df)
+
+# Predicted values for post-treament parasitemia
+mod_gr_para=get_model_data(lmer_gr_para,type = 'pred',terms = "Infection_intensity.2") %>% 
+   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))
+
+# Table with sample sizes specific for growth rate data
+
+m4 = table(df$Infection_intensity.2[!is.na(df$Growth_rate)])
+
+mod_gr_para <- mod_gr_para %>% 
+  mutate(x = factor(c(paste0(x,"\nn= ",m4)), levels = c(paste0(x,"\nn= ",m4))))
+mod_gr_para$lower_CI= c(11.44,mod_gr_para$predicted[1] - 2.22,mod_gr_para$predicted[1] - 10.47,mod_gr_para$predicted[1] - 6.60,mod_gr_para$predicted[1] - 11.39)
+mod_gr_para$higher_CI= c(25.14,mod_gr_para$predicted[1]+7.08,mod_gr_para$predicted[1]+0.92,mod_gr_para$predicted[1]+1.91,mod_gr_para$predicted[1]+0.89)
+mod_gr_para$se= c(3.47,2.36,2.89,2.16,3.12)
+
+# Plotting predicted values across infection intensities
+
+gg4_pred_para = ggplot(mod_gr_para) + 
+  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted) + 
+  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Growth rate") + 
+  geom_errorbar(aes(ymin = mod_gr_para$lower_CI,ymax = mod_gr_para$higher_CI),colour = "black",size = 2, width =.1) + 
+  geom_errorbar(aes(ymin = mod_gr_para$predicted-mod_gr_para$se,ymax = mod_gr_para$predicted+mod_gr_para$se),size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
+  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
+  theme_classic() + 
+  theme(legend.position = "none", 
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12),
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold")) + 
+  geom_segment(size = .8,
+                 aes(x = 1, y =5, xend=5, yend =5)) + 
+    geom_text(aes(x =3, y =5-0.63),
+              label= "p=0.09", size = 5) + 
+  geom_segment(size = .8,
+                 aes(x = 1, y =5, xend=1, yend =5+0.5)) + 
+  geom_segment(size = .8,
+                 aes(x =5, y =5, xend=5, yend =5+0.5))
 
@@
 
-# Parasitemia as explanatory variable
-
-## Breathing rate
-
-```{r mixed model breathing rate 2, warning=F, message=F, echo=F}
-
-# Model
-
-lmer_br_para=lmer(data=data2016_2020, Breathing_rate~Infection_intensity+Infection_intensity:Treatment+days_resample+Age_in_days+Weight_g+Sex+Ambient_Temperature_AvgC+Year+(1|Nest))
-
-# Predicted values for post-treament parasitemia
-
-mod_br_para=get_model_data(lmer_br_para,type='pred',terms="Infection_intensity") %>% 
-   mutate(x=factor(c("0","1","2","3","4"), levels=c("0","1","2","3","4")))
-
-# Table with sample sizes specific for breathing rate change data
-
-m1=table(data2016_2020$Infection_intensity[!is.na(data2016_2020$Breathing_rate)])
-
-mod_br_para <- mod_br_para %>% 
-  mutate(x = factor(c(paste0(x,"\nn=",m1)), levels=c(paste0(x,"\nn=",m1))))
-mod_br_para$lower_CI=c(31.11, mod_br_para$predicted[1]-2.96, mod_br_para$predicted[1]-6.49,mod_br_para$predicted[1]-4.67, mod_br_para$predicted[1]-4.63)
-mod_br_para$higher_CI=c(41.42,mod_br_para$predicted[1]+3.90,mod_br_para$predicted[1]+1.75,mod_br_para$predicted[1]+1.46,mod_br_para$predicted[1]+4.45)
-mod_br_para$se=c(2.61,1.74,2.09,1.56,2.31)
-
-# Plotting predicted values across infection intensities
-
-gg1_pred_para=ggplot(mod_br_para)+
-  aes(as.factor(mod_br_para$x),mod_br_para$predicted)+
-  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Breathing rate")+
-  geom_errorbar(aes(ymin=mod_br_para$lower_CI,ymax=mod_br_para$higher_CI),colour="black",size=2, width=.1)+
-  geom_errorbar(aes(ymin=mod_br_para$predicted-mod_br_para$se,ymax=mod_br_para$predicted+mod_br_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
-  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
-  geom_segment(size = .8,
-                 aes(x=1, y=max(mod_br_para$higher_CI, na.rm=T)+1.2, xend=5, yend=max(mod_br_para$higher_CI, na.rm=T)+1.2))+
-    geom_text(aes(x=3, y=max(mod_br_para$higher_CI, na.rm=T)+2),
-              label="n.s.", size = 5)
-```
-
-## Body temperature
-
-```{r  mixed model body temperature 2, warning=FALSE, message=F, echo=F}
-
-# Model
-
-lmer_bt_para=lmer(data= data2016_2020,body_temperature~Infection_intensity+Infection_intensity:Treatment+days_resample+Ambient_Temperature_AvgC+Age_in_days+Weight_g+Sex+Year+(1|Nest))
-
-# Predicted values for post-treament parasitemia
-
-mod_bt_para=get_model_data(lmer_bt_para,type='pred',terms="Infection_intensity") %>% 
-   mutate(x=factor(c("0","1","2","3","4"), levels=c("0","1","2","3","4")))
-
-# Table with sample sizes specific for body temperature change data
-
-m2=table(data2016_2020$Infection_intensity[!is.na(data2016_2020$body_temperature)])
-
-mod_bt_para <- mod_bt_para %>% 
-  mutate(x = factor(c(paste0(x,"\nn=",m2)), levels=c(paste0(x,"\nn=",m2))))
-mod_bt_para$lower_CI=c(39.40,mod_bt_para$predicted[1]-0.40,mod_bt_para$predicted[1]-0.60,mod_bt_para$predicted[1]-0.65,mod_bt_para$predicted[1]-1.38)
-mod_bt_para$higher_CI=c(40.40,mod_bt_para$predicted[1]+0.55,mod_bt_para$predicted[1]+0.36,mod_bt_para$predicted[1]+0.19,mod_bt_para$predicted[1]+(-0.24))
-mod_bt_para$se=c(0.23,0.24,0.24,0.21,0.29)
-
-# Plotting predicted values across infection intensities
-
-gg2_pred_para=ggplot(mod_bt_para)+
-  aes(as.factor(mod_bt_para$x),mod_bt_para$predicted)+
-  geom_hline(yintercept = mean(mod_bt_para$predicted, na.rm=T), linetype = "dashed")+
-  geom_errorbar(aes(ymin=mod_bt_para$lower_CI,ymax=mod_bt_para$higher_CI),colour="black",size=2, width=.1)+
-  geom_errorbar(aes(ymin=mod_bt_para$predicted-mod_bt_para$se,ymax=mod_bt_para$predicted+mod_bt_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
-  labs(x="", y="Body temperature")+
-  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
-  geom_segment(size = .8,
-                 aes(x=1, y=max(mod_bt_para$higher_CI, na.rm=T)+0.2, xend=5, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.2))+
-    geom_text(aes(x=3, y=max(mod_bt_para$higher_CI, na.rm=T)+0.25),
-              label="**", size = 8)+
-  geom_segment(size = .8,
-                 aes(x=1, y=max(mod_bt_para$higher_CI, na.rm=T)+0.2, xend=1, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.05))+
-  geom_segment(size = .8,
-                 aes(x=5, y=max(mod_bt_para$higher_CI, na.rm=T)+0.05, xend=5, yend=max(mod_bt_para$higher_CI, na.rm=T)+0.2))
-```
-
-## Body condition change
-
-```{r mixed model body condition change 2, warning=FALSE, message=F, echo=F}
-
-# Model
-
-lmer_bc_para=lmer(data= data2016_2020,delta_body_condition~Infection_intensity+Infection_intensity:Treatment+days_resample+Age_in_days+Sex+Year+(1|Nest))
-
-# Predicted values for post-treament parasitemia
-
-mod_bc_para=get_model_data(lmer_bc_para,type='pred',terms="Infection_intensity") %>% 
-   mutate(x=factor(c("0","1","2","3","4"), levels=c("0","1","2","3","4")))
-
-# Table with sample sizes specific for body condition change data
-
-m3=table(data2016_2020$Infection_intensity[!is.na(data2016_2020$delta_body_condition)])
-
-mod_bc_para <- mod_bc_para %>% 
-  mutate(x = factor(c(paste0(x,"\nn=",m3)), levels=c(paste0(x,"\nn=",m3))))
-mod_bc_para$lower_CI=c(-65.99,mod_bc_para$predicted[1]-5.71,mod_bc_para$predicted[1]-53.27,mod_bc_para$predicted[1]-37.05,mod_bc_para$predicted[1]-71.88)
-mod_bc_para$higher_CI=c(25.59,mod_bc_para$predicted[1]+51.67,mod_bc_para$predicted[1]+16.43,mod_bc_para$predicted[1]+16.17,mod_bc_para$predicted[1]+4.09)
-mod_bc_para$se=c(23.20,14.57,17.69,13.51,19.29)
-
-# Plotting predicted values across infection intensities
-
-gg3_pred_para=ggplot(mod_bc_para)+
-  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted)+
-  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Δ Body condition")+
-  geom_errorbar(aes(ymin=mod_bc_para$lower_CI,ymax=mod_bc_para$higher_CI),colour="black",size=2, width=.1)+
-  geom_errorbar(aes(ymin=mod_bc_para$predicted-mod_bc_para$se,ymax=mod_bc_para$predicted+mod_bc_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
-  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
-  geom_segment(size = .8,
-                 aes(x=1, y=-105, xend=5, yend=-105))+
-    geom_text(aes(x=3, y=-110),
-              label="p=0.08", size = 5)+
-  geom_segment(size = .8,
-                 aes(x=1, y=-105, xend=1, yend=-105+5))+
-  geom_segment(size = .8,
-                 aes(x=5, y=-105, xend=5, yend=-105+5))
-
-```
-
-## Growth rate
-
-```{r mixed model growth rate 2, warning=FALSE, message=F, echo=F}
-
-# Model
-
-lmer_gr_para=lmer(data= data2016_2020,Growth_rate~Infection_intensity+Infection_intensity:Treatment+days_resample+Sex+Age_in_days+Year+(1|Nest))
-
-# Predicted values for post-treament parasitemia
-
-mod_gr_para=get_model_data(lmer_gr_para,type='pred',terms="Infection_intensity") %>% 
-   mutate(x=factor(c("0","1","2","3","4"), levels=c("0","1","2","3","4")))
-
-# Table with sample sizes specific for growth rate data
-
-m4=table(data2016_2020$Infection_intensity[!is.na(data2016_2020$Growth_rate)])
-
-mod_gr_para <- mod_gr_para %>% 
-  mutate(x = factor(c(paste0(x,"\nn=",m4)), levels=c(paste0(x,"\nn=",m4))))
-mod_gr_para$lower_CI=c(11.44,mod_gr_para$predicted[1]-2.22,mod_gr_para$predicted[1]-10.47,mod_gr_para$predicted[1]-6.60,mod_gr_para$predicted[1]-11.39)
-mod_gr_para$higher_CI=c(25.14,mod_gr_para$predicted[1]+7.08,mod_gr_para$predicted[1]+0.92,mod_gr_para$predicted[1]+1.91,mod_gr_para$predicted[1]+0.89)
-mod_gr_para$se=c(3.47,2.36,2.89,2.16,3.12)
-
-# Plotting predicted values across infection intensities
-
-gg4_pred_para=ggplot(mod_gr_para)+
-  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted)+
-  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Growth rate")+
-  geom_errorbar(aes(ymin=mod_gr_para$lower_CI,ymax=mod_gr_para$higher_CI),colour="black",size=2, width=.1)+
-  geom_errorbar(aes(ymin=mod_gr_para$predicted-mod_gr_para$se,ymax=mod_gr_para$predicted+mod_gr_para$se),size=8,colour=wes_palette("Zissou1",5), width=0,)+
-  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
-  geom_segment(size = .8,
-                 aes(x=1, y=5, xend=5, yend=5))+
-    geom_text(aes(x=3, y=5-0.63),
-              label="p=0.09", size = 5)+
-  geom_segment(size = .8,
-                 aes(x=1, y=5, xend=1, yend=5+0.5))+
-  geom_segment(size = .8,
-                 aes(x=5, y=5, xend=5, yend=5+0.5))
-
-```
-
-# Summary four models
+### Summary four models
 
 ```{r summary}
-
 # Figure 5
-
 fig5=gg1_pred_para+gg2_pred_para+gg3_pred_para+gg4_pred_para + plot_annotation(tag_levels = 'A')& 
@@
                   show.ci50 = T ,
-                  show.se = T,
                   show.stat = T,
@@
                   dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
-                  file = "./table_results/table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
+                  file = "table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
 
@@
 
-# Host health to parasitemia
+## Host health to parasitemia
 
 ```{r, warning=F,message=F}
-
-tol_resdata=data2016_2020
-
-tol_resdata$Infection_intensity=as.numeric(tol_resdata$Infection_intensity)
-tol_resdata$Diff_Inf_Class=factor(tol_resdata$Diff_Inf_Class, levels=c("Increase","Peak","Decrease"))
+tol_resdata = df
+tol_resdata$Infection_intensity.2 = as.numeric(tol_resdata$Infection_intensity.2)
+tol_resdata$Diff_Inf_Class = factor(tol_resdata$Diff_Inf_Class, levels = c("Increase","Peak","Decrease"))
 
@@
 
-tolres_mod=lm(delta_body_condition~Infection_intensity, data=tol_resdata)
+tolres_mod=lm(delta_body_condition~Infection_intensity.2, data=tol_resdata)
 
@@
 
-tolres_deltamod=lm(delta_body_condition~Infection_intensity*Diff_Inf_Class, data=tol_resdata)
+tolres_deltamod=lm(delta_body_condition~Infection_intensity.2*Diff_Inf_Class, data=tol_resdata)
 
@@
 
-lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity, var="Infection_intensity")
+lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.2, var= "Infection_intensity.2")
 
@@
 
-tolres=ggplot(data =data2016_2020[!
-data2016_2020$Infection_intensity %in% c(NA,0) & !
-data2016_2020$Diff_Inf_Class %in% NA,], aes(y=delta_body_condition,x=as.numeric(Infection_intensity),col=Diff_Inf_Class))+
-    geom_jitter(size=3, alpha=0.5)+
-    geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
-    labs(y="Body condition change",x="Parasitemia \n at second sampling", col='Infection stages')+
-    scale_x_continuous(breaks=seq(2,5,1),labels=c("1","2","3","4"))+
-    scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
-    theme_classic()+
-    theme(legend.text = element_text(size=19),legend.title = element_text(size=22), axis.text = element_text(size=16), axis.title = element_text(size=18))
+tolres <- ggplot(data = df[!df$Infection_intensity.2 %in% c(NA,0) & !df$Diff_Inf_Class %in% NA,],
+                aes(y = delta_body_condition, x = as.numeric(Infection_intensity.2), col = Diff_Inf_Class)) + 
+    geom_jitter(size = 3, alpha=0.5) + 
+    geom_smooth(alpha = 0.2, size =1.5, method='lm',se = T) + 
+    labs(y = "Body condition change",x = "Parasitemia \n at second sampling", col='Infection stages') + 
+    scale_x_continuous(breaks=seq(2,5,1),labels= c("1","2","3","4")) + 
+    scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
+    theme_classic() + 
+    theme(legend.text = element_text(size =19),legend.title = element_text(size =22), axis.text = element_text(size =16), axis.title = element_text(size =18))
 
@@
 
-# Supplementary figures
+## Supplementary figures
+
+Creating supplementary figures:
 
 ```{r}
+# Plotting observed values across infection stages
+gg1 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+  aes(Diff_Inf_Class,Breathing_rate) + 
+  geom_hline(yintercept = mean(df$Breathing_rate, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Breathing rate") + 
+  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
+  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
+               size =2.8 , width = 0.05, show.legend = FALSE, 
+               fun.max = function(x) mean(x) + sd(x),
+               fun.min = function(x) mean(x) - sd(x)) + 
+  stat_summary(fun = mean, colour = "black", geom = "point", 
+               size =5 ,show.legend = FALSE) + 
+  stat_n_text() + 
+  theme_classic() + 
+  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))
 
-# Plotting observed values across infection stages
+gg2 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+  aes(Diff_Inf_Class,body_temperature) + 
+  geom_hline(yintercept = mean(df$body_temperature, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Body temperature") + 
+  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
+  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
+               size =2.8 , width = 0.05, show.legend = FALSE, 
+               fun.max = function(x) mean(x) + sd(x),
+               fun.min = function(x) mean(x) - sd(x)) + 
+  stat_summary(fun = mean, colour = "black", geom = "point", 
+               size =5 ,show.legend = FALSE) + 
+  stat_n_text() + 
+  theme_classic() + 
+  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))
 
-gg1=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
-  aes(Diff_Inf_Class,Breathing_rate)+
-  geom_hline(yintercept = mean(data2016_2020$Breathing_rate, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Breathing rate")+
-  geom_jitter(color ="lightgrey", size=2, width=.3)+
-  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
-               size=2.8 , width=0.05, show.legend = FALSE, 
+gg3 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+  aes(Diff_Inf_Class,delta_body_condition) + 
+  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "\U0394 Body condition") + 
+  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
+  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
+               size =2.8 , width = 0.05, show.legend = FALSE, 
                fun.max = function(x) mean(x) + sd(x),
-               fun.min = function(x) mean(x) - sd(x))+
-  stat_summary(fun=mean, colour="black", geom="point", 
-               size=5 ,show.legend = FALSE)+
-  stat_n_text()+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+               fun.min = function(x) mean(x) - sd(x)) + 
+  stat_summary(fun = mean, colour = "black", geom = "point", 
+               size =5 ,show.legend = FALSE) + 
+  stat_n_text() + 
+  theme_classic() + 
+  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))
 
-gg2=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
-  aes(Diff_Inf_Class,body_temperature)+
-  geom_hline(yintercept = mean(data2016_2020$body_temperature, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Body temperature")+
-  geom_jitter(color ="lightgrey", size=2, width=.3)+
-  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
-               size=2.8 , width=0.05, show.legend = FALSE, 
+gg4 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+  aes(Diff_Inf_Class,Growth_rate) + 
+  geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Growth rate") + 
+  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
+  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
+               size =2.8 , width = 0.05, show.legend = FALSE, 
                fun.max = function(x) mean(x) + sd(x),
-               fun.min = function(x) mean(x) - sd(x))+
-  stat_summary(fun=mean, colour="black", geom="point", 
-               size=5 ,show.legend = FALSE)+
-  stat_n_text()+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
-
-gg3=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
-  aes(Diff_Inf_Class,delta_body_condition)+
-  geom_hline(yintercept = mean(data2016_2020$delta_body_condition, na.rm=T), linetype = "dashed")+
-  labs(x="", y="\U0394 Body condition")+
-  geom_jitter(color ="lightgrey", size=2, width=.3)+
-  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
-               size=2.8 , width=0.05, show.legend = FALSE, 
-               fun.max = function(x) mean(x) + sd(x),
-               fun.min = function(x) mean(x) - sd(x))+
-  stat_summary(fun=mean, colour="black", geom="point", 
-               size=5 ,show.legend = FALSE)+
-  stat_n_text()+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
-
-gg4=ggplot(data2016_2020[!data2016_2020$Diff_Inf_Class %in% NA,])+
-  aes(Diff_Inf_Class,Growth_rate)+
-  geom_hline(yintercept = mean(data2016_2020$Growth_rate, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Growth rate")+
-  geom_jitter(color ="lightgrey", size=2, width=.3)+
-  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
-               size=2.8 , width=0.05, show.legend = FALSE, 
-               fun.max = function(x) mean(x) + sd(x),
-               fun.min = function(x) mean(x) - sd(x))+
-  stat_summary(fun=mean, colour="black", geom="point", 
-               size=5 ,show.legend = FALSE)+
-  stat_n_text()+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+               fun.min = function(x) mean(x) - sd(x)) + 
+  stat_summary(fun = mean, colour = "black", geom = "point", 
+               size =5 ,show.legend = FALSE) + 
+  stat_n_text() + 
+  theme_classic() + 
+  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))
 
@@
 
-gg5=ggplot(data2016_2020[!data2016_2020$Infection_intensity %in% NA,])+
-  aes(Infection_intensity,Breathing_rate)+
-  geom_hline(yintercept = mean(data2016_2020$Breathing_rate, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Breathing rate")+
-  geom_jitter(color ="lightgrey", size=2, width=.3)+
-  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
-               size=2.8 , width=0.05, show.legend = FALSE, 
+gg5 = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+  aes(Infection_intensity.2,Breathing_rate) + 
+  geom_hline(yintercept = mean(df$Breathing_rate, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Breathing rate") + 
+  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
+  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
+               size =2.8 , width = 0.05, show.legend = FALSE, 
                fun.max = function(x) mean(x) + sd(x),
-               fun.min = function(x) mean(x) - sd(x))+
-  stat_summary(fun=mean, colour="black", geom="point", 
-               size=5 ,show.legend = FALSE)+
-  stat_n_text()+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+               fun.min = function(x) mean(x) - sd(x)) + 
+  stat_summary(fun = mean, colour = "black", geom = "point", 
+               size =5 ,show.legend = FALSE) + 
+  stat_n_text() + 
+  theme_classic() + 
+  theme(legend.position = "none",
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12),
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold"))
 
-gg6=ggplot(data2016_2020[!data2016_2020$Infection_intensity %in% NA,])+
-  aes(Infection_intensity,body_temperature)+
-  geom_hline(yintercept = mean(data2016_2020$body_temperature, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Body temperature")+
-  geom_jitter(color ="lightgrey", size=2, width=.3)+
-  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
-               size=2.8 , width=0.05, show.legend = FALSE, 
+gg6 <- ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+  aes(Infection_intensity.2,body_temperature) + 
+  geom_hline(yintercept = mean(df$body_temperature, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Body temperature") + 
+  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
+  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
+               size =2.8 , width = 0.05, show.legend = FALSE, 
                fun.max = function(x) mean(x) + sd(x),
-               fun.min = function(x) mean(x) - sd(x))+
-  stat_summary(fun=mean, colour="black", geom="point", 
-               size=5 ,show.legend = FALSE)+
-  stat_n_text()+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+               fun.min = function(x) mean(x) - sd(x)) + 
+  stat_summary(fun = mean, colour = "black", geom = "point", 
+               size =5 ,show.legend = FALSE) + 
+  stat_n_text() + 
+  theme_classic() + 
+  theme(legend.position = "none",
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12), 
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold"))
 
-gg7=ggplot(data2016_2020[!data2016_2020$Infection_intensity %in% NA,])+
-  aes(Infection_intensity,delta_body_condition)+
-  geom_hline(yintercept = mean(data2016_2020$delta_body_condition, na.rm=T), linetype = "dashed")+
-  labs(x="", y="\U0394 Body condition")+
-  geom_jitter(color ="lightgrey", size=2, width=.3)+
-  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
-               size=2.8 , width=0.05, show.legend = FALSE, 
+gg7 = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+  aes(Infection_intensity.2,delta_body_condition) + 
+  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "\U0394 Body condition") + 
+  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
+  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
+               size =2.8 , width = 0.05, show.legend = FALSE, 
                fun.max = function(x) mean(x) + sd(x),
-               fun.min = function(x) mean(x) - sd(x))+
-  stat_summary(fun=mean, colour="black", geom="point", 
-               size=5 ,show.legend = FALSE)+
-  stat_n_text()+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+               fun.min = function(x) mean(x) - sd(x)) + 
+  stat_summary(fun = mean, colour = "black", geom = "point", 
+               size =5 ,show.legend = FALSE) + 
+  stat_n_text() + 
+  theme_classic() + 
+  theme(legend.position = "none", 
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12), 
+        axis.line.x = element_blank(), 
+        axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold"))
 
-gg8=ggplot(data2016_2020[!data2016_2020$Infection_intensity %in% NA,])+
-  aes(Infection_intensity,Growth_rate)+
-  geom_hline(yintercept = mean(data2016_2020$Growth_rate, na.rm=T), linetype = "dashed")+
-  labs(x="", y="Growth rate")+
-  geom_jitter(color ="lightgrey", size=2, width=.3)+
-  stat_summary(fun=mean, colour="cornflowerblue", geom="errorbar", 
-               size=2.8 , width=0.05, show.legend = FALSE, 
+gg8 = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+  aes(Infection_intensity.2,Growth_rate) + 
+  geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Growth rate") + 
+  geom_jitter(color = "lightgrey", size = 2, width = .3) + 
+  stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
+               size =2.8 , width = 0.05, show.legend = FALSE, 
                fun.max = function(x) mean(x) + sd(x),
-               fun.min = function(x) mean(x) - sd(x))+
-  stat_summary(fun=mean, colour="black", geom="point", 
-               size=5 ,show.legend = FALSE)+
-  stat_n_text()+
-  theme_classic()+
-  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))
+               fun.min = function(x) mean(x) - sd(x)) + 
+  stat_summary(fun = mean, colour = "black", geom = "point", 
+               size =5 ,show.legend = FALSE) + 
+  stat_n_text() + 
+  theme_classic() + 
+  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))
 
@@
                se = T,
-               title = "Δ Body condition",
+               title = "\U0394 Body condition",
                axis.labels = rev(c("Year [2020]","Peak : Treatment [Malarone]","Year [2018]","Year [2019]","Sampling interval","Increase : Treatment [Malarone]","Decrease : Treatment [Malarone]","Age (days)", "Uninfected : Treatment [Malarone]","Sex [Males]","Increasing parasitemia","Decreasing parasitemia","Peak parasitemia")))
@@
                se = T,
-               title = "Δ Body condition",
+               title = "\U0394 Body condition",
                axis.labels = rev(c("Year [2020]","Year [2018]","Year [2019]","Infection intensity [2] : Treatment [Malarone]","Infection intensity 1","Sampling interval","Infection intensity [3] : Treatment [Malarone]","Infection intensity [0] : Treatment [Malarone]","Age (days)","Sex [Males]","Infection intensity 3","Infection intensity 2","Infection intensity [1] : Treatment [Malarone]","Infection intensity 4")))
@@
 ggsave(figs4,filename = "./Figs/effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
+```
+## Estimating measurment error of body temperature
+
+```{r}
+
+rTemp=read.csv2("C://Users/Tony/Documents/Phd Bielefeld/Data manip/Fieldwork_2019/Repeatability_temperatures.csv", h=T, dec='.')
+
+rTemp$ID=as.factor(rTemp$ID)
+rTemp$Date=as.Date(rTemp$Date, format='%d/%m/%y')
+rTemp$Repeat=as.factor(rTemp$Repeat)
+
+## Estimating repeatability of paired measures
+## -----------------------------------------------------------------------------
+rpt(Temperature ~ (1|ID), grname = "ID", data = rTemp, npermut = 1000, datatype = 'Gaussian')
+
+## Estimating the variance of error
+## -----------------------------------------------------------------------------
+
+rt=ddply(rTemp,.(ID),summarize,mean=mean(Temperature),sd=sd(Temperature))
+
+mean(rt$mean)
+mean(rt$sd)
 

### 2022-02-21 MS_physiology_infection.Rmd
Add files via upload

@@
 ---
-title: "R code for 'Apparent physiological costs of early-life blood parasite infection in a vertebrate host'"
+title: "R code for 'Apparent physiological costs of blood parasite infection in the early-life of a vertebrate host - only in highest infections'"
 author: "Tony Rinaud, Meinolf Ottensmann, Oliver Krüger & Nayden Chakarov"
@@
 library(patchwork)
+library(plyr)
 library(rptR)
@@
   dv.labels = c("Breathing rate","Body temperature", "\U0394 Body condition","Growth rate"),
-  file = "./Physiological_parameters_in_decreasing_control_treated.html")
+  file = "./Tables/Physiological_parameters_in_decreasing_control_treated.html")
 ```
@@
 
-```{r mixed model breathing rate, warning=F, message=F}
+```{r mixed model breathing rate}
 ## Run model
@@
 
-```{r mixed model body temp after, warning=FALSE, message=F}
+```{r mixed model body temp}
 ## Model 
@@
 
-```{r mixed model body condition, warning=FALSE, message=F}
+```{r mixed model body condition}
 ## Model 
@@
 
-```{r mixed model body temp, warning=FALSE, message=F}
+```{r mixed model growth rate}
 # Model 
@@
   dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
-  file = "Table_results_lmer_physiological_parameters_p.val_kr.html")
+  file = "./Tables/Table_results_lmer_physiological_parameters_p.val_kr.html")
 ```
@@
 
-```{r mixed model breathing rate 2, warning=F, message=F}
+```{r mixed model breathing rate 2}
 ## Model 
@@
                 size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
-  geom_point(color = "black", outlier.shape = NA, size = 4, width = .3) + 
+  geom_point(color = "black", size = 4) + 
   theme_classic() + 
@@
   labs(x = "", y = "Body temperature") + 
-  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
+  geom_point(color = "black", size =4) + 
   theme_classic() + 
@@
 
-```{r mixed model body condition change 2, warning=FALSE, message=F, echo=T}
+```{r mixed model body condition change 2}
 # Model 
@@
   geom_errorbar(aes(ymin = mod_bc_para$predicted-mod_bc_para$se,ymax = mod_bc_para$predicted+mod_bc_para$se),size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
-  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
+  geom_point(color = "black", size =4) + 
   theme_classic() + 
@@
 
-```{r mixed model growth rate 2, warning=FALSE, message=F, echo=T}
+```{r mixed model growth rate 2}
 # Model 
@@
                   dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
-                  file = "table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
+                  file = "./Tables/table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
 
@@
 ```{r, warning=F,message=F}
+
+## Infection intensity as numerical variable
+## -----------------------------------------------------------------------------
 tol_resdata = df
@@
 
-# Second sampling parasitemia
-
-## linear model testing effect of infection intensity at second sampling on body condition change
-
+## Modeling host health to Infection intensity
+## -----------------------------------------------------------------------------
 tolres_mod=lm(delta_body_condition~Infection_intensity.2, data=tol_resdata)
@@
 
-## Testing the interaction between infection stages and infection intensities
-
-## with delta body condition
-
+## Modeling host health to Infection intensity : Infection stages
+## -----------------------------------------------------------------------------
 tolres_deltamod=lm(delta_body_condition~Infection_intensity.2*Diff_Inf_Class, data=tol_resdata)
 
-## comparison of slopes among infection stages
-
+## Comparison of intercepts
+## -----------------------------------------------------------------------------
+emm=emmeans(tolres_deltamod, "Diff_Inf_Class", at=list(Infection_intensity.2=0))
+
+pairs(emm)
+
+## Pairwise comparison of slopes
+## -----------------------------------------------------------------------------
 lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.2, var= "Infection_intensity.2")
@@
 
+## Comparison of slopes to zero
+## -----------------------------------------------------------------------------
 tolre_deltasum=summary(lms_delta)
 
-## comparison of slopes to zero
-
 summary(lms_delta, infer=T)
 
-# Plotting body condition change - second infection intensity
+## Plotting body condition change with the interaction second infection intensity - infection stage
+## -----------------------------------------------------------------------------
 
@@
     geom_jitter(size = 3, alpha=0.5) + 
-    geom_smooth(alpha = 0.2, size =1.5, method='lm',se = T) + 
+    geom_smooth(alpha = 0.2, size =1.5, method='lm',se = T, width=0.2) + 
+    facet_wrap(facets = 'Diff_Inf_Class')+
     labs(y = "Body condition change",x = "Parasitemia \n at second sampling", col='Infection stages') + 
@@
     scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
-    theme_classic() + 
-    theme(legend.text = element_text(size =19),legend.title = element_text(size =22), axis.text = element_text(size =16), axis.title = element_text(size =18))
-
-# Figure 3
+    theme_pubr() +
+    annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = Inf, xend = Inf, size = 0.5) +
+    annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = -Inf, xend = -Inf, size = 0.5) +
+    theme(legend.position = "none", 
+          legend.text = element_text(size =19),
+          legend.title = element_text(size =22), 
+          axis.text = element_text(size =16), 
+          axis.title = element_text(size =18),
+          strip.text = element_text(face="bold", size=14))
+
+g <- ggplot_gtable(ggplot_build(tolres))
+stripr <- which(grepl('strip-t', g$layout$name))
+fills <- c("#3B9AB2", "#E1AF00", "#F21A00")
+k <- 1
+for (i in stripr) {
+ j <- which(grepl('rect', g$grobs[[i]]$grobs[[1]]$childrenOrder))
+g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
+k <- k+1
+}
+
+g=arrangeGrob(g)
+
+## Saving Figure 3
+## -----------------------------------------------------------------------------
 
@@
 
-ggsave(fig3,filename = "./Figs/delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
+ggsave(g,filename = "./Figs/delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
 ```
@@
 ```{r}
-# Plotting observed values across infection stages
+## Plotting observed values across infection stages
+## -----------------------------------------------------------------------------
+
 gg1 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
@@
 
-# Figure S1
+## Saving Figure S1
+## -----------------------------------------------------------------------------
 
@@
 
-# Plotting observed values across infection intensities
+## Plotting observed values across infection intensities
+## -----------------------------------------------------------------------------
 
@@
 
-# Figure S2
+## Saving figure S2
+## -----------------------------------------------------------------------------
 
@@
 
-# Plotting effect sizes of 'infection stages' models
+## Plotting effect sizes of 'infection stages' models
+## -----------------------------------------------------------------------------
 
@@
 
-# Figure S3
-
+## Saving Figure S3
+## ----------------------------------------------------------------------------- 
 figs3=pm1+pm2+pm3+pm4 + plot_annotation(tag_levels = 'A')& 
@@
 
-# Plotting effect sizes of 'infection intensities' models
+## Plotting effect sizes of 'infection intensities' models
+## -----------------------------------------------------------------------------
 
@@
 
-# Figure S4
+## Figure S4
+## -----------------------------------------------------------------------------
 
@@
 
-```{r}
-
-rTemp=read.csv2("C://Users/Tony/Documents/Phd Bielefeld/Data manip/Fieldwork_2019/Repeatability_temperatures.csv", h=T, dec='.')
+```{r, message=F, warnings=F}
+## Loading repeated temperature measures 
+## -----------------------------------------------------------------------------
+
+rTemp=read.csv2("./Repeatability_temperatures.csv", h=T, dec='.')
 
@@
 ## -----------------------------------------------------------------------------
+
 rpt(Temperature ~ (1|ID), grname = "ID", data = rTemp, npermut = 1000, datatype = 'Gaussian')
@@
 rt=ddply(rTemp,.(ID),summarize,mean=mean(Temperature),sd=sd(Temperature))
+
+## Values of mean and standard deviation of average paired body temperatures
+## -----------------------------------------------------------------------------
 

### 2022-02-22 MS_physiology_infection.Rmd
Add files via upload

@@
                          labels  =  c("Pre-treatment","Post-treatment")),
-  Infection_intensity = as.numeric(c(as.character(df$Infection_intensity.1),as.character(df$Infection_intensity))),
+  Infection_intensity = as.numeric(c(as.character(df$Infection_intensity.1),as.character(df$Infection_intensity.2))),
   Treatment = factor(c(as.character(rep(df$Treatment,2))),levels  =  c("Control","Malarone")))
@@
   labs(y = "Mean infection intensity") +
-  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1)) +
-  stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey")) +
+  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1))+
+  stat_summary(fun = mean, mapping = aes(group=Treatment), geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey"))+ 
   stat_summary(fun = mean, geom = "point",size = 5) +
@@
   theme(plot.tag = element_text(size = 16, face = "bold"))
-ggsave(Fig2,filename = "./Figs/efficiency_malarone.png",units = "px", width = 6000, height = 3000)
+ggsave(Fig2,filename = "./Figs/Fig2_efficiency_malarone.png",units = "px", width = 6000, height = 3000)
 
@@
   dv.labels = c("Breathing rate","Body temperature", "\U0394 Body condition","Growth rate"),
-  file = "./Tables/Physiological_parameters_in_decreasing_control_treated.html")
+  file = "./Tables/TableS1_Physiological_parameters_in_decreasing_control_treated.html")
 ```
@@
   theme(plot.tag = element_text(size = 16, face = "bold"))
-ggsave(fig4,filename = "./Figs/predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)
+ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)
 
@@
   dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
-  file = "./Tables/Table_results_lmer_physiological_parameters_p.val_kr.html")
+  file = "./Tables/Table3_results_lmer_physiological_parameters_p.val_kr.html")
 ```
@@
 
-ggsave(fig5,filename = "./Figs/predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)
+ggsave(fig5,filename = "./Figs/Fig5_predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)
 
@@
                   dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
-                  file = "./Tables/table_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
+                  file = "./Tables/Table4_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
 
@@
 ```{r, warning=F,message=F}
+# Results presented in Table 2
 
@@
 
-ggsave(g,filename = "./Figs/delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
+ggsave(g,filename = "./Figs/Fig3_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
 ```
@@
 
-ggsave(figs1,filename = "./Figs/observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)
+ggsave(figs1,filename = "./Figs/FigS1_observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)
 
@@
 
-ggsave(figs2,filename = "./Figs/observed_physio_param_parasitemia.png",units = "px", width = 3500, height = 3800)
+ggsave(figs2,filename = "./Figs/FigS2_observed_physio_param_parasitemia.png",units = "px", width = 3500, height = 3800)
 
@@
 
-ggsave(figs3,filename = "./Figs/effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)
+ggsave(figs3,filename = "./Figs/FigS3_effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)
 
@@
 
-ggsave(figs4,filename = "./Figs/effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
+ggsave(figs4,filename = "./Figs/FigS4_effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
 ```

### 2022-02-23 MS_physiology_infection.Rmd
Add files via upload

@@
 library(wesanderson)
+library(car)
 theme_set(theme_tidybayes() + panel_border())
@@
   mutate(Age_in_days = scale(as.numeric(Age_in_days))) %>% 
+  mutate(intensity_change = as.numeric(intensity_change)) %>% 
   mutate(Diff_Inf_Class = factor(Diff_Inf_Class, levels = c("Uninfected","Increase","Peak","Decrease")))
@@
 
-```{r}
+```{r, results='hide', message=F, warning=F,prompt=F}
+
 ## Build contingency table: Infection prevalence and treatment: First sampling
@@
   Count = c(infected_treatment[1,], uninfected_treatment[1,], infected_treatment[2,], uninfected_treatment[2,]),
-  Timepoint = rep(c("Pre-treatment","Post-treatment"), 4),
+  Timepoint = rep(c("First sampling","Second sampling"), 4),
   Treatment = rep(c("Control", "Treatment"), each = 4),
   Prevalence = rep(rep(c("Infected", "Uninfected"), each = 2),2)) %>% 
-  mutate(Timepoint = factor(Timepoint, levels = c("Pre-treatment","Post-treatment"))) %>% 
+  mutate(Timepoint = factor(Timepoint, levels = c("First sampling","Second sampling"))) %>% 
   mutate(Prevalence = factor(Prevalence, levels = c("Uninfected","Infected")))
@@
   Sampling_rank = factor(c(rep("1",length(df$Sampling_rank)),as.character(df$Sampling_rank)),levels = c("1","2"),
-                         labels  =  c("Pre-treatment","Post-treatment")),
+                         labels  =  c("First sampling","Second sampling")),
   Infection_intensity = as.numeric(c(as.character(df$Infection_intensity.1),as.character(df$Infection_intensity.2))),
@@
   aes(Sampling_rank, Infection_intensity, group = Treatment) +
-  geom_vline(xintercept  =  "Pre-treatment", linetype = "dashed", color = 'darkgrey') +
-  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color = 'darkgrey') +
+  geom_vline(xintercept  =  "First sampling", linetype = "dashed", color = 'darkgrey') +
+  geom_vline(xintercept = "Second sampling", linetype = "dashed", color = 'darkgrey') +
   labs(y = "Mean infection intensity") +
   geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1))+
-  stat_summary(fun = mean, mapping = aes(group=Treatment), geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey"))+ 
+  stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey"))+ 
   stat_summary(fun = mean, geom = "point",size = 5) +
@@
 
-## Testing for difference in mean infection intensity between Pre and Post treatment
-## -----------------------------------------------------------------------------
-mean_before_after <- data.frame(
-  Ring_no = 
-    c(df$Ring_no[df$Sampling_rank %in% 2], df$Ring_no[df$Sampling_rank %in% 2]),
-  Infection_intensity = c(as.character(df$Infection_intensity.1), as.character(df$Infection_intensity.2)),
-  Treatment = 
-    c(as.character(df$Treatment[df$Sampling_rank %in% 2]), as.character(df$Treatment[df$Sampling_rank %in% 2])),
-  Timepoint = 
-    c(rep("Pre-treatment", times = length(df$Treatment)), rep("Post-treatment", times = length(df$Infection_intensity.2)))) %>% 
-  mutate(Treatment = as.factor(Treatment)) %>% 
-  mutate(Timepoint = as.factor(Timepoint))
-
-mal = mean_before_after[mean_before_after$Treatment %in% "Malarone",]
-ctrl = mean_before_after[mean_before_after$Treatment %in% "Control",]
-first = mean_before_after[mean_before_after$Timepoint %in% "Pre-treatment",]
-
-## Pre-treatment difference in parasitic load between Treatments
-## -----------------------------------------------------------------------------
-perm.t.test(as.numeric(as.character(first$Infection_intensity)) ~ first$Treatment, progress = F)
-sd(first$Infection_intensity[first$Treatment %in% "Control"])
-
-## In malarone treated nestlings
-## -----------------------------------------------------------------------------
-perm.t.test(as.numeric(as.character(mal$Infection_intensity)) ~ mal$Timepoint, progress = F)
-
-# In control nestlings
-## -----------------------------------------------------------------------------
-perm.t.test(as.numeric(as.character(ctrl$Infection_intensity))~ctrl$Timepoint, progress = F)
+## Testing for difference in parasitic load between Treatment groups at first sampling
+## -----------------------------------------------------------------------------
+
+perm.t.test(as.numeric(as.character(df$Infection_intensity.1))~df$Treatment)
+
+## Testing for Treatment effect on parasitemia change between first and second sampling
+## -----------------------------------------------------------------------------
+
+lmerTest::lmer(intensity_change~Treatment+Year+days_resample+(1|Nest), data=df[!df$intensity_change %in% -100,]) %>%
+  summary()
 ```
@@
 ## -----------------------------------------------------------------------------
+
 tolres_mod=lm(delta_body_condition~Infection_intensity.2, data=tol_resdata)

### 2022-02-23 MS_physiology_infection.Rmd
Formatting

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, strip.white = TRUE, collapse = TRUE, fig.align = "center",
+knitr::opts_chunk$set(
+  fig.width = 8, fig.height = 8, comment = "#>",
+  echo = TRUE, strip.white = TRUE, collapse = TRUE, fig.align = "center",
   warning = F, message = F, highlight = TRUE, tidy = TRUE)
-
-# Routine clean-up upon start
-
-rm(list=ls())
 ```
@@
 
-A number of packages, all of which are available on CRAN are required to repeat analyses presented in this document. The code chunk below allows to load them for the analyses.
+A number of packages, all of which are available on CRAN are required to repeat analyses presented in this document.
+The code chunk below allows to load them for the analyses.
+Any missing package needs to be installed before, using the 'install.packages())' function:
 
@@
 library(lme4)
+library(lmerTest)
 library(lsmeans)
@@
 library(car)
+## set theme for ggplot objects
 theme_set(theme_tidybayes() + panel_border())
@@
 The raw data is comprised of 276 common buzzard (*Buteo buteo*) individuals.
-Each individual was sampled twice over the course of nestling period during the years 2016 and 2018 - 2020.
-First, the raw data is loaded from the file `physiology_infection_stage_full_wideformat.csv` and formatted (scaling variables, reordering factor levels etc.) for downstream analyses
+Each individual was sampled twice over the course of the nestling period during the years 2016 and 2018 - 2020.
+First, the raw data is loaded from the file `physiology_infection_stage_full_wideformat.csv` and re-formatted (scaling variables, reordering factor levels etc.) before downstream analyses:
 
@@
 df <- arrange(df, df$Diff_Inf_Class)
-
 ```
@@
 
-Investigating treatment effects on the prevalence of *Leucocytozoon* parasites:
+Investigating treatment (*control* vs *Malarone*) effects on the prevalence of *Leucocytozoon* parasites:
 
 ```{r, results='hide', message=F, warning=F,prompt=F}
-
 ## Build contingency table: Infection prevalence and treatment: First sampling
@@
 ## -----------------------------------------------------------------------------
-treatment_prevalence_changes  <- ggplot(tab_cont) +  
+Fig_2A  <- ggplot(tab_cont) +  
   aes(Timepoint, Count, fill = Prevalence) +  
@@
         axis.text = element_text(size = 16))
+Fig_2A
 
@@
 ## -----------------------------------------------------------------------------
-treatment_meaninf_changes = ggplot(mean_infint) +
+Fig_2B = ggplot(mean_infint) +
   aes(Sampling_rank, Infection_intensity, group = Treatment) +
@@
   labs(y = "Mean infection intensity") +
-  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1))+
-  stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey"))+ 
+  geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1)) +
+  stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey")) + 
   stat_summary(fun = mean, geom = "point",size = 5) +
@@
 ## ----------------------------------------------------------------------------- 
-Fig2 <- treatment_prevalence_changes + 
-  treatment_meaninf_changes +
+Fig2 <- Fig_2A + Fig_2B +
   plot_annotation(tag_levels = 'A') + 
   theme(plot.tag = element_text(size = 16, face = "bold"))
+
+Fig_2A
+Fig_2B
+
 ggsave(Fig2,filename = "./Figs/Fig2_efficiency_malarone.png",units = "px", width = 6000, height = 3000)
@@
 ## Testing for Treatment effect on parasitemia change between first and second sampling
-## -----------------------------------------------------------------------------
-
-lmerTest::lmer(intensity_change~Treatment+Year+days_resample+(1|Nest), data=df[!df$intensity_change %in% -100,]) %>%
+## Note: 
+## intensity change -100 codes for individuals that were uninfected throughout 
+## the experiment!
+## -----------------------------------------------------------------------------
+lmerTest::lmer(intensity_change ~ Treatment + Year + days_resample + (1|Nest), 
+               data = df[!df$intensity_change %in% -100,]) %>%
   summary()
@@
 ```{r}
+## Table S1
+## -----------------------------------------------------------------------------
 lm_d1 = lm(Breathing_rate ~ Treatment, data = df)
@@
 ```{r}
-lm_d2 <- lm(body_temperature~Treatment, data = df)
+## Table S1
+## -----------------------------------------------------------------------------
+lm_d2 <- lm(body_temperature ~ Treatment, data = df)
 summary(lm_d2)
@@
 ```{r}
+## Table S1
+## -----------------------------------------------------------------------------
 lm_d3 <- lm(delta_body_condition~Treatment, data = df)
@@
 ```{r}
+## Table S1
+## -----------------------------------------------------------------------------
 lm_d4 <- lm(Growth_rate~Treatment, data = df)
@@
 Exploring differences in physiological measures that are associated with the infection stage (increase, peak or decreasing) of tested individuals.
+All models account for a number of fixed effects and non-independence among nest mates.
 
@@
 ## -----------------------------------------------------------------------------
-gg1_pred <- ggplot(mod_br) + 
+Fig_4A <- ggplot(mod_br) + 
   aes(x,predicted) + 
@@
 # Plotting predicted values across infection stages
-gg2_pred <- ggplot(mod_bt) + 
+Fig_4B <- ggplot(mod_bt) + 
   aes(x,predicted) + 
@@
 
-gg3_pred = ggplot(mod_bc) + 
+Fig_4C = ggplot(mod_bc) + 
   aes(x,predicted) + 
@@
 # Model 
-lmer_gr = lmer(Growth_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Sex + days_resample + Age_in_days + Year + (1|Nest), data= df)
+lmer_gr = lmer(Growth_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Sex +
+                 days_resample + Age_in_days + Year + (1|Nest), data = df)
 
@@
 
-gg4_pred = ggplot(mod_gr) + 
+Fig_4D = ggplot(mod_gr) + 
   aes(x,predicted) + 
@@
 
-The code below is used to summarise the model output and create Figure 4 and Table 3 as shown in the manuscript.
+The code below is used to summarise the model output and creates Figure 4 and Table 3 as shown in the manuscript.
 
@@
 ## -----------------------------------------------------------------------------
-fig4 <- gg1_pred + gg2_pred + gg3_pred + gg4_pred + plot_annotation(tag_levels = 'A') & 
+fig4 <- Fig_4A + Fig_4B + Fig_4C + Fig_4D + plot_annotation(tag_levels = 'A') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
+fig4
+
 ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)
@@
 
-Exploration of effects by parasitemia levels on physiology of individuals.
+Exploration of effects by parasitemia levels on physiology of individuals. All models account for a number of fixed effects and non-independence among nest mates.
 
@@
 ```{r mixed model breathing rate 2}
-## Model 
+## Model:
+## Note: 
+## One Contrast for the Interaction of Infection intensity and treatment
+## is not estimatable due to the lack of infection level 4 for the Malarone-group
 ## -----------------------------------------------------------------------------
@@
   Breathing_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample + 
-    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data= df)
-
-# Predicted values for post-treament parasitemia
-
-mod_br_para=get_model_data(lmer_br_para,type = 'pred',terms = "Infection_intensity.2") %>% 
+    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data = df)
+
+## Rerun without intercept for plotting mean estimates 
+## -----------------------------------------------------------------------------
+lmer_br_para_no_intercept = lmer(
+  Breathing_rate ~ 0 + Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample + 
+    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data = df)
+
+## Obtain effect sizes for post-treatment parasitemia and derive model predictions
+## -----------------------------------------------------------------------------
+mod_br_para <- 
+  left_join(plot_model(lmer_br_para_no_intercept, se = F, )[["data"]][1:5,], ## 95% CI
+            plot_model(lmer_br_para_no_intercept, se = T, )[["data"]][1:5,]) %>%  ## SE
+  mutate(predicted = estimate) %>% 
+  mutate(lower_CI = conf.low) %>% 
+  mutate(higher_CI = conf.high) %>% 
+  mutate(se = std.error) %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))
 
-# Table with sample sizes specific for breathing rate change data
-
+## Obtain sample sizes for labels 
+## ----------------------------------------------------------------------------- 
 m1 = table(df$Infection_intensity.2[!is.na(df$Breathing_rate)])
-
 mod_br_para <- mod_br_para %>% 
   mutate(x = factor(c(paste0(x,"\nn= ",m1)), levels = c(paste0(x,"\nn= ",m1))))
-mod_br_para$lower_CI= c(31.11, mod_br_para$predicted[1] - 2.96, mod_br_para$predicted[1] - 6.49,mod_br_para$predicted[1] - 4.67, mod_br_para$predicted[1] - 4.63)
-mod_br_para$higher_CI= c(41.42,mod_br_para$predicted[1]+3.90,mod_br_para$predicted[1]+1.75,mod_br_para$predicted[1]+1.46,mod_br_para$predicted[1]+4.45)
-mod_br_para$se= c(2.61,1.74,2.09,1.56,2.31)
 
 # Plotting predicted values across infection intensities
-
-gg1_pred_para = ggplot(mod_br_para) + 
+## -----------------------------------------------------------------------------
+Fig_5A = ggplot(mod_br_para) + 
   aes(as.factor(mod_br_para$x),mod_br_para$predicted) + 
@@
   labs(x = "", y = "Breathing rate") + 
-  geom_errorbar(aes(ymin = mod_br_para$lower_CI,ymax = mod_br_para$higher_CI),colour = "black",size = 2, width = .1) + 
-  geom_errorbar(aes(ymin = mod_br_para$predicted - mod_br_para$se, ymax = mod_br_para$predicted + mod_br_para$se),
+  geom_errorbar(aes(ymin = mod_br_para$lower_CI,
+                    ymax = mod_br_para$higher_CI),colour = "black",size = 2, width = .1) + 
+  geom_errorbar(aes(ymin = mod_br_para$predicted - mod_br_para$se, 
+                    ymax = mod_br_para$predicted + mod_br_para$se),
                 size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
@@
   geom_segment(size = .8, aes(x = 1, y = max(mod_br_para$higher_CI, na.rm = T) + 1.2,
-                              xend=5, yend = max(mod_br_para$higher_CI, na.rm = T) + 1.2)) + 
+                              xend = 5, yend = max(mod_br_para$higher_CI, na.rm = T) + 1.2)) + 
     geom_text(aes(x = 3, y = max(mod_br_para$higher_CI, na.rm = T) + 2),
@@
 ```{r  mixed model body temperature 2, warning=FALSE, message=F, echo=T}
-# Model
-
+## Model:
+## Note: 
+## One Contrast for the Interaction of Infection intensity and treatment
+## is not estimatable due to the lack of infection level 4 for the Malarone-group
+## -----------------------------------------------------------------------------
 lmer_bt_para = lmer(
   body_temperature ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
-    Ambient_Temperature_AvgC + Age_in_days + Weight_g + Sex + Year + (1|Nest), data= df)
-
-# Predicted values for post-treament parasitemia
-
-mod_bt_para = get_model_data(lmer_bt_para, 
-                             type = 'pred',
-                             terms = "Infection_intensity.2") %>% 
+    Ambient_Temperature_AvgC + Age_in_days + Weight_g + Sex + Year + (1|Nest), data = df)
+
+## Rerun without intercept for plotting mean estimates 
+## -----------------------------------------------------------------------------
+lmer_bt_para_no_intercept = lmer(
+  body_temperature ~ 0 + Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
+    Ambient_Temperature_AvgC + Age_in_days + Weight_g + Sex + Year + (1|Nest), data = df)
+
+## Obtain effect sizes for post-treatment parasitemia and derive model predictions
+## -----------------------------------------------------------------------------
+mod_bt_para <- 
+  left_join(plot_model(lmer_bt_para_no_intercept, se = F, )[["data"]][1:5,], ## 95% CI
+            plot_model(lmer_bt_para_no_intercept, se = T, )[["data"]][1:5,]) %>%  ## SE
+  mutate(predicted = estimate) %>% 
+  mutate(lower_CI = conf.low) %>% 
+  mutate(higher_CI = conf.high) %>% 
+  mutate(se = std.error) %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))
 
-# Table with sample sizes specific for body temperature change data
-
+## Obtain sample sizes for labels 
+## ----------------------------------------------------------------------------- 
 m2 = table(df$Infection_intensity.2[!is.na(df$body_temperature)])
 
-mod_bt_para <- mod_bt_para %>% 
-  mutate(x = factor(c(paste0(x,"\nn= ",m2)), levels = c(paste0(x,"\nn= ",m2))))
-mod_bt_para$lower_CI= c(39.40,mod_bt_para$predicted[1] - 0.40,mod_bt_para$predicted[1] - 0.60,mod_bt_para$predicted[1] - 0.65,mod_bt_para$predicted[1] - 1.38)
-mod_bt_para$higher_CI= c(40.40,mod_bt_para$predicted[1]+0.55,mod_bt_para$predicted[1]+0.36,mod_bt_para$predicted[1]+0.19,mod_bt_para$predicted[1]+(-0.24))
-mod_bt_para$se= c(0.23,0.24,0.24,0.21,0.29)
-
-# Plotting predicted values across infection intensities
-
-gg2_pred_para = ggplot(mod_bt_para) + 
+## Plotting predicted values across infection intensities
+## -----------------------------------------------------------------------------
+Fig_5B = ggplot(mod_bt_para) + 
   aes(as.factor(mod_bt_para$x),mod_bt_para$predicted) + 
@@
   geom_errorbar(aes(ymin = mod_bt_para$predicted - mod_bt_para$se,ymax = mod_bt_para$predicted + mod_bt_para$se),
-                size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
+                size = 8,colour = wes_palette("Zissou1",5), width = 0,) + 
   labs(x = "", y = "Body temperature") + 
-  geom_point(color = "black", size =4) + 
+  geom_point(color = "black", size = 4) + 
   theme_classic() + 
@@
   geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.25),
-              label = "**", size = 8) + 
+            label = "0.006", size = 5) + 
   geom_segment(size = .8,
-                 aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2, xend=1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.05)) + 
+               aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
+                   xend = 1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.05)) + 
   geom_segment(size = .8,
-                 aes(x =5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.05, xend=5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2))
+               aes(x = 5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.05,
+                   xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2))
 ```
@@
 ```{r mixed model body condition change 2}
-# Model 
+## Model:
+## Note: 
+## One Contrast for the Interaction of Infection intensity and treatment
+## is not estimatable due to the lack of infection level 4 for the Malarone-group
+## -----------------------------------------------------------------------------
 lmer_bc_para <- lmer(
   delta_body_condition ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
-    Age_in_days + Sex + Year + (1|Nest), data= df)
-
-# Predicted values for post-treament parasitemia
-
-mod_bc_para=get_model_data(lmer_bc_para,type = 'pred',terms = "Infection_intensity.2") %>% 
+    Age_in_days + Sex + Year + (1|Nest), data = df)
+
+## Rerun without intercept for plotting mean estimates 
+## -----------------------------------------------------------------------------
+lmer_bc_para_no_intercept <- lmer(
+  delta_body_condition ~ 0+ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
+    Age_in_days + Sex + Year + (1|Nest), data = df)
+
+## Obtain effect sizes for post-treatment parasitemia and derive model predictions
+## -----------------------------------------------------------------------------
+mod_bc_para <- 
+  left_join(plot_model(lmer_bc_para_no_intercept, se = F, )[["data"]][1:5,], ## 95% CI
+            plot_model(lmer_bc_para_no_intercept, se = T, )[["data"]][1:5,]) %>%  ## SE
+  mutate(predicted = estimate) %>% 
+  mutate(lower_CI = conf.low) %>% 
+  mutate(higher_CI = conf.high) %>% 
+  mutate(se = std.error) %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))
@@
 # Table with sample sizes specific for body condition change data
-
 m3 = table(df$Infection_intensity.2[!is.na(df$delta_body_condition)])
-
 mod_bc_para <- mod_bc_para %>% 
   mutate(x = factor(c(paste0(x,"\nn= ",m3)), levels = c(paste0(x,"\nn= ",m3))))
-mod_bc_para$lower_CI= c(-65.99,mod_bc_para$predicted[1] - 5.71,mod_bc_para$predicted[1] - 53.27,mod_bc_para$predicted[1] - 37.05,mod_bc_para$predicted[1] - 71.88)
-mod_bc_para$higher_CI= c(25.59,mod_bc_para$predicted[1]+51.67,mod_bc_para$predicted[1]+16.43,mod_bc_para$predicted[1]+16.17,mod_bc_para$predicted[1]+4.09)
-mod_bc_para$se= c(23.20,14.57,17.69,13.51,19.29)
 
@@
 
-gg3_pred_para = ggplot(mod_bc_para) + 
+Fig_5C = ggplot(mod_bc_para) + 
   aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
@@
   labs(x = "", y = "Δ Body condition") + 
-  geom_errorbar(aes(ymin = mod_bc_para$lower_CI,ymax = mod_bc_para$higher_CI),colour = "black",size = 2, width =.1) + 
-  geom_errorbar(aes(ymin = mod_bc_para$predicted-mod_bc_para$se,ymax = mod_bc_para$predicted+mod_bc_para$se),size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
-  geom_point(color = "black", size =4) + 
+  geom_errorbar(aes(ymin = mod_bc_para$lower_CI, ymax = mod_bc_para$higher_CI),
+                colour = "black",size = 2, width = .1) + 
+  geom_errorbar(aes(ymin = mod_bc_para$predicted - mod_bc_para$se,
+                    ymax = mod_bc_para$predicted + mod_bc_para$se),
+                size = 8, colour = wes_palette("Zissou1",5), width = 0,) + 
+  geom_point(color = "black", size = 4) + 
   theme_classic() + 
@@
   geom_segment(size = .8,
-                 aes(x = 1, y =-105, xend=5, yend =-105)) + 
-    geom_text(aes(x =3, y =-110),
-              label= "p=0.08", size = 5) + 
+                 aes(x = 1, y = -105, xend = 5, yend = -105)) + 
+    geom_text(aes(x = 3, y = -110),
+              label = "p=0.08", size = 5) + 
   geom_segment(size = .8,
-                 aes(x = 1, y =-105, xend=1, yend =-105+5)) + 
+                 aes(x = 1, y = -105, xend = 1, yend = -105 + 5)) + 
   geom_segment(size = .8,
-                 aes(x =5, y =-105, xend=5, yend =-105+5))
+                 aes(x = 5, y = -105, xend = 5, yend = -105 + 5))
 ```
@@
 ```{r mixed model growth rate 2}
-# Model 
+## Model:
+## Note: 
+## One Contrast for the Interaction of Infection intensity and treatment
+## is not estimatable due to the lack of infection level 4 for the Malarone-group
+## -----------------------------------------------------------------------------
 lmer_gr_para = lmer(
   Growth_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment +
-    days_resample + Sex + Age_in_days + Year + (1|Nest), data= df)
-
-# Predicted values for post-treament parasitemia
-mod_gr_para=get_model_data(lmer_gr_para,type = 'pred',terms = "Infection_intensity.2") %>% 
+    days_resample + Sex + Age_in_days + Year + (1 | Nest), data = df)
+
+## Rerun without intercept for plotting mean estimates 
+## -----------------------------------------------------------------------------
+lmer_gr_para_no_intercept  = lmer(
+  Growth_rate ~ 0 + Infection_intensity.2 + Infection_intensity.2:Treatment +
+    days_resample + Sex + Age_in_days + Year + (1 | Nest), data = df)
+
+## Obtain effect sizes for post-treatment parasitemia and derive model predictions
+## -----------------------------------------------------------------------------
+mod_gr_para <- 
+  left_join(plot_model(lmer_gr_para_no_intercept, se = F, )[["data"]][1:5,], ## 95% CI
+            plot_model(lmer_gr_para_no_intercept, se = T, )[["data"]][1:5,]) %>%  ## SE
+  mutate(predicted = estimate) %>% 
+  mutate(lower_CI = conf.low) %>% 
+  mutate(higher_CI = conf.high) %>% 
+  mutate(se = std.error) %>% 
   mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))
@@
 # Table with sample sizes specific for growth rate data
-
 m4 = table(df$Infection_intensity.2[!is.na(df$Growth_rate)])
@@
   mutate(x = factor(c(paste0(x,"\nn= ",m4)), levels = c(paste0(x,"\nn= ",m4))))
-mod_gr_para$lower_CI= c(11.44,mod_gr_para$predicted[1] - 2.22,mod_gr_para$predicted[1] - 10.47,mod_gr_para$predicted[1] - 6.60,mod_gr_para$predicted[1] - 11.39)
-mod_gr_para$higher_CI= c(25.14,mod_gr_para$predicted[1]+7.08,mod_gr_para$predicted[1]+0.92,mod_gr_para$predicted[1]+1.91,mod_gr_para$predicted[1]+0.89)
-mod_gr_para$se= c(3.47,2.36,2.89,2.16,3.12)
 
 # Plotting predicted values across infection intensities
-
-gg4_pred_para = ggplot(mod_gr_para) + 
+## -----------------------------------------------------------------------------
+Fig_5D = ggplot(mod_gr_para) + 
   aes(as.factor(mod_gr_para$x),mod_gr_para$predicted) + 
@@
   labs(x = "", y = "Growth rate") + 
-  geom_errorbar(aes(ymin = mod_gr_para$lower_CI,ymax = mod_gr_para$higher_CI),colour = "black",size = 2, width =.1) + 
-  geom_errorbar(aes(ymin = mod_gr_para$predicted-mod_gr_para$se,ymax = mod_gr_para$predicted+mod_gr_para$se),size =8,colour = wes_palette("Zissou1",5), width = 0,) + 
-  geom_point(color = "black", outlier.shape = NA, size =4, width = .3) + 
+  geom_errorbar(aes(ymin = mod_gr_para$lower_CI,
+                    ymax = mod_gr_para$higher_CI), colour = "black",size = 2, width = .1) + 
+  geom_errorbar(aes(ymin = mod_gr_para$predicted - mod_gr_para$se,
+                    ymax = mod_gr_para$predicted + mod_gr_para$se),size = 8, 
+                colour = wes_palette("Zissou1",5), width = 0) + 
+  geom_point(color = "black", outlier.shape = NA, size = 4, width = .3) + 
   theme_classic() + 
@@
   geom_segment(size = .8,
-                 aes(x = 1, y =5, xend=5, yend =5)) + 
-    geom_text(aes(x =3, y =5-0.63),
-              label= "p=0.09", size = 5) + 
+               aes(x = 1, y = 4, xend = 5, yend = 4)) + 
+  geom_text(aes(x = 3, y = 5 - 0.63),
+            label = "p = 0.094", size = 5) + 
   geom_segment(size = .8,
-                 aes(x = 1, y =5, xend=1, yend =5+0.5)) + 
+               aes(x = 1, y = 4, xend = 1, yend = 4 + 0.5)) + 
   geom_segment(size = .8,
-                 aes(x =5, y =5, xend=5, yend =5+0.5))
-
+               aes(x = 5, y = 4, xend = 5, yend = 4 + 0.5))
 ```
@@
 ```{r summary}
-# Figure 5
-fig5=gg1_pred_para+gg2_pred_para+gg3_pred_para+gg4_pred_para + plot_annotation(tag_levels = 'A')& 
+## Create multipanel Figure 5
+## -----------------------------------------------------------------------------
+fig5 = Fig_5A + Fig_5B + Fig_5C + Fig_5D + plot_annotation(tag_levels = 'A') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
+fig5
 
@@
 
-# Table 4
-
-sjPlot::tab_model(lmer_br_para,lmer_bt_para,lmer_bc_para,lmer_gr_para,
+## Table 4 
+## ----------------------------------------------------------------------------- 
+sjPlot::tab_model(
+  lmer_br_para,
+  lmer_bt_para,
+  lmer_bc_para,
+  lmer_gr_para,
   show.ci50 = T ,
@@
   file = "./Tables/Table4_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
-
 ```
@@
 ## -----------------------------------------------------------------------------
-tol_resdata = df
-tol_resdata$Infection_intensity.2 = as.numeric(tol_resdata$Infection_intensity.2)
-tol_resdata$Diff_Inf_Class = factor(tol_resdata$Diff_Inf_Class, levels = c("Increase","Peak","Decrease"))
+tol_resdata <- df %>% 
+  mutate(Infection_intensity.2 = as.numeric(Infection_intensity.2)) %>% 
+  mutate(Diff_Inf_Class = factor(Diff_Inf_Class, levels = c("Increase","Peak","Decrease")))
 
@@
 ## -----------------------------------------------------------------------------
-
-tolres_mod=lm(delta_body_condition~Infection_intensity.2, data=tol_resdata)
-
+tolres_mod = lm(delta_body_condition~Infection_intensity.2, data = tol_resdata)
 summary(tolres_mod)
@@
 ## -----------------------------------------------------------------------------
-tolres_deltamod=lm(delta_body_condition~Infection_intensity.2*Diff_Inf_Class, data=tol_resdata)
+tolres_deltamod = lm(delta_body_condition ~ Infection_intensity.2*Diff_Inf_Class,
+                     data = tol_resdata)
+summary(tolres_deltamod)
 
@@
 ## -----------------------------------------------------------------------------
-emm=emmeans(tolres_deltamod, "Diff_Inf_Class", at=list(Infection_intensity.2=0))
-
+emm = emmeans(tolres_deltamod, "Diff_Inf_Class", at = list(Infection_intensity.2 = 0))
 pairs(emm)
@@
 ## -----------------------------------------------------------------------------
-lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.2, var= "Infection_intensity.2")
-
+lms_delta = lstrends(tolres_deltamod, ~ Diff_Inf_Class:Infection_intensity.2,
+                     var = "Infection_intensity.2")
 contrast(lms_delta,"pairwise")
@@
 ## -----------------------------------------------------------------------------
-tolre_deltasum=summary(lms_delta)
-
-summary(lms_delta, infer=T)
+tolre_deltasum = summary(lms_delta)
+summary(lms_delta, infer = T)
 
@@
 ## -----------------------------------------------------------------------------
-
-tolres <- ggplot(data = df[!df$Infection_intensity.2 %in% c(NA,0) & !df$Diff_Inf_Class %in% NA,],
+tolres <- 
+  ggplot(data = filter(df, !Infection_intensity.2 %in% c(NA,0), !Diff_Inf_Class %in% NA),
          aes(y = delta_body_condition, x = as.numeric(Infection_intensity.2), col = Diff_Inf_Class)) + 
-    geom_jitter(size = 3, alpha=0.5) + 
-    geom_smooth(alpha = 0.2, size =1.5, method='lm',se = T, width=0.2) + 
-    facet_wrap(facets = 'Diff_Inf_Class')+
-    labs(y = "Body condition change",x = "Parasitemia \n at second sampling", col='Infection stages') + 
-    scale_x_continuous(breaks=seq(2,5,1),labels= c("1","2","3","4")) + 
-    scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
+  geom_jitter(size = 3, alpha = 0.5) + 
+  geom_smooth(alpha = 0.2, size = 1.5, method = 'lm',se = T, width = 0.2) + 
+  facet_wrap(facets = 'Diff_Inf_Class') +
+  labs(y = "Body condition change",x = "Parasitemia \n at second sampling",
+       col = 'Infection stages') + 
+  scale_x_continuous(breaks = seq(2,5,1),labels = c("1","2","3","4")) + 
+  scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),
+                     values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
   theme_pubr() +
@@
   theme(legend.position = "none", 
-          legend.text = element_text(size =19),
-          legend.title = element_text(size =22), 
-          axis.text = element_text(size =16), 
-          axis.title = element_text(size =18),
-          strip.text = element_text(face="bold", size=14))
-
+        legend.text = element_text(size = 19),
+        legend.title = element_text(size = 22), 
+        axis.text = element_text(size = 16), 
+        axis.title = element_text(size = 18),
+        strip.text = element_text(face = "bold", size = 14))
+
+## Arrange plot for three infection stages 
+## -----------------------------------------------------------------------------
 g <- ggplot_gtable(ggplot_build(tolres))
@@
 g$grobs[[i]]$grobs[[1]]$children[[j]]$gp$fill <- fills[k]
-k <- k+1
+k <- k + 1
 }
 
-g=arrangeGrob(g)
+g = arrangeGrob(g)
 
@@
 ## -----------------------------------------------------------------------------
-
-fig3=tolres + 
+fig3 = tolres + 
   theme(plot.tag = element_text(size = 16, face = "bold"))
+fig3
 
@@
 ## ----------------------------------------------------------------------------- 
-
-gg1 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+Fig_S1A = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
   aes(Diff_Inf_Class,Breathing_rate) + 
@@
   stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
-               size =2.8 , width = 0.05, show.legend = FALSE, 
+               size = 2.8 , width = 0.05, show.legend = FALSE, 
                fun.max = function(x) mean(x) + sd(x),
@@
   stat_summary(fun = mean, colour = "black", geom = "point", 
-               size =5 ,show.legend = FALSE) + 
+               size = 5, show.legend = FALSE) + 
   stat_n_text() +  
   theme_classic() + 
-  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))
-
-gg2 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+  theme(legend.position = "none",
+        axis.title = element_text(size = 14),
+        axis.text = element_text(size = 12), 
+        axis.line.x = element_blank(), 
+        axis.ticks.x = element_blank(),
+        plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold"))
+
+Fig_S1B = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
   aes(Diff_Inf_Class,body_temperature) + 
@@
   stat_summary(fun = mean, colour = "black", geom = "point", 
-               size =5 ,show.legend = FALSE) + 
+               size = 5 ,show.legend = FALSE) + 
   stat_n_text() + 
   theme_classic() + 
-  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))
-
-gg3 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+  theme(legend.position = "none", 
+        axis.title = element_text(size = 14), 
+        axis.text = element_text(size = 12),
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold"))
+
+Fig_S1C = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
   aes(Diff_Inf_Class,delta_body_condition) + 
@@
   stat_summary(fun = mean, colour = "black", geom = "point", 
-               size =5 ,show.legend = FALSE) + 
+               size = 5 ,show.legend = FALSE) + 
   stat_n_text() + 
   theme_classic() + 
-  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))
-
-gg4 = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+  theme(legend.position = "none", 
+        axis.title = element_text(size = 14), 
+        axis.text = element_text(size = 12),
+        axis.line.x = element_blank(), 
+        axis.ticks.x = element_blank(),
+        plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold"))
+
+Fig_S1D = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
   aes(Diff_Inf_Class,Growth_rate) + 
@@
   stat_summary(fun = mean, colour = "black", geom = "point", 
-               size =5 ,show.legend = FALSE) + 
+               size = 5 ,show.legend = FALSE) + 
   stat_n_text() + 
   theme_classic() + 
-  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))
+  theme(legend.position = "none", 
+        axis.title = element_text(size = 14), 
+        axis.text = element_text(size = 12), 
+        axis.line.x = element_blank(), 
+        axis.ticks.x = element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "cm"), 
+        plot.title = element_text(hjust = 0.5, face = "bold"))
 
@@
 ## ----------------------------------------------------------------------------- 
-
-figs1=gg1+gg2+gg3+gg4 + plot_annotation(tag_levels = 'A')& 
+figs1 = Fig_S1A + Fig_S1B + Fig_S1C + Fig_S1D + plot_annotation(tag_levels = 'A') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
+figs1
 
@@
 ## ----------------------------------------------------------------------------- 
-
-gg5 = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+Fig_S2A = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
   aes(Infection_intensity.2,Breathing_rate) + 
@@
   stat_summary(fun = mean, colour = "black", geom = "point", 
-               size =5 ,show.legend = FALSE) + 
+               size = 5, show.legend = FALSE) + 
   stat_n_text() + 
@@
 
-gg6 <- ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+Fig_S2B <- ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
   aes(Infection_intensity.2,body_temperature) + 
@@
 
-gg7 = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+Fig_S2C = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
   aes(Infection_intensity.2,delta_body_condition) + 
@@
 
-gg8 = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+Fig_S2D = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
   aes(Infection_intensity.2,Growth_rate) + 
@@
   stat_summary(fun = mean, colour = "cornflowerblue", geom = "errorbar", 
-               size =2.8 , width = 0.05, show.legend = FALSE, 
+               size = 2.8, width = 0.05, show.legend = FALSE, 
                fun.max = function(x) mean(x) + sd(x),
@@
   stat_summary(fun = mean, colour = "black", geom = "point", 
-               size =5 ,show.legend = FALSE) + 
+               size = 5, show.legend = FALSE) + 
   stat_n_text() + 
   theme_classic() + 
-  theme(legend.position = "none", axis.title = element_text(size = 14),  axis.text = element_text(size = 12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face = "bold"))
+  theme(legend.position = "none", 
+        axis.title = element_text(size = 14), 
+        axis.text = element_text(size = 12),
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold"))
 
@@
 ## ----------------------------------------------------------------------------- 
-
-figs2=gg5+gg6+gg7+gg8 + plot_annotation(tag_levels = 'A')& 
+figs2 = Fig_S2A + Fig_S2B + Fig_S2C + Fig_S2D + plot_annotation(tag_levels = 'A') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
+figs2
 
@@
 ## ----------------------------------------------------------------------------- 
-
-pm1=plot_model(lmer_br,
+Fig_S3A = plot_model(
+  lmer_br,
   sort.est = T,
@@
   title = "Breathing rate",
-               axis.labels = rev(c("Increase : Treatment [Malarone]","Age (days)","Peak : Treatment [Malarone]","Decrease : Treatment [Malarone]","Uninfected : Treatment [Malarone]","Increasing parasitemia","Sex [Males]","Decreasing parasitemia","Sampling interval","Peak parasitemia","Weight (g)","Ambient temperature","Year [2019]","Year [2018]","Year [2020]")))
-
-pm2=plot_model(lmer_bt,
+  axis.labels = 
+    rev(c("Increase : Treatment [Malarone]","Age (days)",
+          "Peak : Treatment [Malarone]","Decrease : Treatment [Malarone]",
+          "Uninfected : Treatment [Malarone]","Increasing parasitemia",
+          "Sex [Males]","Decreasing parasitemia","Sampling interval",
+          "Peak parasitemia","Weight (g)","Ambient temperature",
+          "Year [2019]","Year [2018]","Year [2020]")))
+
+Fig_S3B = plot_model(
+  lmer_bt,
   sort.est = T,
@@
   title = "Body temperature",
-               axis.labels = rev(c("Peak : Treatment [Malarone]","Ambient temperature","Year [2020]","Age (days)","Decrease : Treatment [Malarone]","Weight (g)","Sex [Males]",
-"Decreasing parasitemia","Increase : Treatment [Malarone]","Increasing parasitemia","Uninfected : Treatment [Malarone]",
+  axis.labels = 
+    rev(c("Peak : Treatment [Malarone]","Ambient temperature","Year [2020]",
+          "Age (days)","Decrease : Treatment [Malarone]","Weight (g)",
+          "Sex [Males]", "Decreasing parasitemia","Increase : Treatment [Malarone]",
+          "Increasing parasitemia","Uninfected : Treatment [Malarone]",
           "Peak parasitemia","Sampling interval")))
 
-pm3=plot_model(lmer_bc,
+Fig_S3C = plot_model(
+  lmer_bc,
   sort.est = T,
@@
   title = "\U0394 Body condition",
-               axis.labels = rev(c("Year [2020]","Peak : Treatment [Malarone]","Year [2018]","Year [2019]","Sampling interval","Increase : Treatment [Malarone]","Decrease : Treatment [Malarone]","Age (days)", "Uninfected : Treatment [Malarone]","Sex [Males]","Increasing parasitemia","Decreasing parasitemia","Peak parasitemia")))
-
-pm4=plot_model(lmer_gr,
+  axis.labels =
+    rev(c("Year [2020]","Peak : Treatment [Malarone]","Year [2018]",
+          "Year [2019]","Sampling interval","Increase : Treatment [Malarone]",
+          "Decrease : Treatment [Malarone]","Age (days)",
+          "Uninfected : Treatment [Malarone]","Sex [Males]",
+          "Increasing parasitemia","Decreasing parasitemia","Peak parasitemia")))
+
+Fig_S3D = plot_model(
+  lmer_gr,
   sort.est = T,
@@
   title = "Growth rate", 
-               axis.labels = rev(c("Peak : Treatment [Malarone]","Year [2020]","Year [2018]","Sampling interval","Year [2019]","Decrease : Treatment [Malarone]","Increase : Treatment [Malarone]","Uninfected : Treatment [Malarone]","Increasing parasitemia","Decreasing parasitemia","Peak parasitemia","Sex [Males]","Age (days)")))
+  axis.labels = 
+    rev(c("Peak : Treatment [Malarone]","Year [2020]","Year [2018]",
+          "Sampling interval","Year [2019]","Decrease : Treatment [Malarone]",
+          "Increase : Treatment [Malarone]","Uninfected : Treatment [Malarone]",
+          "Increasing parasitemia","Decreasing parasitemia","Peak parasitemia",
+          "Sex [Males]","Age (days)")))
 
@@
 ## ----------------------------------------------------------------------------- 
-figs3=pm1+pm2+pm3+pm4 + plot_annotation(tag_levels = 'A')& 
+figs3 = Fig_S3A + Fig_S3B + Fig_S3C + Fig_S3D + plot_annotation(tag_levels = 'A') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
+figs3
 
@@
 ## ----------------------------------------------------------------------------- 
-
-pm5=plot_model(lmer_br_para,
+Fig_S4A = plot_model(
+  lmer_br_para,
   sort.est = T,
@@
   title = "Breathing rate",
-               axis.labels = rev(c("Infection intensity [2] : Treatment [Malarone]","Age (days)","Infection intensity 1", "Infection intensity 4", "Infection intensity [1] : Treatment [Malarone]","Infection intensity [3] : Treatment [Malarone]", "Infection intensity [0] : Treatment [Malarone]","Sex [Males]","Infection intensity 3","Sampling interval","Infection intensity 2","Weight (g)","Ambient temperature","Year [2019]","Year [2018]","Year [2020]")))
-
-pm6=plot_model(lmer_bt_para,
+  axis.labels = 
+    rev(c("Infection intensity [2] : Treatment [Malarone]","Age (days)",
+          "Infection intensity 1", "Infection intensity 4",
+          "Infection intensity [1] : Treatment [Malarone]",
+          "Infection intensity [3] : Treatment [Malarone]",
+          "Infection intensity [0] : Treatment [Malarone]",
+          "Sex [Males]","Infection intensity 3","Sampling interval",
+          "Infection intensity 2","Weight (g)","Ambient temperature",
+          "Year [2019]","Year [2018]","Year [2020]")))
+
+Fig_S4B = plot_model(
+  lmer_bt_para,
   sort.est = T,
@@
   title = "Body temperature",
-               axis.labels = rev(c("Ambient temperature","Year [2020]","Age (days)", "Infection intensity [3] : Treatment [Malarone]","Infection intensity 1", "Infection intensity [2] : Treatment [Malarone]","Weight (g)","Infection intensity 2","Sex [Males]","Infection intensity [0] : Treatment [Malarone]","Infection intensity [1] : Treatment [Malarone]","Infection intensity 3", "Sampling interval","Infection intensity 4")))
-
-pm7=plot_model(lmer_bc_para,
+  axis.labels = 
+    rev(c("Ambient temperature","Year [2020]","Age (days)",
+          "Infection intensity [3] : Treatment [Malarone]",
+          "Infection intensity 1", "Infection intensity [2] : Treatment [Malarone]",
+          "Weight (g)","Infection intensity 2","Sex [Males]",
+          "Infection intensity [0] : Treatment [Malarone]",
+          "Infection intensity [1] : Treatment [Malarone]",
+          "Infection intensity 3", "Sampling interval","Infection intensity 4")))
+
+Fig_S4C = plot_model(
+  lmer_bc_para,
   sort.est = T,
@@
   title = "\U0394 Body condition",
-               axis.labels = rev(c("Year [2020]","Year [2018]","Year [2019]","Infection intensity [2] : Treatment [Malarone]","Infection intensity 1","Sampling interval","Infection intensity [3] : Treatment [Malarone]","Infection intensity [0] : Treatment [Malarone]","Age (days)","Sex [Males]","Infection intensity 3","Infection intensity 2","Infection intensity [1] : Treatment [Malarone]","Infection intensity 4")))
-
-pm8=plot_model(lmer_gr_para,
+  axis.labels = 
+    rev(c("Year [2020]","Year [2018]","Year [2019]",
+          "Infection intensity [2] : Treatment [Malarone]",
+          "Infection intensity 1","Sampling interval",
+          "Infection intensity [3] : Treatment [Malarone]",
+          "Infection intensity [0] : Treatment [Malarone]",
+          "Age (days)","Sex [Males]","Infection intensity 3",
+          "Infection intensity 2","Infection intensity [1] : Treatment [Malarone]",
+          "Infection intensity 4")))
+
+Fig_S4D = plot_model(
+  lmer_gr_para,
   sort.est = T,
@@
   title = "Growth rate", 
-               axis.labels = rev(c("Year [2020]","Infection intensity [2] : Treatment [Malarone]","Year [2018]","Year [2019]","Sampling interval","Infection intensity 1","Infection intensity [3] : Treatment [Malarone]","Infection intensity [0] : Treatment [Malarone]","Infection intensity 3","Sex [Males]","Infection intensity 2","Age (days)","Infection intensity 4","Infection intensity [1] : Treatment [Malarone]")))
+  axis.labels = 
+    rev(c("Year [2020]","Infection intensity [2] : Treatment [Malarone]",
+          "Year [2018]","Year [2019]","Sampling interval","Infection intensity 1",
+          "Infection intensity [3] : Treatment [Malarone]",
+          "Infection intensity [0] : Treatment [Malarone]",
+          "Infection intensity 3","Sex [Males]","Infection intensity 2",
+          "Age (days)","Infection intensity 4","Infection intensity [1] : Treatment [Malarone]")))
 
@@
 ## ----------------------------------------------------------------------------- 
-
-figs4=pm5+pm6+pm7+pm8 + plot_annotation(tag_levels = 'A')& 
+figs4 = Fig_S4A + Fig_S4B + Fig_S4C + Fig_S4D + plot_annotation(tag_levels = 'A') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
+figs4
 
@@
 ```
+
 ## Estimating measurment error of body temperature
@@
 ## ----------------------------------------------------------------------------- 
-
-rTemp=read.csv2("./Repeatability_temperatures.csv", h=T, dec='.')
-
-rTemp$ID=as.factor(rTemp$ID)
-rTemp$Date=as.Date(rTemp$Date, format='%d/%m/%y')
-rTemp$Repeat=as.factor(rTemp$Repeat)
+rTemp = read.csv2("./Repeatability_temperatures.csv", h = T, dec = '.') %>% 
+  mutate(ID = as.factor(ID)) %>% 
+  mutate(Date = as.Date(Date, format = '%d/%m/%y')) %>% 
+  mutate(Repeat = as.factor(Repeat))
 
@@
 ## -----------------------------------------------------------------------------
-
 rpt(Temperature ~ (1|ID), grname = "ID", data = rTemp, npermut = 1000, datatype = 'Gaussian')
@@
 ## -----------------------------------------------------------------------------
-
-rt=ddply(rTemp,.(ID),summarize,mean=mean(Temperature),sd=sd(Temperature))
+rt = ddply(rTemp,.(ID),summarize, mean = mean(Temperature), sd = sd(Temperature))
 
@@
 ## ----------------------------------------------------------------------------- 
-
 mean(rt$mean)
 mean(rt$sd)
-
-```
+```
+
+```{r}
+sessionInfo()
+```

### 2022-02-24 MS_physiology_infection.Rmd
Add files via upload

@@
         axis.text = element_text(size = 16))
-Fig_2A
 
@@
 
-perm.t.test(as.numeric(as.character(df$Infection_intensity.1))~df$Treatment)
+perm.t.test(as.numeric(as.character(df$Infection_intensity.1))~df$Treatment, progress = F)
 
@@
 
-No treatment effect on breathing rate!
+No treatment effect on breathing rate
 
@@
     geom_text(aes(x = 3, y = max(mod_br_para$higher_CI, na.rm = T) + 2),
-              label = "n.s.", size = 5)
+              label = "n.s.", size = 6)
 ```
@@
                               xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2)) + 
-  geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.25),
-            label = "0.006", size = 5) + 
+  geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.3),
+            label = "P = 0.006", size = 5) + 
   geom_segment(size = .8,
                aes(x = 1, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.2,
-                   xend = 1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.05)) + 
+                   xend = 1, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.1)) + 
   geom_segment(size = .8,
-               aes(x = 5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.05,
+               aes(x = 5, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.1,
                    xend = 5, yend = max(mod_bt_para$higher_CI, na.rm = T) + 0.2))
@@
   geom_segment(size = .8,
-                 aes(x = 1, y = -105, xend = 5, yend = -105)) + 
-    geom_text(aes(x = 3, y = -110),
-              label = "p=0.08", size = 5) + 
+                 aes(x = 1, y = 60, xend = 5, yend = 60)) + 
+    geom_text(aes(x = 3, y = 67),
+              label = "P = 0.080", size = 5) + 
   geom_segment(size = .8,
-                 aes(x = 1, y = -105, xend = 1, yend = -105 + 5)) + 
+                 aes(x = 1, y = 60, xend = 1, yend = 53)) + 
   geom_segment(size = .8,
-                 aes(x = 5, y = -105, xend = 5, yend = -105 + 5))
+                 aes(x = 5, y = 60, xend = 5, yend = 53))
 ```
@@
   geom_segment(size = .8,
-               aes(x = 1, y = 4, xend = 5, yend = 4)) + 
-  geom_text(aes(x = 3, y = 5 - 0.63),
-            label = "p = 0.094", size = 5) + 
+               aes(x = 1, y = 30, xend = 5, yend = 30)) + 
+  geom_text(aes(x = 3, y = 31),
+            label = "P = 0.094", size = 5) + 
   geom_segment(size = .8,
-               aes(x = 1, y = 4, xend = 1, yend = 4 + 0.5)) + 
+               aes(x = 1, y = 29, xend = 1, yend = 30)) + 
   geom_segment(size = .8,
-               aes(x = 5, y = 4, xend = 5, yend = 4 + 0.5))
+               aes(x = 5, y = 29, xend = 5, yend = 30))
 ```
@@
 ## -----------------------------------------------------------------------------
-tolres_mod = lm(delta_body_condition~Infection_intensity.2, data = tol_resdata)
-summary(tolres_mod)
+lm(delta_body_condition~Infection_intensity.2, data = tol_resdata) %>%
+summary()
 
@@
 ## -----------------------------------------------------------------------------
-tolre_deltasum = summary(lms_delta)
+
 summary(lms_delta, infer = T)
@@
 stripr <- which(grepl('strip-t', g$layout$name))
-fills <- c("#3B9AB2", "#E1AF00", "#F21A00")
+fills <- c("#4CC6E5", "#F7C600", "#FF5643")
 k <- 1

### 2022-03-30 MS_physiology_infection.Rmd
Add files via upload

@@
   labs(y = "Count of nestlings") +  
-  geom_text(aes(label = Count),position  = position_stack(0.5)) +  
+  geom_text(aes(label = Count),position  = position_stack(0.5),size=5) +  
   scale_fill_manual(values = c("#D0D0D0","#A8A8A8")) + 
+  scale_x_discrete(labels = c("First\nsampling","Second\nsampling","First\nsampling","Second\nsampling"))+  
   theme(axis.title.x  =  element_blank(), 
-        strip.text = element_text(size = 16, face = "bold"),
-        legend.text = element_text(size = 14),
-        legend.title = element_text(size = 16),
-        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
-        axis.text = element_text(size = 16))
+        strip.text = element_text(size = 22, face = "bold"),
+        legend.text = element_text(size = 20),
+        legend.title = element_blank(),
+        legend.position = c(0.85, 0.90),
+        axis.title.y = element_text(size = 28, margin =  unit(c(0, 3, 0, 0), "mm")),
+        axis.text.x = element_text(size = 22, margin =  unit(c(3, 0, 0, 0), "mm")),
+        axis.text.y = element_text(size = 22, margin =  unit(c(0, 1, 0, 0), "mm")))
 
@@
 ## -----------------------------------------------------------------------------
-Fig_2B = ggplot(mean_infint) +
+Fig_2B <- ggplot(mean_infint) +
   aes(Sampling_rank, Infection_intensity, group = Treatment) +
@@
   stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey")) + 
+  scale_x_discrete(labels = c("First\nsampling","Second\nsampling"))+
   stat_summary(fun = mean, geom = "point",size = 5) +
@@
   scale_color_manual(values = c("lightgrey","black")) + 
-  theme_classic() + 
   theme(axis.title.x = element_blank(),
-        legend.text = element_text(size = 16),
-        legend.title = element_text(size = 16),
-        axis.title.y = element_text(size = 18, margin =  unit(c(0, 3, 0, 0), "mm")),
-        axis.text = element_text(size = 16),
+        legend.text = element_text(size = 20),
+        legend.title = element_text(size = 22),
+        axis.title.y = element_text(size = 28, margin =  unit(c(0, 5, 0, 0), "mm")),
+        axis.text.x = element_text(size = 22, margin =  unit(c(3, 0, 0, 0), "mm")),
+        axis.text.y = element_text(size = 22, margin =  unit(c(0, 1, 0, 3), "mm")),
         plot.margin = unit(c(0,0,0,30), "pt"))
@@
 ## ----------------------------------------------------------------------------- 
-Fig2 <- Fig_2A + Fig_2B +
-  plot_annotation(tag_levels = 'A') + 
-  theme(plot.tag = element_text(size = 16, face = "bold"))
+Fig2 <-  Fig_2A +Fig_2B+
+  plot_annotation(tag_levels = 'a') + 
+  theme(plot.tag = element_text(size = 22, face = "bold"))
 
@@
 
-## Effects on physiology
-
-Exploring effects on physiology of nestlings due to the treatment:
-
-### Breathing rate
-
-No treatment effect on breathing rate
-
-```{r}
-## Table S1
-## -----------------------------------------------------------------------------
-lm_d1 = lm(Breathing_rate ~ Treatment, data = df)
-summary(lm_d1)
-```
-
-### Body temperature
-
-No treatment effect on body temperature
-
-```{r}
-## Table S1
-## -----------------------------------------------------------------------------
-lm_d2 <- lm(body_temperature ~ Treatment, data = df)
-summary(lm_d2)
-```
-
-### Body condition change
-
-No treatment effect on body condition change
-
-```{r}
-## Table S1
-## -----------------------------------------------------------------------------
-lm_d3 <- lm(delta_body_condition~Treatment, data = df)
-summary(lm_d3)
-```
-
-### Growth rate
-
-No treatment effect on growth rates
-
-```{r}
-## Table S1
-## -----------------------------------------------------------------------------
-lm_d4 <- lm(Growth_rate~Treatment, data = df)
-summary(lm_d4)
-
-## Create Table S1
-## -----------------------------------------------------------------------------
-tab_model(
-  lm_d1,lm_d2,lm_d3,lm_d4,
-  show.reflvl = T,
-  show.ci50 = T ,
-  show.stat = T,
-  string.stat = "t",
-  pred.labels = c("Intercept","Treatment [Malarone]"),
-  dv.labels = c("Breathing rate","Body temperature", "\U0394 Body condition","Growth rate"),
-  file = "./Tables/TableS1_Physiological_parameters_in_decreasing_control_treated.html")
-```
-
 ## Infection stages as explanatory variable
@@
 ## -----------------------------------------------------------------------------
-Fig_4A <- ggplot(mod_br) + 
+Fig_S1A <- ggplot(mod_br) + 
   aes(x,predicted) + 
@@
   theme(legend.position = "none",
-        axis.title = element_text(size = 14),
-        axis.text = element_text(size = 12),
+        axis.title = element_text(size = 18),
+        axis.text = element_text(size = 16),
         axis.line.x = element_blank(), 
@@
 # Plotting predicted values across infection stages
-Fig_4B <- ggplot(mod_bt) + 
+Fig_S1B <- ggplot(mod_bt) + 
   aes(x,predicted) + 
@@
   theme(legend.position = "none",
-        axis.title.y = element_text(size = 14, margin = unit(c(0,3,0,0),"mm")), 
-        axis.text = element_text(size = 12),
+        axis.title.y = element_text(size = 18, margin = unit(c(0,3,0,0),"mm")), 
+        axis.text = element_text(size = 16),
         axis.line.x = element_blank(),
@@
 
-Fig_4C = ggplot(mod_bc) + 
+Fig_S1C = ggplot(mod_bc) + 
   aes(x,predicted) + 
@@
   theme(legend.position = "none",
-        axis.title = element_text(size = 14),
-        axis.text = element_text(size = 12),
+        axis.title = element_text(size = 18),
+        axis.text = element_text(size = 16),
         axis.line.x = element_blank(),
@@
 
-Fig_4D = ggplot(mod_gr) + 
+Fig_S1D = ggplot(mod_gr) + 
   aes(x,predicted) + 
@@
   theme(legend.position = "none", 
-        axis.title.y = element_text(size = 14, margin = unit(c(0, 3, 0, 0), "mm")),
-        axis.text = element_text(size = 12),
+        axis.title.y = element_text(size = 18, margin = unit(c(0, 3, 0, 0), "mm")),
+        axis.text = element_text(size = 16),
         axis.line.x = element_blank(),
@@
 
-## Summarise models
+## Summary four models
 
@@
 ```{r}
-## Figure 4 
-## -----------------------------------------------------------------------------
-fig4 <- Fig_4A + Fig_4B + Fig_4C + Fig_4D + plot_annotation(tag_levels = 'A') & 
-  theme(plot.tag = element_text(size = 16, face = "bold"))
-fig4
-
-ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)
-
-# Table 3
+
+# Table 1 and Table S3 
 ## -----------------------------------------------------------------------------
@@
   df.method = "kr",
+  show.df=T,
   dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
-  file = "./Tables/Table3_results_lmer_physiological_parameters_p.val_kr.html")
+  file = "./Tables/Table1_results_lmer_physiological_parameters_p.val_kr.html")
 ```
@@
 ## -----------------------------------------------------------------------------
-Fig_5A = ggplot(mod_br_para) + 
+Fig_4A = ggplot(mod_br_para) + 
   aes(as.factor(mod_br_para$x),mod_br_para$predicted) + 
@@
   theme(legend.position = "none",
-        axis.title = element_text(size = 14),
-        axis.text = element_text(size = 12),
+        axis.title = element_text(size = 20),
+        axis.text = element_text(size = 16),
         axis.line.x = element_blank(),
@@
 m2 = table(df$Infection_intensity.2[!is.na(df$body_temperature)])
+mod_bt_para <- mod_bt_para %>% 
+  mutate(x = factor(c(paste0(x,"\nn= ",m2)), levels = c(paste0(x,"\nn= ",m2))))
 
@@
 ## -----------------------------------------------------------------------------
-Fig_5B = ggplot(mod_bt_para) + 
+Fig_4B = ggplot(mod_bt_para) + 
   aes(as.factor(mod_bt_para$x),mod_bt_para$predicted) + 
@@
   theme(legend.position = "none",
-        axis.title = element_text(size = 14),
-        axis.text = element_text(size = 12),
+        axis.title = element_text(size = 20),
+        axis.text = element_text(size = 16),
         axis.line.x = element_blank(), 
@@
 
-Fig_5C = ggplot(mod_bc_para) + 
+Fig_4C = ggplot(mod_bc_para) + 
   aes(as.factor(mod_bc_para$x),mod_bc_para$predicted) + 
@@
   theme(legend.position = "none",
-        axis.title = element_text(size = 14),  
-        axis.text = element_text(size = 12), 
+        axis.title = element_text(size = 20),  
+        axis.text = element_text(size = 16), 
         axis.line.x = element_blank(),
@@
 ## -----------------------------------------------------------------------------
-Fig_5D = ggplot(mod_gr_para) + 
+Fig_4D = ggplot(mod_gr_para) + 
   aes(as.factor(mod_gr_para$x),mod_gr_para$predicted) + 
@@
   theme(legend.position = "none", 
-        axis.title = element_text(size = 14),
-        axis.text = element_text(size = 12),
+        axis.title = element_text(size = 20),
+        axis.text = element_text(size = 16),
         axis.line.x = element_blank(),
@@
 ```{r summary}
-## Create multipanel Figure 5
-## -----------------------------------------------------------------------------
-fig5 = Fig_5A + Fig_5B + Fig_5C + Fig_5D + plot_annotation(tag_levels = 'A') & 
+## Create multipanel Figure 4
+## -----------------------------------------------------------------------------
+fig4 = Fig_4A + Fig_4B + Fig_4C + Fig_4D + plot_annotation(tag_levels = 'a') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
-fig5
-
-ggsave(fig5,filename = "./Figs/Fig5_predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)
+fig4
+
+ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)
 
@@
   p.val = "kr",
+  show.df = T,
   dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
@@
   theme(legend.position = "none", 
-        legend.text = element_text(size = 19),
-        legend.title = element_text(size = 22), 
-        axis.text = element_text(size = 16), 
-        axis.title = element_text(size = 18),
-        strip.text = element_text(face = "bold", size = 14))
+        axis.text = element_text(size = 18), 
+        axis.title = element_text(size = 20),
+        strip.text = element_text(face = "bold", size = 16))
 
@@
 ```{r}
+
+figS1 <- Fig_S1A + Fig_S1B + Fig_S1C + Fig_S1D + plot_annotation(tag_levels = 'a') & 
+  theme(plot.tag = element_text(size = 16, face = "bold"))
+figS1
+
 ## Plotting observed values across infection stages
 ## -----------------------------------------------------------------------------
-Fig_S1A = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+
+ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)
+
+Fig_S2A = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
   aes(Diff_Inf_Class,Breathing_rate) + 
@@
   theme(legend.position = "none",
-        axis.title = element_text(size = 14),
-        axis.text = element_text(size = 12), 
+        axis.title = element_text(size = 20),
+        axis.text = element_text(size = 16), 
         axis.line.x = element_blank(), 
@@
 
-Fig_S1B = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+Fig_S2B = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
   aes(Diff_Inf_Class,body_temperature) + 
@@
   theme(legend.position = "none", 
-        axis.title = element_text(size = 14), 
-        axis.text = element_text(size = 12),
+        axis.title = element_text(size = 20), 
+        axis.text = element_text(size = 16),
         axis.line.x = element_blank(),
@@
 
-Fig_S1C = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+Fig_S2C = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
   aes(Diff_Inf_Class,delta_body_condition) + 
@@
   theme(legend.position = "none", 
-        axis.title = element_text(size = 14), 
-        axis.text = element_text(size = 12),
+        axis.title = element_text(size = 20), 
+        axis.text = element_text(size = 16),
         axis.line.x = element_blank(), 
@@
 
-Fig_S1D = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
+Fig_S2D = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
   aes(Diff_Inf_Class,Growth_rate) + 
@@
   theme(legend.position = "none", 
-        axis.title = element_text(size = 14), 
-        axis.text = element_text(size = 12), 
+        axis.title = element_text(size = 20), 
+        axis.text = element_text(size = 16), 
         axis.line.x = element_blank(), 
@@
 
-## Saving Figure S1
-## ----------------------------------------------------------------------------- 
-figs1 = Fig_S1A + Fig_S1B + Fig_S1C + Fig_S1D + plot_annotation(tag_levels = 'A') & 
+## Saving Figure S2
+## ----------------------------------------------------------------------------- 
+figs2 = Fig_S2A + Fig_S2B + Fig_S2C + Fig_S2D + plot_annotation(tag_levels = 'a') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
-figs1
-
-ggsave(figs1,filename = "./Figs/FigS1_observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)
+figs2
+
+ggsave(figs2,filename = "./Figs/FigS2_observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)
 
@@
 ## ----------------------------------------------------------------------------- 
-Fig_S2A = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+Fig_S3A = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
   aes(Infection_intensity.2,Breathing_rate) + 
@@
 
-Fig_S2B <- ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+Fig_S3B <- ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
   aes(Infection_intensity.2,body_temperature) + 
@@
   theme(legend.position = "none",
-        axis.title = element_text(size = 14),
-        axis.text = element_text(size = 12), 
+        axis.title = element_text(size = 20),
+        axis.text = element_text(size = 16), 
         axis.line.x = element_blank(),
@@
 
-Fig_S2C = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+Fig_S3C = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
   aes(Infection_intensity.2,delta_body_condition) + 
@@
   theme(legend.position = "none", 
-        axis.title = element_text(size = 14),
-        axis.text = element_text(size = 12), 
+        axis.title = element_text(size = 20),
+        axis.text = element_text(size = 16), 
         axis.line.x = element_blank(), 
@@
 
-Fig_S2D = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
+Fig_S3D = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
   aes(Infection_intensity.2,Growth_rate) + 
@@
 
-## Saving figure S2
-## ----------------------------------------------------------------------------- 
-figs2 = Fig_S2A + Fig_S2B + Fig_S2C + Fig_S2D + plot_annotation(tag_levels = 'A') & 
+## Saving figure S3
+## ----------------------------------------------------------------------------- 
+figs3 = Fig_S3A + Fig_S3B + Fig_S3C + Fig_S3D + plot_annotation(tag_levels = 'a') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
-figs2
-
-ggsave(figs2,filename = "./Figs/FigS2_observed_physio_param_parasitemia.png",units = "px", width = 3500, height = 3800)
+figs3
+
+ggsave(figs3,filename = "./Figs/FigS3_observed_physio_param_parasitemia.png",units = "px", width = 3500, height = 3800)
 
@@
 ## ----------------------------------------------------------------------------- 
-Fig_S3A = plot_model(
+Fig_S4A = plot_model(
   lmer_br,
@@
 
-Fig_S3B = plot_model(
+Fig_S4B = plot_model(
   lmer_bt,
@@
 
-Fig_S3C = plot_model(
+Fig_S4C = plot_model(
   lmer_bc,
@@
 
-Fig_S3D = plot_model(
+Fig_S4D = plot_model(
   lmer_gr,
@@
 
-## Saving Figure S3
-## ----------------------------------------------------------------------------- 
-figs3 = Fig_S3A + Fig_S3B + Fig_S3C + Fig_S3D + plot_annotation(tag_levels = 'A') & 
+## Saving Figure S4
+## ----------------------------------------------------------------------------- 
+figs4 = Fig_S4A + Fig_S4B + Fig_S4C + Fig_S4D + plot_annotation(tag_levels = 'a') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
-figs3
-
-ggsave(figs3,filename = "./Figs/FigS3_effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)
+figs4
+
+ggsave(figs4,filename = "./Figs/FigS4_effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)
 
@@
 ## ----------------------------------------------------------------------------- 
-Fig_S4A = plot_model(
+Fig_S5A = plot_model(
   lmer_br_para,
@@
 
-Fig_S4B = plot_model(
+Fig_S5B = plot_model(
   lmer_bt_para,
@@
 
-Fig_S4C = plot_model(
+Fig_S5C = plot_model(
   lmer_bc_para,
@@
 
-Fig_S4D = plot_model(
+Fig_S5D = plot_model(
   lmer_gr_para,
@@
 ## ----------------------------------------------------------------------------- 
-figs4 = Fig_S4A + Fig_S4B + Fig_S4C + Fig_S4D + plot_annotation(tag_levels = 'A') & 
+figs5 = Fig_S5A + Fig_S5B + Fig_S5C + Fig_S5D + plot_annotation(tag_levels = 'a') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
-figs4
-
-ggsave(figs4,filename = "./Figs/FigS4_effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
+figs5
+
+ggsave(figs5, filename = "./Figs/FigS5_effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
 ```

### 2022-03-30 MS_physiology_infection.Rmd
Add files via upload

@@
 
-## Table 4 
+## Table 2 
 ## ----------------------------------------------------------------------------- 
@@
   dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
-  file = "./Tables/Table4_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
+  file = "./Tables/Table2_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
 ```

### 2022-04-04 MS_physiology_infection.Rmd
Add files via upload

@@
   theme(axis.title.x  =  element_blank(), 
-        strip.text = element_text(size = 22, face = "bold"),
-        legend.text = element_text(size = 20),
+        strip.text = element_text(size = 26, face = "bold"),
+        legend.text = element_text(size = 24),
         legend.title = element_blank(),
@@
         axis.title.y = element_text(size = 28, margin =  unit(c(0, 3, 0, 0), "mm")),
-        axis.text.x = element_text(size = 22, margin =  unit(c(3, 0, 0, 0), "mm")),
-        axis.text.y = element_text(size = 22, margin =  unit(c(0, 1, 0, 0), "mm")))
+        axis.text.x = element_text(size = 24, margin =  unit(c(3, 0, 0, 0), "mm")),
+        axis.text.y = element_text(size = 24, margin =  unit(c(0, 1, 0, 0), "mm")))
 
@@
   theme(axis.title.x = element_blank(),
-        legend.text = element_text(size = 20),
-        legend.title = element_text(size = 22),
+        legend.text = element_text(size = 24),
+        legend.title = element_text(size = 26),
         axis.title.y = element_text(size = 28, margin =  unit(c(0, 5, 0, 0), "mm")),
-        axis.text.x = element_text(size = 22, margin =  unit(c(3, 0, 0, 0), "mm")),
-        axis.text.y = element_text(size = 22, margin =  unit(c(0, 1, 0, 3), "mm")),
+        axis.text.x = element_text(size = 26, margin =  unit(c(3, 0, 0, 0), "mm")),
+        axis.text.y = element_text(size = 26, margin =  unit(c(0, 1, 0, 3), "mm")),
         plot.margin = unit(c(0,0,0,30), "pt"))
@@
   geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.3),
-            label = "P = 0.006", size = 5) + 
+            label = "t = -2.80, df = 140, P = 0.006", size = 5) + 
   geom_segment(size = .8,
@@
     geom_text(aes(x = 3, y = 67),
-              label = "P = 0.080", size = 5) + 
+              label = "t = -1.76, df = 247, P = 0.080", size = 5) + 
   geom_segment(size = .8,
@@
   geom_text(aes(x = 3, y = 31),
-            label = "P = 0.094", size = 5) + 
+            label = "t = 2.06, df = 258, P = 0.094", size = 5) + 
   geom_segment(size = .8,
@@
                      values = c("#3B9AB2", "#E1AF00", "#F21A00")) + 
-  theme_pubr() +
+  theme_bw()+
   annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = Inf, xend = Inf, size = 0.5) +
@@
 
-ggsave(g,filename = "./Figs/Fig3_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2800)
+ggsave(g,filename = "./Figs/Fig3_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2400)
 ```

### 2022-09-19 MS_physiology_infection.Rmd
Add files via upload

@@
   geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
-  labs(x = "", y = "Δ Body condition") + 
+  labs(x = "Parasitemia", y = "Δ Body condition") + 
   geom_errorbar(aes(ymin = mod_bc_para$lower_CI, ymax = mod_bc_para$higher_CI),
@@
         axis.title = element_text(size = 20),  
+        axis.title.x = element_text(size = 20, vjust=-0.5),
         axis.text = element_text(size = 16), 
@@
   geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm = T), linetype = "dashed") + 
-  labs(x = "", y = "Growth rate") + 
+  labs(x = "Parasitemia", y = "Growth rate") + 
   geom_errorbar(aes(ymin = mod_gr_para$lower_CI,
@@
         axis.title = element_text(size = 20),
+        axis.title.x = element_text(size = 20, vjust=-0.5),
         axis.text = element_text(size = 16),
@@
   geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
-  labs(x = "", y = "\U0394 Body condition") + 
+  labs(x = "Parasitemia", y = "\U0394 Body condition") + 
   geom_jitter(color = "lightgrey", size = 2, width = .3) + 
@@
   geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
-  labs(x = "", y = "Growth rate") + 
+  labs(x = "Parasitemia", y = "Growth rate") + 
   geom_jitter(color = "lightgrey", size = 2, width = .3) + 
@@
   axis.labels = 
-    rev(c("Infection intensity [2] : Treatment [Malarone]","Age (days)",
-          "Infection intensity 1", "Infection intensity 4",
-          "Infection intensity [1] : Treatment [Malarone]",
-          "Infection intensity [3] : Treatment [Malarone]",
-          "Infection intensity [0] : Treatment [Malarone]",
-          "Sex [Males]","Infection intensity 3","Sampling interval",
-          "Infection intensity 2","Weight (g)","Ambient temperature",
+    rev(c("Parasitemia [2] : Treatment [Malarone]","Age (days)",
+          "Parasitemia 1", "Parasitemia 4",
+          "Parasitemia [1] : Treatment [Malarone]",
+          "Parasitemia [3] : Treatment [Malarone]",
+          "Parasitemia [0] : Treatment [Malarone]",
+          "Sex [Males]","Parasitemia 3","Sampling interval",
+          "Parasitemia 2","Weight (g)","Ambient temperature",
           "Year [2019]","Year [2018]","Year [2020]")))
@@
     rev(c("Ambient temperature","Year [2020]","Age (days)",
-          "Infection intensity [3] : Treatment [Malarone]",
-          "Infection intensity 1", "Infection intensity [2] : Treatment [Malarone]",
-          "Weight (g)","Infection intensity 2","Sex [Males]",
-          "Infection intensity [0] : Treatment [Malarone]",
-          "Infection intensity [1] : Treatment [Malarone]",
-          "Infection intensity 3", "Sampling interval","Infection intensity 4")))
+          "Parasitemia [3] : Treatment [Malarone]",
+          "Parasitemia 1", "Parasitemia [2] : Treatment [Malarone]",
+          "Weight (g)","Parasitemia 2","Sex [Males]",
+          "Parasitemia [0] : Treatment [Malarone]",
+          "Parasitemia [1] : Treatment [Malarone]",
+          "Parasitemia 3", "Sampling interval","Parasitemia 4")))
 
@@
     rev(c("Year [2020]","Year [2018]","Year [2019]",
-          "Infection intensity [2] : Treatment [Malarone]",
-          "Infection intensity 1","Sampling interval",
-          "Infection intensity [3] : Treatment [Malarone]",
-          "Infection intensity [0] : Treatment [Malarone]",
-          "Age (days)","Sex [Males]","Infection intensity 3",
-          "Infection intensity 2","Infection intensity [1] : Treatment [Malarone]",
-          "Infection intensity 4")))
+          "Parasitemia [2] : Treatment [Malarone]",
+          "Parasitemia 1","Sampling interval",
+          "Parasitemia [3] : Treatment [Malarone]",
+          "Parasitemia [0] : Treatment [Malarone]",
+          "Age (days)","Sex [Males]","Parasitemia 3",
+          "Parasitemia 2","Parasitemia [1] : Treatment [Malarone]",
+          "Parasitemia 4")))
 
@@
   axis.labels = 
-    rev(c("Year [2020]","Infection intensity [2] : Treatment [Malarone]",
-          "Year [2018]","Year [2019]","Sampling interval","Infection intensity 1",
-          "Infection intensity [3] : Treatment [Malarone]",
-          "Infection intensity [0] : Treatment [Malarone]",
-          "Infection intensity 3","Sex [Males]","Infection intensity 2",
-          "Age (days)","Infection intensity 4","Infection intensity [1] : Treatment [Malarone]")))
+    rev(c("Year [2020]","Parasitemia [2] : Treatment [Malarone]",
+          "Year [2018]","Year [2019]","Sampling interval","Parasitemia 1",
+          "Parasitemia [3] : Treatment [Malarone]",
+          "Parasitemia [0] : Treatment [Malarone]",
+          "Parasitemia 3","Sex [Males]","Parasitemia 2",
+          "Age (days)","Parasitemia 4","Parasitemia [1] : Treatment [Malarone]")))
 

### 2023-03-24 MS_physiology_infection.Rmd
explicited timepoints in figures and tables

@@
   read.csv('./physiology_infection_stage_full_wideformat.csv', h = T, sep = ';', dec = ".") %>% 
+  mutate(Age_unz = as.numeric(Age_in_days)) %>%
+  mutate(Age_unz.1 = as.numeric(Age_unz - days_resample)) %>% 
+  mutate(days_resample_unz = days_resample) %>%
+  mutate(Age_in_days_unz = as.numeric(Age_in_days)) %>%
   mutate(Nest = as.factor(Nest)) %>% 
@@
 ```{r, results='hide', message=F, warning=F,prompt=F}
+
+## Testing for differences in age at first and second sampling
+## -----------------------------------------------------------------------------
+# First
+t.test(df$Age_unz.1[df$Treatment %in% "Malarone"], df$Age_unz.1[df$Treatment %in% 'Control'])
+
+#Second
+
+t.test(df$Age_unz[df$Treatment %in% "Malarone"], df$Age_unz[df$Treatment %in% 'Control'])
+
 ## Build contingency table: Infection prevalence and treatment: First sampling
@@
   matrix(c(pre_treatment[2,], post_treatment[2,]), nrow = 2) %>% 
-  set_colnames(., c("Pre", "Post")) %>% 
+  set_colnames(., c("First sampling", "Second sampling")) %>% 
   set_rownames(., c("Control", "Malarone"))
@@
   matrix(c(pre_treatment[1,], post_treatment[1,]), nrow = 2) %>% 
-  set_colnames(., c("Pre", "Post")) %>% 
+  set_colnames(., c("First sampling", "Second sampling")) %>% 
   set_rownames(., c("Control", "Malarone"))
@@
   Count = c(infected_treatment[1,], uninfected_treatment[1,], infected_treatment[2,], uninfected_treatment[2,]),
-  Timepoint = rep(c("First sampling","Second sampling"), 4),
+  Timepoint = rep(c("First sampling", "Second sampling"), 4),
   Treatment = rep(c("Control", "Treatment"), each = 4),
   Prevalence = rep(rep(c("Infected", "Uninfected"), each = 2),2)) %>% 
-  mutate(Timepoint = factor(Timepoint, levels = c("First sampling","Second sampling"))) %>% 
+  mutate(Timepoint = factor(Timepoint, levels = c("First sampling", "Second sampling"))) %>% 
   mutate(Prevalence = factor(Prevalence, levels = c("Uninfected","Infected")))
@@
   scale_fill_manual(values = c("#D0D0D0","#A8A8A8")) + 
-  scale_x_discrete(labels = c("First\nsampling","Second\nsampling","First\nsampling","Second\nsampling"))+  
+  scale_x_discrete(labels = c("First\nsampling", "Second\nsampling", 
+                              "First\nsampling", "Second\nsampling"))+  
   theme(axis.title.x  =  element_blank(), 
@@
         axis.title.y = element_text(size = 28, margin =  unit(c(0, 3, 0, 0), "mm")),
-        axis.text.x = element_text(size = 24, margin =  unit(c(3, 0, 0, 0), "mm")),
+        axis.text.x = element_text(size = 22, margin =  unit(c(3, 0, 0, 0), "mm")),
         axis.text.y = element_text(size = 24, margin =  unit(c(0, 1, 0, 0), "mm")))
@@
   Sampling_rank = factor(c(rep("1",length(df$Sampling_rank)),as.character(df$Sampling_rank)),levels = c("1","2"),
-                         labels  =  c("First sampling","Second sampling")),
+                         labels  =  c(bquote("T"[0]), bquote("T"[1]))),
   Infection_intensity = as.numeric(c(as.character(df$Infection_intensity.1),as.character(df$Infection_intensity.2))),
@@
   geom_vline(xintercept = "Second sampling", linetype = "dashed", color = 'darkgrey') +
-  labs(y = "Mean infection intensity") +
+  labs(y = "Infection intensity (Mean +/- s.e.)") +
   geom_point(aes(colour = Treatment),position = position_jitterdodge(jitter.height  =  0.1)) +
   stat_summary(fun = mean, geom = "line",size = 2,color = c("lightgrey","black","black","lightgrey")) + 
-  scale_x_discrete(labels = c("First\nsampling","Second\nsampling"))+
+  scale_x_discrete(labels = c("First sampling","Second sampling"))+
   stat_summary(fun = mean, geom = "point",size = 5) +
@@
   theme(axis.title.x = element_blank(),
-        legend.text = element_text(size = 24),
+        legend.text = element_text(size = 22),
         legend.title = element_text(size = 26),
@@
 lmer_br <- lmer(
-  Breathing_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + 
-    days_resample + Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest),
+  Breathing_rate ~ Diff_Inf_Class + Treatment + 
+     Age_in_days + days_resample + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest),
   data = df)
@@
   geom_hline(yintercept = mean(mod_br$predicted, na.rm = T), linetype = "dashed") + 
-  labs(x = "", y = "Breathing rate") + 
+  labs(x = "", y = bquote("Breathing rate at T"[1])) + 
   ylim(c(min(mod_br$conf.low) - 1.5,max(mod_br$conf.high) + 1.5)) + 
@@
 lmer_bt = lmer(
-  body_temperature ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Ambient_Temperature_AvgC + 
-    days_resample + Age_in_days + Weight_g + Sex + Year + (1|Nest),
+  body_temperature ~ Diff_Inf_Class + Treatment + Ambient_Temperature_AvgC + 
+    Age_in_days + days_resample + Weight_g + Sex + Year + (1|Nest),
   data = df)
@@
   geom_hline(yintercept = mean(mod_bt$predicted, na.rm = T), linetype = "dashed") + 
-  labs(x = "", y = "Body temperature") + 
+  labs(x = "", y = bquote("Body temperature at T"[1])) + 
   geom_errorbar(aes(ymin = mod_bt$conf.low,ymax = mod_bt$conf.high),colour = "black",size = 2, width = .1) + 
@@
 lmer_bc <- lmer(
-  delta_body_condition ~ Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample + 
-    Age_in_days+Sex+Year+(1|Nest),
+  delta_body_condition ~ Diff_Inf_Class + Treatment + Age_in_days + days_resample +
+    Sex + Year + (1|Nest),
   data = df)
@@
 # Model 
-lmer_gr = lmer(Growth_rate ~ Diff_Inf_Class + Diff_Inf_Class:Treatment + Sex +
-                 days_resample + Age_in_days + Year + (1|Nest), data = df)
+lmer_gr = lmer(Growth_rate ~ Diff_Inf_Class + Treatment + Sex +
+                Age_in_days + days_resample + Year + (1|Nest), data = df)
 
@@
   show.df=T,
-  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
-  file = "./Tables/Table1_results_lmer_physiological_parameters_p.val_kr.html")
+  dv.labels = c(bquote("Breathing rate at T"[1]),
+                bquote("Body temperature at T"[1]),
+                "\U0394 Body condition",
+                "Growth rate"),
+  file = "./Tables/Table1_results_lmer_physiological_parameters_p.val_kr_Treatment.html")
 ```
@@
 lmer_br_para = lmer(
-  Breathing_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample + 
-    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data = df)
+  Breathing_rate ~ Infection_intensity.2 + Treatment + Age_in_days + days_resample +
+    Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data = df)
 
@@
 lmer_br_para_no_intercept = lmer(
-  Breathing_rate ~ 0 + Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample + 
-    Age_in_days + Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data = df)
+  Breathing_rate ~ 0 + Infection_intensity.2 + Treatment + Age_in_days + days_resample + 
+    Weight_g + Sex + Ambient_Temperature_AvgC + Year + (1|Nest), data = df)
 
@@
   geom_hline(yintercept = mean(mod_br_para$predicted, na.rm = T), linetype = "dashed") + 
-  labs(x = "", y = "Breathing rate") + 
+  labs(x = "", y = bquote("Breathing rate at T"[1])) + 
   geom_errorbar(aes(ymin = mod_br_para$lower_CI,
@@
     geom_text(aes(x = 3, y = max(mod_br_para$higher_CI, na.rm = T) + 2),
-              label = "n.s.", size = 6)
+              label = "P = 0.15", size = 6)
 ```
@@
 lmer_bt_para = lmer(
-  body_temperature ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
-    Ambient_Temperature_AvgC + Age_in_days + Weight_g + Sex + Year + (1|Nest), data = df)
+  body_temperature ~ Infection_intensity.2 + Treatment + Age_in_days + days_resample +
+    Ambient_Temperature_AvgC + Weight_g + Sex + Year + (1|Nest), data = df)
 
@@
 lmer_bt_para_no_intercept = lmer(
-  body_temperature ~ 0 + Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
+  body_temperature ~ 0 + Infection_intensity.2 + Treatment + days_resample +
     Ambient_Temperature_AvgC + Age_in_days + Weight_g + Sex + Year + (1|Nest), data = df)
@@
                 size = 8,colour = wes_palette("Zissou1",5), width = 0,) + 
-  labs(x = "", y = "Body temperature") + 
+  labs(x = "", y = bquote("Body temperature at T"[1])) + 
   geom_point(color = "black", size = 4) + 
@@
   geom_text(aes(x = 3, y = max(mod_bt_para$higher_CI, na.rm = T) + 0.3),
-            label = "t = -2.80, df = 140, P = 0.006", size = 5) + 
+            label = "P = 0.006", size = 5) + 
   geom_segment(size = .8,
@@
 lmer_bc_para <- lmer(
-  delta_body_condition ~ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
-    Age_in_days + Sex + Year + (1|Nest), data = df)
+  delta_body_condition ~ Infection_intensity.2 + Treatment + Age_in_days + days_resample +
+    Sex + Year + (1|Nest), data = df)
 
@@
 lmer_bc_para_no_intercept <- lmer(
-  delta_body_condition ~ 0+ Infection_intensity.2 + Infection_intensity.2:Treatment + days_resample +
-    Age_in_days + Sex + Year + (1|Nest), data = df)
+  delta_body_condition ~ 0+ Infection_intensity.2 + Treatment + Age_in_days + days_resample +
+    Sex + Year + (1|Nest), data = df)
 
@@
   geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm = T), linetype = "dashed") + 
-  labs(x = "Parasitemia", y = "Δ Body condition") + 
+  labs(x = bquote("Parasitemia at T"[1]), y = "Δ Body condition") + 
   geom_errorbar(aes(ymin = mod_bc_para$lower_CI, ymax = mod_bc_para$higher_CI),
@@
     geom_text(aes(x = 3, y = 67),
-              label = "t = -1.76, df = 247, P = 0.080", size = 5) + 
+              label = "P = 0.067", size = 5) + 
   geom_segment(size = .8,
@@
 lmer_gr_para = lmer(
-  Growth_rate ~ Infection_intensity.2 + Infection_intensity.2:Treatment +
-    days_resample + Sex + Age_in_days + Year + (1 | Nest), data = df)
+  Growth_rate ~ Infection_intensity.2 + Treatment +
+   Age_in_days + days_resample + Sex +  Year + (1 | Nest), data = df)
 
@@
 lmer_gr_para_no_intercept  = lmer(
-  Growth_rate ~ 0 + Infection_intensity.2 + Infection_intensity.2:Treatment +
-    days_resample + Sex + Age_in_days + Year + (1 | Nest), data = df)
+  Growth_rate ~ 0 + Infection_intensity.2 + Treatment +
+    Age_in_days + days_resample + Sex +  Year + (1 | Nest), data = df)
 
@@
   geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm = T), linetype = "dashed") + 
-  labs(x = "Parasitemia", y = "Growth rate") + 
+  labs(x = bquote("Parasitemia at T"[1]), y = "Growth rate") + 
   geom_errorbar(aes(ymin = mod_gr_para$lower_CI,
@@
   geom_text(aes(x = 3, y = 31),
-            label = "t = 2.06, df = 258, P = 0.094", size = 5) + 
+            label = "P = 0.087", size = 5) + 
   geom_segment(size = .8,
@@
 
-ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)
+ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities_Treatment.png",units = "px", width = 3700, height = 3700)
 
@@
   show.ci50 = T ,
+  show.df = T,
   show.stat = T,
@@
   p.val = "kr",
-  show.df = T,
-  dv.labels = c("Breathing rate","Body temperature","\U0394 Body condition","Growth rate"),
-  file = "./Tables/Table2_results_parasitemia_lmer_physiological_parameters_p.val_kr.html")
+  dv.labels = c(bquote("Breathing rate at T"[1]),
+                bquote("Body temperature at T"[1]),
+                "\U0394 Body condition",
+                "Growth rate"),
+  file = "./Tables/Table2_results_parasitemia_lmer_physiological_parameters_p.val_kr_Treatment.html")
 ```
@@
   ggplot(data = filter(df, !Infection_intensity.2 %in% c(NA,0), !Diff_Inf_Class %in% NA),
+         aes(y = delta_body_condition, x = as.numeric(Infection_intensity.2))) + 
+  geom_jitter(size = 2, alpha = 0.5, width=0.2) +
+  geom_line(y=0, linetype='dashed')+
+  geom_smooth(alpha = 0.2, size = 1.5, method = 'lm',se = T, width = 0.2) + 
+  labs(y = "\U0394 Body condition", x = bquote("Parasitemia at T"[1])) + 
+  scale_x_continuous(breaks = seq(2,5,1),labels = c("1","2","3","4")) + 
+  theme_bw()+
+  annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = Inf, xend = Inf, size = 0.5) +
+  annotate(geom = 'segment', y = -Inf, yend = Inf, color = 'black', x = -Inf, xend = -Inf, size = 0.5) +
+  theme(legend.position = "none", 
+        axis.text = element_text(size = 14), 
+        axis.title = element_text(size = 20),
+        strip.text = element_text(face = "bold", size = 16),
+        axis.title.x = element_text(vjust= 0.2))
+
+tolres_facets <- 
+  ggplot(data = filter(df, !Infection_intensity.2 %in% c(NA,0), !Diff_Inf_Class %in% NA),
          aes(y = delta_body_condition, x = as.numeric(Infection_intensity.2), col = Diff_Inf_Class)) + 
-  geom_jitter(size = 3, alpha = 0.5) + 
+  geom_jitter(size = 2, alpha = 0.5, width=0.2) + 
+  geom_line(y=0, linetype='dashed')+
   geom_smooth(alpha = 0.2, size = 1.5, method = 'lm',se = T, width = 0.2) + 
   facet_wrap(facets = 'Diff_Inf_Class') +
-  labs(y = "Body condition change",x = "Parasitemia \n at second sampling",
+  labs(y = "",x = bquote("Parasitemia at T"[1]),
        col = 'Infection stages') + 
@@
   theme(legend.position = "none", 
-        axis.text = element_text(size = 18), 
-        axis.title = element_text(size = 20),
-        strip.text = element_text(face = "bold", size = 16))
+        axis.text = element_text(size = 14), 
+        axis.title = element_text(size = 20),
+        strip.text = element_text(face = "bold", size = 16),
+        axis.title.x = element_text(vjust= 0.2))
 
@@
 ## -----------------------------------------------------------------------------
-g <- ggplot_gtable(ggplot_build(tolres))
+g <- ggplot_gtable(ggplot_build(tolres_facets))
 stripr <- which(grepl('strip-t', g$layout$name))
@@
 ## -----------------------------------------------------------------------------
-fig3 = tolres + 
+fig3 = tolres + g + plot_layout(width=c(1,2)) &  
   theme(plot.tag = element_text(size = 16, face = "bold")) 
@@
 
-ggsave(g,filename = "./Figs/Fig3_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 2400)
+ggsave(fig3,filename = "./Figs/Fig3.2_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 1700)
 ```
@@
 
-ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)
+ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages_Treatment.png",units = "px", width = 3700, height = 3700)
 
@@
   geom_hline(yintercept = mean(df$Breathing_rate, na.rm = T), linetype = "dashed") + 
-  labs(x = "", y = "Breathing rate") + 
+  labs(x = "", y = bquote("Breathing rate at T"[1])) + 
   geom_jitter(color = "lightgrey", size = 2, width = .3) + 
@@
   geom_hline(yintercept = mean(df$body_temperature, na.rm = T), linetype = "dashed") + 
-  labs(x = "", y = "Body temperature") + 
+  labs(x = "", y = bquote("Body temperature at T"[1])) + 
   geom_jitter(color = "lightgrey", size = 2, width = .3) + 
@@
 
-ggsave(figs2,filename = "./Figs/FigS2_observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)
+ggsave(figs2,filename = "./Figs/FigS2_observed_physio_param_infection_stages_Treatment.png",units = "px", width = 3500, height = 3800)
 
@@
   geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
-  labs(x = "Parasitemia", y = "\U0394 Body condition") + 
+  labs(x = bquote("Parasitemia at T"[1]), y = "\U0394 Body condition") + 
   geom_jitter(color = "lightgrey", size = 2, width = .3) + 
@@
   geom_hline(yintercept = mean(df$Growth_rate, na.rm = T), linetype = "dashed") + 
-  labs(x = "Parasitemia", y = "Growth rate") + 
+  labs(x = bquote("Parasitemia at T"[1]), y = "Growth rate") + 
   geom_jitter(color = "lightgrey", size = 2, width = .3) + 
@@
 
-ggsave(figs3,filename = "./Figs/FigS3_observed_physio_param_parasitemia.png",units = "px", width = 3500, height = 3800)
+ggsave(figs3,filename = "./Figs/FigS3_observed_physio_param_parasitemia_Treatment.png",units = "px", width = 3500, height = 3800)
 
@@
   se = T,
-  title = "Breathing rate",
+  title = "Breathing rate at T1",
   axis.labels = 
-    rev(c("Increase : Treatment [Malarone]","Age (days)",
-          "Peak : Treatment [Malarone]","Decrease : Treatment [Malarone]",
-          "Uninfected : Treatment [Malarone]","Increasing parasitemia",
-          "Sex [Males]","Decreasing parasitemia","Sampling interval",
-          "Peak parasitemia","Weight (g)","Ambient temperature",
-          "Year [2019]","Year [2018]","Year [2020]")))
+    rev(c("Age (days) at T1",
+          "Treatment [Malarone] at T0",
+          "Increasing parasitemia",
+          "Peak parasitemia",
+          "Decreasing parasitemia",
+          "Sex [Males]",
+          "Sampling interval",
+          "Weight (g) at T1",
+          "Ambient temperature at T1",
+          "Year [2019]",
+          "Year [2018]",
+          "Year [2020]")))
 
@@
   se = T,
-  title = "Body temperature",
+  title = "Body temperature at T1",
   axis.labels = 
-    rev(c("Peak : Treatment [Malarone]","Ambient temperature","Year [2020]",
-          "Age (days)","Decrease : Treatment [Malarone]","Weight (g)",
-          "Sex [Males]", "Decreasing parasitemia","Increase : Treatment [Malarone]",
-          "Increasing parasitemia","Uninfected : Treatment [Malarone]",
-          "Peak parasitemia","Sampling interval")))
+    rev(c("Ambient temperature at T1",
+          "Year [2020]",
+          "Age (days) at T1",
+          "Decreasing parasitemia",
+          "Weight (g) at T1",
+          "Treatment [Malarone] at T0",
+          "Sex [Males]", 
+          "Peak parasitemia",
+          "Increasing parasitemia",
+          "Sampling interval")))
 
@@
   axis.labels =
-    rev(c("Year [2020]","Peak : Treatment [Malarone]","Year [2018]",
-          "Year [2019]","Sampling interval","Increase : Treatment [Malarone]",
-          "Decrease : Treatment [Malarone]","Age (days)",
-          "Uninfected : Treatment [Malarone]","Sex [Males]",
-          "Increasing parasitemia","Decreasing parasitemia","Peak parasitemia")))
+    rev(c("Year [2020]",
+          "Year [2018]",
+          "Year [2019]",
+          "Sampling interval",
+          "Treatment [Malarone] at T0",
+          "Age (days) at T1",
+          "Increasing parasitemia",
+          "Sex [Males]",
+          "Peak parasitemia",
+          "Decreasing parasitemia")))
 
@@
   axis.labels = 
-    rev(c("Peak : Treatment [Malarone]","Year [2020]","Year [2018]",
-          "Sampling interval","Year [2019]","Decrease : Treatment [Malarone]",
-          "Increase : Treatment [Malarone]","Uninfected : Treatment [Malarone]",
-          "Increasing parasitemia","Decreasing parasitemia","Peak parasitemia",
-          "Sex [Males]","Age (days)")))
+    rev(c("Year [2020]",
+          "Year [2018]",
+          "Sampling interval",
+          "Year [2019]",
+          "Treatment [Malarone] at T0",
+          "Increasing parasitemia",
+          "Peak parasitemia",
+          "Decreasing parasitemia",
+          "Sex [Males]",
+          "Age (days) at T1")))
 
@@
 figs4 = Fig_S4A + Fig_S4B + Fig_S4C + Fig_S4D + plot_annotation(tag_levels = 'a') & 
-  theme(plot.tag = element_text(size = 16, face = "bold"))
+  theme(axis.text = element_text(size=14), plot.tag = element_text(size = 16, face = "bold"))
 figs4
@@
   se = T,
-  title = "Breathing rate",
+  title = "Breathing rate at T1",
   axis.labels = 
-    rev(c("Parasitemia [2] : Treatment [Malarone]","Age (days)",
-          "Parasitemia 1", "Parasitemia 4",
-          "Parasitemia [1] : Treatment [Malarone]",
-          "Parasitemia [3] : Treatment [Malarone]",
-          "Parasitemia [0] : Treatment [Malarone]",
-          "Sex [Males]","Parasitemia 3","Sampling interval",
-          "Parasitemia 2","Weight (g)","Ambient temperature",
-          "Year [2019]","Year [2018]","Year [2020]")))
+    rev(c("Age (days) at T1",
+          "Parasitemia 1 at T1", 
+          "Parasitemia 4 at T1",
+          "Treatment [Malarone] at T0",
+          "Parasitemia 2 at T1",
+          "Parasitemia 3 at T1",
+          "Sex [Males]",
+          "Sampling interval",
+          "Weight (g) at T1",
+          "Ambient temperature at T1",
+          "Year [2019]",
+          "Year [2018]",
+          "Year [2020]")))
 
@@
   se = T,
-  title = "Body temperature",
+  title = "Body temperature at T1",
   axis.labels = 
-    rev(c("Ambient temperature","Year [2020]","Age (days)",
-          "Parasitemia [3] : Treatment [Malarone]",
-          "Parasitemia 1", "Parasitemia [2] : Treatment [Malarone]",
-          "Weight (g)","Parasitemia 2","Sex [Males]",
-          "Parasitemia [0] : Treatment [Malarone]",
-          "Parasitemia [1] : Treatment [Malarone]",
-          "Parasitemia 3", "Sampling interval","Parasitemia 4")))
+    rev(c("Ambient temperature at T1",
+          "Year [2020]",
+          "Age (days) at T1",
+          "Parasitemia 1 at T1",
+          "Parasitemia 2 at T1",
+          "Weight (g) at T1",
+          "Treatment [Malarone] at T0",
+          "Sex [Males]",
+          "Parasitemia 3 at T1",
+          "Sampling interval",
+          "Parasitemia 4 at T1")))
 
@@
   axis.labels = 
-    rev(c("Year [2020]","Year [2018]","Year [2019]",
-          "Parasitemia [2] : Treatment [Malarone]",
-          "Parasitemia 1","Sampling interval",
-          "Parasitemia [3] : Treatment [Malarone]",
-          "Parasitemia [0] : Treatment [Malarone]",
-          "Age (days)","Sex [Males]","Parasitemia 3",
-          "Parasitemia 2","Parasitemia [1] : Treatment [Malarone]",
-          "Parasitemia 4")))
+    rev(c("Year [2020]",
+          "Year [2018]",
+          "Year [2019]",
+          "Sampling interval",
+          "Parasitemia 1 at T1",
+          "Treatment [Malarone] at T0",
+          "Age (days) at T1",
+          "Sex [Males]",
+          "Parasitemia 2 at T1",
+          "Parasitemia 3 at T1",
+          "Parasitemia 4 at T1")))
 
@@
   axis.labels = 
-    rev(c("Year [2020]","Parasitemia [2] : Treatment [Malarone]",
-          "Year [2018]","Year [2019]","Sampling interval","Parasitemia 1",
-          "Parasitemia [3] : Treatment [Malarone]",
-          "Parasitemia [0] : Treatment [Malarone]",
-          "Parasitemia 3","Sex [Males]","Parasitemia 2",
-          "Age (days)","Parasitemia 4","Parasitemia [1] : Treatment [Malarone]")))
+    rev(c("Year [2020]",
+          "Year [2018]",
+          "Sampling interval",
+          "Year [2019]",
+          "Parasitemia 1 at T1",
+          "Treatment [Malarone] at T0",
+          "Parasitemia 2 at T1",
+          "Parasitemia 3 at T1",
+          "Sex [Males]",
+          "Age (days) at T1",
+          "Parasitemia 4 at T1")))
 
@@
 figs5 = Fig_S5A + Fig_S5B + Fig_S5C + Fig_S5D + plot_annotation(tag_levels = 'a') & 
-  theme(plot.tag = element_text(size = 16, face = "bold"))
+  theme(axis.text = element_text(size=14), plot.tag = element_text(size = 16, face = "bold"))
 figs5
@@
 ggsave(figs5, filename = "./Figs/FigS5_effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
+
+## Additional figure: body condition at first sampling according to L. prevalence
+##------------------------------------------------------------------------------
+
+figs6 = ggplot(df)+
+          aes(Prevalence1, body_condition.1)+
+          geom_jitter(width=0.1)+
+          geom_boxplot()+
+          stat_summary(fun = mean, colour = "black", geom = "point", size = 5, show.legend = FALSE)+
+          labs(x=bquote("Leucocytozoon prevalence at T"[1]),y=bquote("Body condition at T"[0]))+
+          stat_compare_means(method = 't.test')
+
+figs6
+
+ggsave(figs6,filename = "./Figs/FigS6_body_condition_1_to_prevalence.png",units = "px", width = 3700, height = 3700)
 ```

### 2025-01-08 MS_physiology_infection.Rmd
delta body condition to condition T1

@@
 ---
-title: "R code for 'Apparent physiological costs of blood parasite infection in the early-life of a vertebrate host - only in highest infections'"
-author: "Tony Rinaud, Meinolf Ottensmann, Oliver Krüger & Nayden Chakarov"
+title: "R code for 'Blood parasite infection causes marginal temporary costs in juvenile birds of prey'"
+author: "Tony Rinaud, Meinolf Ottensmann, Hugo Pereira, Tim M. Rapp, Kai-Philipp Gladow, Oliver Krüger & Nayden Chakarov"
 output: html_document
@@
 The raw data is comprised of 276 common buzzard (*Buteo buteo*) individuals.
-Each individual was sampled twice over the course of the nestling period during the years 2016 and 2018 - 2020.
+Each individual was sampled at least twice over the course of the nestling period during the years 2016 and 2018 - 2020.
 First, the raw data is loaded from the file `physiology_infection_stage_full_wideformat.csv` and re-formatted (scaling variables, reordering factor levels etc.) before downstream analyses:
@@
 
+mod_br <- mod_br[1:4,]
+
 ## Plotting predicted values across infection stages
 ## -----------------------------------------------------------------------------
-Fig_S1A <- ggplot(mod_br) + 
+Fig_S1A <-
+
+  ggplot(mod_br) + 
   aes(x,predicted) + 
@@
                 size = 8, colour = wes_palette("Zissou1",4), width = 0,) + 
-  geom_point(color = "black", outlier.shape = NA, size = 2, width = .3) + 
+  geom_point(color = "black", size = 2) + 
   theme_classic() + 
@@
   mutate(x = factor(c(paste0(x,"\nn= ",n2)), levels = c(paste0(x,"\nn= ",n2))))
+
+mod_bt <- mod_bt[1:4,]
 
@@
 
-```{r mixed model body condition}
+```{r mixed model delta body condition}
 ## Model 
@@
   mutate(x = factor(c(paste0(x,"\nn= ",n3)), levels = c(paste0(x,"\nn= ",n3))))
+
+mod_bc <- mod_bc[1:4,]
 
@@
 
+### Body condition at T1
+
+```{r mixed model body condition - Stages}
+## Model 
+## -----------------------------------------------------------------------------
+lmer_bc2 <- lmer(
+  body_condition.2 ~ Diff_Inf_Class + Treatment + Age_in_days + days_resample +
+    Sex + Year + (1|Nest),
+  data = df)
+
+# Predicted values for each infection stage
+mod_bc2 = get_model_data(lmer_bc2,type = 'pred',terms = "Diff_Inf_Class") %>%
+  mutate(x = factor(c("Uninfected","Increase","Peak","Decrease"), 
+                  levels = c("Uninfected","Increase","Peak","Decrease")))
+
+# Table with sample sizes specific for body condition change data
+n3.2 = table(df$Diff_Inf_Class[!is.na(df$body_condition.2)])
+
+mod_bc2 <- mod_bc2 %>% 
+  mutate(x = factor(c(paste0(x,"\nn= ",n3.2)), levels = c(paste0(x,"\nn= ",n3.2))))
+
+mod_bc2 <- mod_bc2[1:4,]
+
+# Plotting predicted values across infection stages
+
+Fig_S1C2 =
+
+  ggplot(mod_bc2) + 
+  aes(x,predicted) + 
+  geom_hline(yintercept = mean(mod_bc2$predicted, na.rm = T), 
+             linetype = "dashed") + 
+  labs(x = "", 
+       y = "Body condition at T1") + 
+  geom_errorbar(aes(ymin = mod_bc2$conf.low,
+                    ymax = mod_bc2$conf.high),
+                colour = "black",
+                size = 2, 
+                width = .1) +
+  geom_errorbar(aes(ymin = mod_bc2$predicted - mod_bc2$std.error,
+                    ymax = mod_bc2$predicted + mod_bc2$std.error),
+                size = 8,
+                colour = wes_palette("Zissou1",4),
+                width = 0,) +
+  geom_point(color = "black", 
+             size = 2) + 
+  theme_classic() + 
+  theme(legend.position = "none",
+        axis.title = element_text(size = 18),
+        axis.text = element_text(size = 16),
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, face = "bold")) + 
+  geom_segment(size = .8, 
+               aes(x = 1, 
+                   y = max(mod_bc2$conf.high) + 17, 
+                   xend = 4, 
+                   yend = max(mod_bc2$conf.high) + 17)) + 
+  geom_text(aes(x = 2.5, 
+                y = max(mod_bc2$conf.high) + 23),
+              label = "n.s.", size = 5)
+```
+
 ### Growth rate
@@
   mutate(x = factor(c(paste0(x,"\nn= ",n4)), levels = c(paste0(x,"\nn= ",n4))))
+
+mod_gr <- mod_gr[1:4,]
 
@@
 sjPlot::tab_model(
-  lmer_br,lmer_bt,lmer_bc,lmer_gr,
+  lmer_br,lmer_bt,lmer_bc2,lmer_gr,
   show.ci50 = T ,
@@
                 bquote("Body temperature at T"[1]),
-                "\U0394 Body condition",
+                bquote("Body condition at T"[1]),
                 "Growth rate"),
-  file = "./Tables/Table1_results_lmer_physiological_parameters_p.val_kr_Treatment.html")
+  file = "./Tables/Table1_results_lmer_physiological_parameters_p.val_kr_Treatment2.html")
 ```
@@
 
-```{r mixed model body condition change 2}
+```{r mixed model delta body condition change 2}
 ## Model:
@@
 
+### Body condition at T1
+
+```{r mixed model body condition - Parasitemia}
+## Model:
+## Note: 
+## One Contrast for the Interaction of Infection intensity and treatment
+## is not estimatable due to the lack of infection level 4 for the Malarone-group
+## -----------------------------------------------------------------------------
+lmer_bc_para2 <- lmer(
+  body_condition.2 ~ Infection_intensity.2 + Treatment + Age_in_days + days_resample +
+    Sex + Year + (1|Nest), data = df)
+
+## Rerun without intercept for plotting mean estimates 
+## -----------------------------------------------------------------------------
+lmer_bc_para_no_intercept2 <- lmer(
+  body_condition.2 ~ 0+ Infection_intensity.2 + Treatment + Age_in_days + days_resample +
+    Sex + Year + (1|Nest), data = df)
+
+## Obtain effect sizes for post-treatment parasitemia and derive model predictions
+## -----------------------------------------------------------------------------
+mod_bc_para2 <- 
+  left_join(plot_model(lmer_bc_para_no_intercept2, se = F, )[["data"]][1:5,], ## 95% CI
+            plot_model(lmer_bc_para_no_intercept2, se = T, )[["data"]][1:5,]) %>%  ## SE
+  mutate(predicted = estimate) %>% 
+  mutate(lower_CI = conf.low) %>% 
+  mutate(higher_CI = conf.high) %>% 
+  mutate(se = std.error) %>% 
+  mutate(x = factor(c("0","1","2","3","4"), levels = c("0","1","2","3","4")))
+
+# Table with sample sizes specific for body condition change data
+m3.2 = table(df$Infection_intensity.2[!is.na(df$body_condition.2)])
+
+mod_bc_para2 <- mod_bc_para2 %>% 
+  mutate(x = factor(c(paste0(x,"\nn= ",m3.2)), levels = c(paste0(x,"\nn= ",m3.2))))
+
+# Plotting predicted values across infection intensities
+
+Fig_4C2 = ggplot(mod_bc_para2) + 
+  aes(as.factor(mod_bc_para2$x),
+      mod_bc_para2$predicted) + 
+  geom_hline(yintercept = mean(mod_bc_para2$predicted, na.rm = T), 
+             linetype = "dashed") + 
+  labs(x = bquote("Parasitemia at T"[1]),
+       y = "Body condition at T1") + 
+  geom_errorbar(aes(ymin = mod_bc_para2$lower_CI, 
+                    ymax = mod_bc_para2$higher_CI),
+                colour = "black",
+                size = 2, 
+                width = .1) + 
+  geom_errorbar(aes(ymin = mod_bc_para2$predicted - mod_bc_para2$se,
+                    ymax = mod_bc_para2$predicted + mod_bc_para2$se),
+                size = 8, 
+                colour = wes_palette("Zissou1",5), 
+                width = 0,) + 
+  geom_point(color = "black", 
+             size = 4) + 
+  theme_classic() + 
+  theme(legend.position = "none",
+        axis.title = element_text(size = 20),  
+        axis.title.x = element_text(size = 20, 
+                                    vjust=-0.5),
+        axis.text = element_text(size = 16), 
+        axis.line.x = element_blank(),
+        axis.ticks.x = element_blank(), 
+        plot.margin = margin(0, 0, 0, 0, "cm"),
+        plot.title = element_text(hjust = 0.5, 
+                                  face = "bold")) + 
+  geom_segment(size = .8,
+                 aes(x = 1, y = 60, xend = 5, yend = 60)) + 
+    geom_text(aes(x = 3, y = 67),
+              label = "P = 0.026", size = 5) + 
+  geom_segment(size = .8,
+                 aes(x = 1, y = 60, xend = 1, yend = 53)) + 
+  geom_segment(size = .8,
+                 aes(x = 5, y = 60, xend = 5, yend = 53))
+```
+
 ### Growth rate
@@
 ## -----------------------------------------------------------------------------
-fig4 = Fig_4A + Fig_4B + Fig_4C + Fig_4D + plot_annotation(tag_levels = 'a') & 
+fig4 = Fig_4A + Fig_4B + Fig_4C2 + Fig_4D + plot_annotation(tag_levels = 'a') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
@@
 
-ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities_Treatment.png",units = "px", width = 3700, height = 3700)
+ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities_Treatment2.png",units = "px", width = 3700, height = 3700)
 
@@
   lmer_bt_para,
-  lmer_bc_para,
+  lmer_bc_para2,
   lmer_gr_para,
@@
                 bquote("Body temperature at T"[1]),
-                "\U0394 Body condition",
+                bquote("Body condition at T"[1]),
                 "Growth rate"),
-  file = "./Tables/Table2_results_parasitemia_lmer_physiological_parameters_p.val_kr_Treatment.html")
+  file = "./Tables/Table2_results_parasitemia_lmer_physiological_parameters_p.val_kr_Treatment2.html")
 ```
@@
   geom_line(y=0, linetype='dashed')+
-  geom_smooth(alpha = 0.2, size = 1.5, method = 'lm',se = T, width = 0.2) + 
+  geom_smooth(alpha = 0.3, size = 1.5, method = 'lm',se = T, width = 0.2) + 
   facet_wrap(facets = 'Diff_Inf_Class') +
@@
 ggsave(fig3,filename = "./Figs/Fig3.2_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 1700)
+
+## Comparing means parasitemia X stages
+df %>% mutate(para_stage=factor(paste(df$Infection_intensity.2,df$Diff_Inf_Class,sep='_'), levels=c('1_Increase',"2_Increase","2_Peak","3_Increase","3_Peak",'4_Increase','4_Peak','3_Decrease',"2_Decrease","1_Decrease", "0_Decrease")))  %>%
+  mutate(treat_stage=factor(paste(df$Treatment,df$Diff_Inf_Class,sep='_'))) -> df
+
+ggplot(df)+
+  aes(para_stage,delta_body_condition)+
+  geom_boxplot()+
+  geom_jitter()+
+  stat_n_text()+
+  geom_hline(yintercept = mean(df$delta_body_condition), linetype = 2)+
+  geom_hline(yintercept = 0,colour = 'red')+
+  stat_compare_means(ref.group = ".all.",hide.ns = T,method = "t.test")
+
+## Comparing physio parameters between sucessfully treated and rest
+
+comp=list(c("Malarone_Decrease","Malarone_not_decrease"),c("Malarone_Decrease","Malarone_Uninfected"),c("Malarone_not_decrease", "Malarone_Uninfected"))
+
+ggplot(df)+
+    aes(treat_stage, delta_body_condition)+
+    geom_hline(yintercept = mean(df$delta_body_condition), linetype = 2)+
+    geom_hline(yintercept = 0,colour = 'red')+
+    stat_n_text()+
+    geom_boxplot()+
+    stat_compare_means(comparisons = comp)
+
+ggplot(df)+
+    aes(treat_stage, Breathing_rate)+
+    geom_hline(yintercept = mean(df$Breathing_rate), linetype = 2)+
+    geom_hline(yintercept = 0,colour = 'red')+
+    stat_n_text()+
+    geom_boxplot()+
+    stat_compare_means(comparisons = comp)
+
+ggplot(df)+
+    aes(treat_stage, body_temperature)+
+    geom_hline(yintercept = mean(df$body_temperature), linetype = 2)+
+    geom_hline(yintercept = 0,colour = 'red')+
+    stat_n_text()+
+    geom_boxplot()+
+    stat_compare_means(comparisons = comp)
+
+ggplot(df)+
+    aes(treat_stage, Growth_rate)+
+    geom_hline(yintercept = mean(df$Growth_rate), linetype = 2)+
+    geom_hline(yintercept = 0,colour = 'red')+
+    stat_n_text()+
+    geom_boxplot()+
+    stat_compare_means(comparisons = comp)
 ```
@@
 
-figS1 <- Fig_S1A + Fig_S1B + Fig_S1C + Fig_S1D + plot_annotation(tag_levels = 'a') & 
+figS1 <- Fig_S1A + Fig_S1B + Fig_S1C2 + Fig_S1D + plot_annotation(tag_levels = 'a') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
@@
 
-ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages_Treatment.png",units = "px", width = 3700, height = 3700)
+ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages_Treatment2.png",units = "px", width = 3700, height = 3700)
 
@@
 Fig_S2C = ggplot(df[!df$Diff_Inf_Class %in% NA,]) + 
-  aes(Diff_Inf_Class,delta_body_condition) + 
-  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
-  labs(x = "", y = "\U0394 Body condition") + 
+  aes(Diff_Inf_Class,body_condition.2) + 
+  geom_hline(yintercept = mean(df$body_condition.2, na.rm = T), linetype = "dashed") + 
+  labs(x = "", y = "Body condition at T1") + 
   geom_jitter(color = "lightgrey", size = 2, width = .3) + 
@@
 Fig_S3C = ggplot(df[!df$Infection_intensity.2 %in% NA,]) + 
-  aes(Infection_intensity.2,delta_body_condition) + 
-  geom_hline(yintercept = mean(df$delta_body_condition, na.rm = T), linetype = "dashed") + 
-  labs(x = bquote("Parasitemia at T"[1]), y = "\U0394 Body condition") + 
+  aes(Infection_intensity.2,body_condition.2) + 
+  geom_hline(yintercept = mean(df$body_condition.2, na.rm = T), linetype = "dashed") + 
+  labs(x = bquote("Parasitemia at T"[1]), y = bquote("Body condition at T"[1])) + 
   geom_jitter(color = "lightgrey", size = 2, width = .3) + 
@@
 Fig_S4C = plot_model(
-  lmer_bc,
+  lmer_bc2,
   sort.est = T,
   se = T,
-  title = "\U0394 Body condition",
+  title = "Body condition at T1",
   axis.labels =
@@
 Fig_S5C = plot_model(
-  lmer_bc_para,
+  lmer_bc_para2,
   sort.est = T,
   se = T,
-  title = "\U0394 Body condition",
+  title = "Body condition at T1",
   axis.labels = 

### 2025-02-21 MS_physiology_infection.Rmd
Add files via upload

@@
 ```{r packages, message=F, warning=F}
-library(chron)
-library(cowplot)
-library(EnvStats)
-library(lme4)
-library(lmerTest)
-library(lsmeans)
-library(ggalt)
-library(ggdist)
-library(ggeffects)
-library(ggplot2)
-library(ggpubr)
-library(ggrepel)
-library(ggridges)
-library(ggsci)
-library(ggsignif)
-library(grid)
-library(gridExtra)
-library(magrittr)
-library(patchwork)
-library(plyr)
-library(rptR)
-library(RVAideMemoire)
-library(sjPlot)
-library(sjlabelled)
-library(sjmisc)
-library(tidybayes)
-library(tidyverse)
-library(wesanderson)
-library(car)
+
+require(easypackages)
+
+libraries("chron", "cowplot","EnvStats","lsmeans","ggalt","ggdist","ggeffects",
+          "ggplot2","ggpubr","ggrepel","ggridges","ggsci","ggsignif","grid",
+          "gridExtra","magrittr","patchwork","plyr","rptR","RVAideMemoire",
+          "sjPlot","sjlabelled","sjmisc","tidybayes","tidyverse","wesanderson",
+          "car","ggh4x","ggforce","lme4","lmerTest")
+
 ## set theme for ggplot objects
@@
 Fig2 <-  Fig_2A +Fig_2B+
-  plot_annotation(tag_levels = 'a') + 
+  plot_annotation(tag_levels = 'A',tag_suffix = ')') + 
   theme(plot.tag = element_text(size = 22, face = "bold"))
@@
   labs(x = "", 
-       y = "Body condition at T1") + 
+       y = bquote("Body condition at T"[1])) + 
   geom_errorbar(aes(ymin = mod_bc2$conf.low,
@@
   labs(x = bquote("Parasitemia at T"[1]),
-       y = "Body condition at T1") + 
+       y = bquote("Body condition at T"[1])) + 
   geom_errorbar(aes(ymin = mod_bc_para2$lower_CI, 
@@
 ## -----------------------------------------------------------------------------
-fig4 = Fig_4A + Fig_4B + Fig_4C2 + Fig_4D + plot_annotation(tag_levels = 'a') & 
+fig4 = Fig_4A + Fig_4B + Fig_4C2 + Fig_4D + plot_annotation(tag_levels = 'A', 
+                  tag_suffix = ')') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
@@
 
-ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities_Treatment2.png",units = "px", width = 3700, height = 3700)
+ggsave(fig4,filename = "./Figs/Fig4_predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)
 
@@
 ## -----------------------------------------------------------------------------
-fig3 = tolres + g + plot_layout(width=c(1,2)) &  
+fig3 = tolres + g + plot_layout(width=c(1,2)) + plot_annotation(tag_levels = 'A',
+                    tag_suffix = ')') &
   theme(plot.tag = element_text(size = 16, face = "bold")) 
@@
 
-ggsave(fig3,filename = "./Figs/Fig3.2_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 1700)
+ggsave(fig3,filename = "./Figs/Fig3_delta_body_condition_to_parasitemia_second.png",units = "px", width = 3700, height = 1700)
 
@@
 
-ggplot(df)+
+g0=ggplot(df)+
   aes(para_stage,delta_body_condition)+
@@
 
-ggplot(df)+
+g1=ggplot(df)+
     aes(treat_stage, delta_body_condition)+
@@
 
-ggplot(df)+
+g2=ggplot(df)+
     aes(treat_stage, Breathing_rate)+
@@
 
-ggplot(df)+
+g3=ggplot(df)+
     aes(treat_stage, body_temperature)+
@@
 
-ggplot(df)+
+g4=ggplot(df)+
     aes(treat_stage, Growth_rate)+
@@
 
-figS1 <- Fig_S1A + Fig_S1B + Fig_S1C2 + Fig_S1D + plot_annotation(tag_levels = 'a') & 
+figS1 <- Fig_S1A + Fig_S1B + Fig_S1C2 + Fig_S1D + plot_annotation(tag_levels = 'A', tag_suffix = ")") & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
@@
 
-ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages_Treatment2.png",units = "px", width = 3700, height = 3700)
+ggsave(figS1,filename = "./Figs/FigS1_predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)
 
@@
   geom_hline(yintercept = mean(df$body_condition.2, na.rm = T), linetype = "dashed") + 
-  labs(x = "", y = "Body condition at T1") + 
+  labs(x = "", y = bquote("Body condition at T"[1])) + 
   geom_jitter(color = "lightgrey", size = 2, width = .3) + 
@@
 ## ----------------------------------------------------------------------------- 
-figs2 = Fig_S2A + Fig_S2B + Fig_S2C + Fig_S2D + plot_annotation(tag_levels = 'a') & 
+figs2 = Fig_S2A + Fig_S2B + Fig_S2C + Fig_S2D + plot_annotation(tag_levels = 'A',
+                  tag_suffix = ')') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
@@
 
-ggsave(figs2,filename = "./Figs/FigS2_observed_physio_param_infection_stages_Treatment.png",units = "px", width = 3500, height = 3800)
+ggsave(figs2,filename = "./Figs/FigS2_observed_physio_param_infection_stages.png",units = "px", width = 3500, height = 3800)
 
@@
 ## ----------------------------------------------------------------------------- 
-figs3 = Fig_S3A + Fig_S3B + Fig_S3C + Fig_S3D + plot_annotation(tag_levels = 'a') & 
+figs3 = Fig_S3A + Fig_S3B + Fig_S3C + Fig_S3D + plot_annotation(tag_levels = 'A', tag_suffix = ')') & 
   theme(plot.tag = element_text(size = 16, face = "bold"))
@@
 
-ggsave(figs3,filename = "./Figs/FigS3_observed_physio_param_parasitemia_Treatment.png",units = "px", width = 3500, height = 3800)
+ggsave(figs3,filename = "./Figs/FigS3_observed_physio_param_infection_intensities.png",units = "px", width = 3500, height = 3800)
 
@@
 ## ----------------------------------------------------------------------------- 
-figs4 = Fig_S4A + Fig_S4B + Fig_S4C + Fig_S4D + plot_annotation(tag_levels = 'a') & 
+figs4 = Fig_S4A + Fig_S4B + Fig_S4C + Fig_S4D + plot_annotation(tag_levels = 'A',
+                                                                tag_suffix = ')') & 
   theme(axis.text = element_text(size=14), plot.tag = element_text(size = 16, face = "bold"))
@@
 
-ggsave(figs4,filename = "./Figs/FigS4_effect_sizes_param_stages.png",units = "px", width = 3500, height = 3800)
+ggsave(figs4,filename = "./Figs/FigS4_effect_sizes_param_infection_stages.png",units = "px", width = 3500, height = 3800)
 
@@
 
-## Figure S4
-## ----------------------------------------------------------------------------- 
-figs5 = Fig_S5A + Fig_S5B + Fig_S5C + Fig_S5D + plot_annotation(tag_levels = 'a') & 
+## Figure S5: effect sizes for infection intensity models
+## ----------------------------------------------------------------------------- 
+figs5 = Fig_S5A + Fig_S5B + Fig_S5C + Fig_S5D + plot_annotation(tag_levels = 'A',
+                                                                tag_suffix = ')') & 
   theme(axis.text = element_text(size=14), plot.tag = element_text(size = 16, face = "bold"))
@@
 
-ggsave(figs5, filename = "./Figs/FigS5_effect_sizes_param_intensities.png",units = "px", width = 3500, height = 3800)
-
-## Additional figure: body condition at first sampling according to L. prevalence
+ggsave(figs5, filename = "./Figs/FigS5_effect_sizes_param_infection_intensities.png",units = "px", width = 3500, height = 3800)
+```
+
+```{r robustness}
+## Robustness infection stages - summary graph of third sampled individuals
 ##------------------------------------------------------------------------------
 
-figs6 = ggplot(df)+
+# Loading the dataset
+
+third_sampled=readxl::read_excel("third_samples_indidividuals.xlsx")
+
+# Computing the number of days between second and third sampling
+
+third_sampled$Avg_third=third_sampled$Date.3-third_sampled$Date.2
+
+# Categorizing infection trends
+
+third_sampled$Stage.1_2=as.numeric(third_sampled$Infection_intensity.2)-as.numeric(third_sampled$Infection_intensity.1)
+
+third_sampled$Stage.2_3=as.numeric(third_sampled$Infection_intensity.3)-as.numeric(third_sampled$Infection_intensity.1)
+
+third_sampled$comp_inf_stages=NA
+
+for(i in 1:length(third_sampled$Date.1)){
+  # cat(third_sampled$Stage.1_2[i], 'versus', third_sampled$Stage.2_3[i], "\n")
+  if(third_sampled$Infection_intensity.1[i] == 0 & third_sampled$Infection_intensity.2[i] == 0 &
+     third_sampled$Infection_intensity.3[i]== 0){
+    third_sampled$comp_inf_stages[i]="Unchanged_uninfected"
+    next
+  }
+  if(third_sampled$Stage.1_2[i] > 0 & third_sampled$Stage.1_2[i] == third_sampled$Stage.2_3[i]){
+  third_sampled$comp_inf_stages[i]="Unchanged_increase"
+  next
+  }
+  if(third_sampled$Stage.1_2[i] < 0 & third_sampled$Stage.1_2[i] == third_sampled$Stage.2_3[i]){
+    third_sampled$comp_inf_stages[i]="Unchanged_decrease"
+    next
+  }
+  if(third_sampled$Stage.1_2[i] == 0 & third_sampled$Stage.1_2[i] == third_sampled$Stage.2_3[i]){
+    third_sampled$comp_inf_stages[i]="Unchanged_stable"  
+    next
+  }
+  if(third_sampled$Stage.1_2[i] < 0 & third_sampled$Stage.2_3[i] > 0){
+    third_sampled$comp_inf_stages[i]="Decrease_to_Increase"  
+    next
+  }
+  if(third_sampled$Stage.1_2[i] < 0 & third_sampled$Stage.2_3[i] == 0){
+    third_sampled$comp_inf_stages[i]="Decrease_to_Stable" 
+    next
+  }
+  if(third_sampled$Stage.1_2[i] == 0 & third_sampled$Stage.2_3[i] < 0){
+    third_sampled$comp_inf_stages[i]="Stable_to_Decrease" 
+    next
+  }
+  if(third_sampled$Stage.1_2[i] == 0 & third_sampled$Stage.2_3[i] > 0){
+    third_sampled$comp_inf_stages[i]="Stable_to_Increase" 
+    next
+  }
+  if(third_sampled$Stage.1_2[i] > 0 & third_sampled$Stage.2_3[i] < 0){
+    third_sampled$comp_inf_stages[i]="Increase_to_decrease" 
+    next
+  }
+  if(third_sampled$Stage.1_2[i] > 0 & third_sampled$Stage.2_3[i] == 0){
+    third_sampled$comp_inf_stages[i]="Increase_to_stable" 
+    next
+  }
+  if(third_sampled$Stage.1_2[i] > 0 & third_sampled$Stage.2_3[i] > 0){
+    third_sampled$comp_inf_stages[i]="Unchanged_increase"  
+    next
+  }
+}
+
+third_sampled$comp_inf_stages_summary=ifelse(third_sampled$comp_inf_stages %in% c("Unchanged_increase",
+                "Unchanged_decrease","Unchanged_stable",'Unchanged_uninfected'),"Unchanged","Differed")
+
+# Plotting infection intensity across three sampling
+
+strip=strip_themed(background_x = elem_list_rect(fill = ifelse(third_sampled$comp_inf_stages_summary %in% "Unchanged",'#30D40F','#D41C0F')))
+
+gg_trends=ggplot(third_sampled)+
+  geom_point(aes(Date.1,Infection_intensity.1))+
+  geom_point(aes(Date.2,Infection_intensity.2))+
+  geom_point(aes(Date.3,Infection_intensity.3))+
+  facet_wrap2(~`Ring no`,scales = "free_x", strip=strip)+
+  labs(title="Individual infection course - three-time sampled",x="Date",y="Infection intensity")
+
+gg_trends
+
+## Figure S6: Infection course - third sampled individuals
+##------------------------------------------------------------------------------
+
+ggsave(gg_trends,filename = "./Figs/FigS6_infection_trends_third_sampled.png",units = "px", width = 3700, height = 1700)
+
+```
+
+```{r body condition at T1 according to prevalence}
+## Figure S7: body condition at first sampling according to L. prevalence
+##------------------------------------------------------------------------------
+
+figs7 = ggplot(df)+
           aes(Prevalence1, body_condition.1)+
@@
 
-figs6
-
-ggsave(figs6,filename = "./Figs/FigS6_body_condition_1_to_prevalence.png",units = "px", width = 3700, height = 3700)
-```
-
-## Estimating measurment error of body temperature
+figs7
+
+ggsave(figs7,filename = "./Figs/FigS7_body_condition_T1_to_prevalence.png",units = "px", width = 3700, height = 3700)
+
+```
+
+## Estimating measurement error of body temperature
 
